### 2016-02-05 text/ms.tex
added some words

\documentclass[12pt, preprint]{aastex}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{bm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\hypersetup{colorlinks}
\usepackage{color}
\usepackage{morefloats}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue }

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\begin{document}

\title{Constraining galaxy assembly bias with galaxy-galaxy measurements of Sloan Digital Sky Survey}

\begin{abstract}

\end{abstract}

\section{Introduction}

Throughout this paper, unless stated otherwise, all radii and densities are in comoving units.
Standard flat $\lambda$CDM is assumed, and all cosmological parameters are set to the planck 
2015 best-fit estimates.

\section{Galaxy assembly bias}

The assumption that galaxies reside dark matter halos is the bedrock of the modern cosmology and 
large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
that the halo mass alone is sufficient in determining the population of halos. Despite its simplifying 
assumption, this model has ben widely used in fitting the measurements of galaxy clustering an galaxy-galaxy lensing.

\section{Galaxy-Galaxy Lensing}

In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
as the ensemble average of the product of galaxy over densities and matter overdensities
\beq
\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
\eeq
where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
and galaxies.

This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
lenses,
\begin{eqnarray}
\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
\end{eqnarray}

\section{Concentration-dependence of galaxy-halo connection}

\section{Method}

\section{SDSS measurements}

\section{Results}

\section{Discussion}

\begin{thebibliography}{70}

\end{thebibliography}

\end{document}

### 2016-02-05 code/dsigma.py

@@ -1,17 +1,19 @@
 import numpy as np
-#import matplotlib.pyplot as plt
-#plt.switch_backend("Agg")
 import pylab
 from matplotlib import lines as mlines
 from matplotlib import pyplot as plt
 import numpy as np
-from halotools.empirical_models import PrebuiltHodModelFactory
 
-"""convenience functions for lensing calaculations"""
 
 eps = 1.e-13
 
-def sigma(xigm , rbins):
+def get_sigma(xigm , r):
+
+    """
+    computes projected matter surface density as a function of 
+    comoving radius (Mpc/h)
+    from a tabulated \xi_{gm} and bins of radii
+    """
 
     sig = np.zeros_like((xigm))
 

### 2016-02-08 text/ms.tex
updating the text and the list of papers

@@
 
-In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
+In g-g lensing, the connection between dark matter and galaxies is probed by measuring 
 the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
@@
 \Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
-          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
+          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}},
 \end{eqnarray}
+where $\chi$ is the projected comoving line-of-sight distance, and $R$ is the projected comoving transverse distance.
+
+Since the galaxy-matter cross correlation falls off rapidly that in practice thre redshoft evolution of $\xi_{gm}$ 
+can be neglected, integrating only out to a line-fo-sight distance of $\chi=$ 50 Mpc is sufficient. 
+The mean excess projected density $\bar{\Sigma}(R)$ can be approximated by the following radial integral,
+\beq
+\bar{\Sigma}(R , z_{l}) = 2 \rho_{c,0}\Omega_{m,0}\int_{0}^{\mathrm{50Mpc}} \; \xi_{gm}\Big(\sqrt{R^{2}+\chi^{2}},z_{L} \Big)d\chi.
+\eeq
 

### 2016-02-08 code/xigm.py

@@ -48,4 +48,3 @@ def xigm_tabulated_generator(hod = 'leauthaud11' , threshold = 10.6 , \
     rr , xigm = model.mock.compute_galaxy_matter_cross_clustering(rbins = rbin)
 
     return rr , xigm
-

### 2016-02-09 code/dsigma.py
working g-m cross correlation

@@ -32,9 +32,7 @@ def get_sigma(xigm , r):
 def sigmabar(xigm , rbins):
 
     sigbar = np.zeros_like((xigm))
-    
     sig = sigma(xigm , rbins)
-
     r = .5*(rbins[1:]+rbins[:-1])
     dr = rbins[1:]-rbins[:-1]
 
@@ -60,7 +58,6 @@ def dsigma(xigm , rbins):
 
 
 def dsigmap(xigm , rbins):
-
 
     return sigma(xigm , rbins) - sigmabar(xigm , rbins)   
 

### 2016-02-09 code/xigm.py

@@ -3,10 +3,17 @@ from matplotlib import lines as mlines
 from matplotlib import pyplot as plt
 import numpy as np
 from halotools.empirical_models import PrebuiltHodModelFactory
+from scipy import interpolate 
 
+###Constants necessary in calculation of Sigma(R)###
 
-def xigm_tabulated_generator(hod = 'leauthaud11' , threshold = 10.6 , \
-                             rmin = 0.001 , rmax = 80 , nbins = 100 , \
+Omegam = 0.315
+rho_crit = 2.77536627 * 1.e11   #units h^2M_sun/Mpc^-3
+r_los_max = 50
+r_los_min = .001
+
+def xigm_tabulated_generator(hod = 'leauthaud11' , tr = 9.8 , \
+                             rmin = 0.001 , rmax = 80 , nbins = 10 , \
                              scale = 'log' , sim = 'bolshoi', z = 0.0):
 
 
@@ -41,10 +48,42 @@ def xigm_tabulated_generator(hod = 'leauthaud11' , threshold = 10.6 , \
 
         raise ValueError("invalid scaling for the rbins")
 
-    model = PrebuiltHodModelFactory(hod , threshold)
+    model = PrebuiltHodModelFactory(hod ,threshold = tr , redshift = z)
     model.populate_mock(simname = sim , redshift = z)
 
 
     rr , xigm = model.mock.compute_galaxy_matter_cross_clustering(rbins = rbin)
 
     return rr , xigm
+
+
+def xigm_func(r , r1 , r2):
+ 
+    tabulated_rr , tabulated_xigm = xigm_tabulated_generator(rmin = r1 , rmax = r2)
+   
+    if r.min() < tabulated_rr.min():
+        if r.max() > tabulated_rr.max():
+    
+            raise ValueError("invalid input for radius")    
+ 
+    f = interpolate.interp1d(tabulated_rr, tabulated_xigm , kind = 'cubic')
+    
+    return f(r)
+    
+
+
+if  __name__=='__main__':
+
+    import pylab
+    import time
+    a = time.time()
+    rr ,xigm = xigm_tabulated_generator(rmin = .1 , rmax = 10. , nbins = 50)
+    print time.time() - a
+    pylab.loglog(rr , xigm)
+    #pylab.show()
+    rr2 = np.logspace(np.log10(.2) , np.log10(8) , 10)
+    a = time.time()
+    xigm2 = xigm_func(rr2, .1 , 10)
[…]

### 2016-02-10 code/tutorial.py
added a demo for wp

@@ -1,0 +1,14 @@
+import numpy as np
+import matplotlib.pyplot as plt
+plt.switch_backend("Agg")
+from halotools.empirical_models import PrebuiltModelFactory
+from scipy import interpolate
+
+
+
+
+model = PrebuiltModelFactory("zheng07")
+model.populate_mock()
+
+
+

### 2016-02-10 code/wp_tutorial.py

@@ -1,0 +1,121 @@
+
+from halotools.mock_observables import wp
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+
+from matplotlib import lines as mlines
+from matplotlib import pyplot as plt
+plt.switch_backend("Agg")
+import numpy as np
+
+def fracdiff(alt, fid):
+    return (alt-fid)/fid
+
+
+rbins = np.logspace(-1, 1.25, 15)
+rmax = rbins.max()
+rbin_centers = (rbins[1:] + rbins[0:-1])/2.
+pbins = np.logspace(-1, 1.25, 15)
+
+
+
+def proj_clustering(pos , rbins, pbins , cellsize):
+
+    return wp(sample1 = pos, rp_bins = rbins, 
+              pi_bins = pbins, sample2 = None, 
+              period = np.array([250,250,250]), approx_cell1_size = cellsize)
+
+
+from halotools.empirical_models import PrebuiltHodModelFactory
+
+# The "fiducial" stellar mass threshold is 10**10.5
+model = PrebuiltHodModelFactory('hearin15', threshold = 10.5, redshift = 0., 
+                        central_assembias_strength = 1, 
+                        satellite_assembias_strength = 1)
+model.param_dict['scatter_model_param1'] = 0.4 # This is the "fiducial" scatter used throughout the paper
+
+baseline_model = PrebuiltHodModelFactory('leauthaud11', threshold = 10.5, redshift = 0.)
+baseline_model.param_dict['scatter_model_param1'] = 0.4
+
+#base_model
+
+baseline_model.populate_mock()
+pos = three_dim_pos_bundle(baseline_model.mock.galaxy_table, 'x', 'y', 'z')
+wp_base = proj_clustering(pos , rbins , pbins , cellsize = [rmax, rmax, rmax])
+
+
+#central assembly bias only
+
+model.param_dict['mean_occupation_satellites_assembias_param1'] = 0
+model.param_dict['mean_occupation_centrals_assembias_param1'] = 1
+model.populate_mock()
+pos = three_dim_pos_bundle(model.mock.galaxy_table, 'x', 'y', 'z')
[…]

### 2016-02-10 code/xigm.py

@@ -81,7 +81,7 @@ if  __name__=='__main__':
     print time.time() - a
     pylab.loglog(rr , xigm)
     #pylab.show()
-    rr2 = np.logspace(np.log10(.2) , np.log10(8) , 10)
+    rr2 = np.logspace(np.log10(.2) , np.log10(8) , 5)
     a = time.time()
     xigm2 = xigm_func(rr2, .1 , 10)
     print time.time() - a

### 2016-05-08 code/biased_hod.py
changed the way luminosity threshold is passed around

@@ -34,7 +34,6 @@ class MCMC_model(object):
     def __init__(self, Mr):
         
         self.Mr = Mr
-        thr = -1. * np.float(Mr)
         self.model = composite_model(Mr)
         self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
 

### 2016-05-08 code/mcmc.py

@@ -9,7 +9,8 @@ import h5py
 # --- Local ---
 import util
 import data as Data
-from dechod import MCMC_model
+#from dechod import MCMC_model
+from biased_hod import MCMC_model
 from prior import PriorRange
 
 
@@ -70,7 +71,7 @@ def lnPost(theta, **kwargs):
     return lp + lnlike(theta, **kwargs)
 
 
-def mcmc_mpi(Nwalkers, Niters, data_dict={'Mr':Mr}, prior_name = 'first_try'): 
+def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try'): 
     '''
     Parameters
     -----------
@@ -80,21 +81,21 @@ def mcmc_mpi(Nwalkers, Niters, data_dict={'Mr':Mr}, prior_name = 'first_try'):
         Number of MCMC chains   
     '''
     #data and covariance matrix
-    fake_obs_icov = Data.load_covariance(**data_dict)
-    fake_obs = Data.load_data(**data_dict)
+    fake_obs_icov = Data.load_covariance(Mr)
+    fake_obs = Data.load_data(Mr)
         
     # True HOD parameters
-    data_hod = Data.load_dechhod_random_guess(**data_dict)
+    data_hod = Data.load_dechod_random_guess(Mr)
     Ndim = len(data_hod)
 
     # Priors
-    prior_min, prior_max = PriorRange(**data_dict , prior_name)
+    prior_min, prior_max = PriorRange(prior_name , Mr)
     prior_range = np.zeros((len(prior_min),2))
     prior_range[:,0] = prior_min
     prior_range[:,1] = prior_max
     
     # mcmc chain output file 
-    chain_file_name = ''.join([util.mcmc_dir(),'mcmc_chain_Mr',str(**data_dict),'.hdf5'])
+    chain_file_name = ''.join([util.mcmc_dir(),'mcmc_chain_Mr',str(Mr),'.hdf5'])
  
 
     if os.path.isfile(chain_file_name) and continue_chain:   
@@ -133,7 +134,7 @@ def mcmc_mpi(Nwalkers, Niters, data_dict={'Mr':Mr}, prior_name = 'first_try'):
             'prior_range': prior_range, 
             'data': fake_obs, 
             'data_icov': fake_obs_icov, 
-            'Mr': data_dict['Mr']
+            'Mr': Mr
[…]

### 2016-05-08 code/tests/test_double_assembly.py
testing the effect of central assembly bias on occupation and adding some example figures

@@ -1,0 +1,158 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from halotools.sim_manager import CachedHaloCatalog
+from halotools.empirical_models import HodModelFactory
+from halotools.empirical_models import TrivialPhaseSpace, Zheng07Cens
+from halotools.empirical_models import Zheng07Sats , HeavisideAssembias
+from halotools.empirical_models import PrebuiltHodModelFactory
+from halotools.mock_observables import tpcf
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables import FoFGroups
+from halotools.mock_observables.pair_counters import npairs_3d
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+import matplotlib.pyplot as plt
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models import NFWPhaseSpace
+from matplotlib import lines as mlines
+
+halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+
+class AssembiasZheng07Cens(Zheng07Cens, HeavisideAssembias):
+
+    def __init__(self, **kwargs):
+
+        Zheng07Cens.__init__(self, threshold = -21)
+
+        HeavisideAssembias.__init__(self,
+            method_name_to_decorate = 'mean_occupation',
+            lower_assembias_bound = 0.,
+            upper_assembias_bound = 1,
+            **kwargs)
+
+class AssembiasZheng07Sats(Zheng07Sats, HeavisideAssembias):
+
+    def __init__(self, **kwargs):
+
+        Zheng07Sats.__init__(self, threshold = -21)
+
+        HeavisideAssembias.__init__(self,
+            method_name_to_decorate = 'mean_occupation',
+            lower_assembias_bound = 0.,
+            upper_assembias_bound = np.inf,
+            **kwargs)
+
[…]

### 2016-05-09 code/data.py
pushing new changes in mcmc

@@ -23,19 +23,19 @@ def load_wp(Mr):
     Mr : (int)
         Absolute r-band magnitude threshold. Default is M_r = -21
     '''
-    if Mr == 21:
+    if Mr == 21.:
         data_file = ''.join([util.dat_dir(),
             'wpxi_dr72_bright0_mr21.0_z0.159_nj400']) 
     if Mr == 20.5:
         data_file = ''.join([util.dat_dir(),
             'wpxi_dr72_bright0_mr20.5_z0.132_nj400']) 
-    if Mr == 20:
+    if Mr == 20.:
         data_file = ''.join([util.dat_dir(),
             'wpxi_dr72_bright0_mr20.0_z0.106_nj400']) 
     if Mr == 19.5:
         data_file = ''.join([util.dat_dir(),
             'wpxi_dr72_bright0_mr19.5_z0.085_nj400']) 
-    if Mr == 19:
+    if Mr == 19.:
         data_file = ''.join([util.dat_dir(),
             'wpxi_dr72_bright0_mr19.0_z0.064_nj400'])
     wp = np.loadtxt(data_file)[:,1]
@@ -45,15 +45,15 @@ def load_wp(Mr):
 def load_nbar(Mr):
     '''load the number density of the data
     '''
-    if Mr == 21:
+    if Mr == 21.:
         nbar = 1.16 * 10**-3.
     if Mr == 20.5:
         nbar = 3.13 * 10**-3.
-    if Mr == 20:
+    if Mr == 20.:
         nbar = 6.37 * 10**-3.
     if Mr == 19.5:
         nbar = 11.64 * 10**-3.
-    if Mr == 19:
+    if Mr == 19.:
         nbar = 15.66 * 10**-3.
 
     return nbar
@@ -66,19 +66,19 @@ def load_wp_covariance(Mr):
     Mr : (int)
         Absolute r-band magnitude threshold. Default is M_r = -21
     '''
-    if Mr == 21:
+    if Mr == 21.:
         data_file = ''.join([util.dat_dir(),
             'wpxicov_dr72_bright0_mr21.0_z0.159_nj400']) 
     if Mr == 20.5:
         data_file = ''.join([util.dat_dir(),
             'wpxicov_dr72_bright0_mr20.5_z0.132_nj400']) 
-    if Mr == 20:
+    if Mr == 20.:
[…]

### 2016-05-09 code/dechod.py

@@ -19,8 +19,6 @@ from halotools.empirical_models import enforce_periodicity_of_box
 
 class AssembiasZheng07Sats(Zheng07Sats, HeavisideAssembias):
    
-  
-
     def __init__(self, Mr = 21 , **kwargs):
         
         self.Mr = Mr

### 2016-05-09 code/prior.py

@@ -3,13 +3,13 @@ Module to deal with prior range
 '''
 import numpy as np
 
-def PriorRange(prior_name): 
+def PriorRange(prior_name , Mr): 
     ''' Given prior dictionary name, return the prior range. 
     '''
     if prior_name is None: 
         prior_name = 'first_try'
     
-    dict_table = prior_dict_table() 
+    dict_table = prior_dict_table(Mr) 
 
     prior_dict = dict_table[prior_name]
 
@@ -20,40 +20,40 @@ def PriorRange(prior_name):
 def prior_dict_table(Mr): 
     ''' dictionary table of priors 
     '''
-    if Mr ==21 :
+    if Mr ==21. :
       dict_table = { 
             'first_try': {
-                'prior_min': [10.5, 0.1, 11.8, 0.85, 13., -1. , -1.],
-                'prior_max': [14.5, 0.8, 13.8, 1.45, 15., 1. , 1.]
+                'prior_min': [10., 0.05, 10., 0.85, 13., -1. , -1.],
+                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
                 }
               }
             
     if Mr ==20.5 :
       dict_table = { 
             'first_try': {
-                'prior_min': [10.5, 0.1, 11.8, 0.85, 13., -1. , -1.],
-                'prior_max': [14.5, 0.8, 13.8, 1.45, 15., 1. , 1.]
+                'prior_min': [10., 0.05, 10., 0.85, 12., -1. , -1.],
+                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
                 }
               }
     if Mr ==20. :
       dict_table = { 
             'first_try': {
-                'prior_min': [10.5, 0.1, 11.8, 0.85, 13., -1. , -1.],
-                'prior_max': [14.5, 0.8, 13.8, 1.45, 15., 1. , 1.]
+                'prior_min': [10., 0.05, 10., 0.85, 12., -1. , -1.],
+                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
                 }
               }
     if Mr ==19.5 :
       dict_table = { 
             'first_try': {
-                'prior_min': [10.5, 0.1, 11.8, 0.85, 13., -1. , -1.],
-                'prior_max': [14.5, 0.8, 13.8, 1.45, 15., 1. , 1.]
[…]

### 2016-05-11 text/ms.tex
text

--- 2016-02-05 text/ms.tex
@@
 
-\title{Constraining galaxy assembly bias with galaxy-galaxy measurements of Sloan Digital Sky Survey}
+\title{Searching for galaxy assembly bias with the clustering measurements of Sloan Digital Sky Survey}
 
@@
 
+The assumption that galaxies reside dark matter halos is the central tenent of the modern cosmology and 
+large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
+connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
+that the halo mass alone is sufficient in determining the population of galaxies inside halos. 
+Despite this simplifying assumption, this model has ben widely---and succesfully---utilized in fitting 
+the measurements of galaxy clustering and galaxy-galaxy lensing.
+
+In this investigation, we explore the notion that how the dependence of galaxy-halo connection on 
+halo properties beyond mass---such as concentration, age, etc---
 Throughout this paper, unless stated otherwise, all radii and densities are in comoving units.
@@
 
-The assumption that galaxies reside dark matter halos is the bedrock of the modern cosmology and 
-large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
-connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
-that the halo mass alone is sufficient in determining the population of halos. Despite its simplifying 
-assumption, this model has ben widely used in fitting the measurements of galaxy clustering an galaxy-galaxy lensing.
+%%%%I'm most likely going to postpone lensing to another manuscript, just wanna focus on clustering
+%%%%because I have better handle on that%%%%%%
 
-\section{Galaxy-Galaxy Lensing}
+%\section{Galaxy-Galaxy Lensing}
 
-In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
-the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
-as the ensemble average of the product of galaxy over densities and matter overdensities
-\beq
-\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
-\eeq
-where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
-assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
-and galaxies.
+%In g-g lensing, the connection between dark matter and galaxies is probed by measuring 
+%the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
+%as the ensemble average of the product of galaxy over densities and matter overdensities
+%\beq
+%\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
+%\eeq
+%where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
+%assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
+%and galaxies.
 
-This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
-lenses,
-\begin{eqnarray}
-\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
-          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
-\end{eqnarray}
+%This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
+%lenses,
+%\begin{eqnarray}
+%\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
+%          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}},
+%\end{eqnarray}
+%where $\chi$ is the projected comoving line-of-sight distance, and $R$ is the projected comoving transverse distance.
+
+%Since the galaxy-matter cross correlation falls off rapidly that in practice thre redshoft evolution of $\xi_{gm}$ 
+%can be neglected, integrating only out to a line-fo-sight distance of $\chi=$ 50 Mpc is sufficient. 
+%The mean excess projected density $\bar{\Sigma}(R)$ can be approximated by the following radial integral,
+%\beq
+%\bar{\Sigma}(R , z_{l}) = 2 \rho_{c,0}\Omega_{m,0}\int_{0}^{\mathrm{50Mpc}} \; \xi_{gm}\Big(\sqrt{R^{2}+\chi^{2}},z_{L} \Big)d\chi.
+%\eeq
 

### 2016-05-11 code/diagnosis/plotter.py
corner plot for posterior probabilities

@@ -4,6 +4,8 @@ Plotting modules
 
 '''
 import os
+import os.path as path 
+
 import h5py
 import corner
 import numpy as np
@@ -11,11 +13,15 @@ import matplotlib.pyplot as plt
 import matplotlib.image as mpimg
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 from matplotlib.ticker import MaxNLocator
-
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
 plt.switch_backend("Agg")
 
+prior_min = [10., 0.05, 10., 0.85, 12., -1. , -1.]
+prior_max = [14.5, 0.7, 14., 1.45, 15., 1. , 1.]  
 
-def plot_mcmc(Nwalkers, Nburns, filename):
+def plot_time_mcmc(Nwalkers, Nburns, filename):
 
     sample = h5py.File(filename , "r")["mcmc"]
     npars = sample.shape[2]
@@ -25,7 +31,7 @@ def plot_mcmc(Nwalkers, Nburns, filename):
         axes[i].plot(sample[:, :, i], color="b", alpha=.4 , lw = .5)
 	axes[i].yaxis.set_major_locator(MaxNLocator(5))
         #axes[i].set_ylim([plot_range[i,0], plot_range[i,1]])
-        axes[i].set_xlim(0, 7750)
+        axes[i].set_xlim(0, 20000)
         #axes[i].set_ylabel(labels[i], fontsize=25)
 
     axes[-1].set_xlabel("Step Number", fontsize=25)
@@ -34,5 +40,50 @@ def plot_mcmc(Nwalkers, Nburns, filename):
     plt.savefig(fig_file)
     plt.close()
 
+def plot_corner_mcmc(Nchains , Nburns, Mr , filename):
+
+    sample = h5py.File(filename , "r")["mcmc"]
+    npars = sample.shape[2]
+    nwalkers = sample.shape[1]
+    sample = sample[Nburns:Nchains, : , :]
+    sample = sample.reshape(sample.shape[0]*sample.shape[1] , sample.shape[2])
+    print sample.shape    
+    #prior_min, prior_max = PriorRange('first_try' , Mr)
+    prior_range = np.zeros((len(prior_min),2))
+    prior_range[:,0] = np.array(prior_min)
+    prior_range[:,1] = np.array(prior_max) 
+
+    fig = corner.corner(
+            sample,
[…]

### 2016-05-11 code/mcmc.py
added Hartlap correction to the inverse of the covariance and changed the upper bound of scatter prior

@@ -58,9 +58,10 @@ def lnPost(theta, **kwargs):
         res_wp = model_wp - data_wp
 
         f_bol = (1. + 71.74*10.**6. / (250.)**3.)
+        f_bias = (400. - len(res_wp) -1.)/(400. - 1.)
 
         neg_chisq_nbar = -0.5*(res_nbar**2.)/(nbar_var)
-        neg_chisq_wp = -0.5*np.sum(np.dot(res_wp , solve(wp_cov , res_wp)))
+        neg_chisq_wp = -0.5 * f_bias * np.sum(np.dot(res_wp , solve(wp_cov , res_wp)))
     	neg_chisq = neg_chisq_nbar + neg_chisq_wp
 
         print "neg_chi_tot" , neg_chisq

### 2016-05-11 code/prior.py

@@ -24,7 +24,7 @@ def prior_dict_table(Mr):
       dict_table = { 
             'first_try': {
                 'prior_min': [10., 0.05, 10., 0.85, 13., -1. , -1.],
-                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
+                'prior_max': [14.5, 1.5, 14., 1.45, 15., 1. , 1.]
                 }
               }
             
@@ -32,28 +32,28 @@ def prior_dict_table(Mr):
       dict_table = { 
             'first_try': {
                 'prior_min': [10., 0.05, 10., 0.85, 12., -1. , -1.],
-                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
+                'prior_max': [14.5, 1.5, 14., 1.45, 15., 1. , 1.]
                 }
               }
     if Mr ==20. :
       dict_table = { 
             'first_try': {
                 'prior_min': [10., 0.05, 10., 0.85, 12., -1. , -1.],
-                'prior_max': [14.5, 0.7, 14., 1.45, 15., 1. , 1.]
+                'prior_max': [14.5, 1.5, 14., 1.45, 15., 1. , 1.]
                 }
               }
     if Mr ==19.5 :
       dict_table = { 
             'first_try': {
                 'prior_min': [10., 0.05, 10., 0.85, 11.5, -1. , -1.],
-                'prior_max': [14.5, 0.7, 14.0, 1.45, 15., 1. , 1.]
+                'prior_max': [14.5, 1.5, 14.0, 1.45, 15., 1. , 1.]
                 }
               }
     if Mr ==19. :
       dict_table = { 
             'first_try': {
                 'prior_min': [10., 0.05, 10.0, 0.85, 11.5, -1. , -1.],
-                'prior_max': [14.5, 0.7, 14.0, 1.45, 15., 1. , 1.]
+                'prior_max': [14.5, 1.5, 14.0, 1.45, 15., 1. , 1.]
                 }
               }
 

### 2016-05-11 code/data.py
added correction to log-likelihood from finite volume model

@@ -125,3 +125,22 @@ def load_dechod_random_guess(Mr):
         pos = [11.49 , 0.26 , 11.6 , 1.02 , 12.83 , 0.5 , 0.5]
 
     return pos
+
+def load_Volume_corrector(Mr):
+    '''calculate the volume correction term of the 
+       covariance matrix'''
+    Vsim = 250. ** 3.
+    
+    if Mr == 21.:
+        Vd = 71.74 * 10**6.
+    if Mr == 20.5:
+        Vd = 41.82 * 10**6.
+    if Mr == 20.:
+        Vd = 22.0 * 10**6.
+    if Mr == 19.5:
+        Vd = 11.44 * 10**6.
+    if Mr == 19.:
+        Vd = 4.87 * 10**6.
+
+    return (1. + Vd / Vsim)
+

### 2016-05-11 code/mcmc.py

@@ -57,11 +57,12 @@ def lnPost(theta, **kwargs):
         res_nbar = model_nbar - data_nbar
         res_wp = model_wp - data_wp
 
-        f_bol = (1. + 71.74*10.**6. / (250.)**3.)
+        f_vol = Data.load_Volume_corrector(Mr)**-1.
+
         f_bias = (400. - len(res_wp) -1.)/(400. - 1.)
 
         neg_chisq_nbar = -0.5*(res_nbar**2.)/(nbar_var)
-        neg_chisq_wp = -0.5 * f_bias * np.sum(np.dot(res_wp , solve(wp_cov , res_wp)))
+        neg_chisq_wp = -0.5 * f_bias * f_vol * np.sum(np.dot(res_wp , solve(wp_cov , res_wp)))
     	neg_chisq = neg_chisq_nbar + neg_chisq_wp
 
         print "neg_chi_tot" , neg_chisq

### 2016-05-13 code/adhoc_mcmc.py
model with no galaxy assembly bias

@@ -1,0 +1,164 @@
+import os 
+import sys
+import numpy as np
+import emcee
+from numpy.linalg import solve
+from emcee.utils import MPIPool
+from numpy.linalg import solve
+import h5py
+# --- Local ---
+import util
+import data as Data
+from hod import MCMC_model
+from prior import PriorRange
+
+
+def lnPost(theta, **kwargs):
+    def lnprior(theta, **kwargs):
+        '''log prior 
+        '''
+        fake_obs = kwargs['data']
+    	fake_obs_icov = kwargs['data_icov']
+    	kwargs.pop('data', None)
+    	kwargs.pop('data_icov', None)
+
+    	prior_range = kwargs['prior_range']
+    	prior_min = prior_range[:,0]
+    	prior_max = prior_range[:,1]
+    	# Prior 
+        if prior_min[0] < theta[0] < prior_max[0] and \
+       	    prior_min[1] < theta[1] < prior_max[1] and \
+            prior_min[2] < theta[2] < prior_max[2] and \
+            prior_min[3] < theta[3] < prior_max[3] and \
+            prior_min[4] < theta[4] < prior_max[4]
+
+                return 0
+    
+        else:
+		return -np.inf
+
+    def lnlike(theta, **kwargs):
+
+    	fake_obs = kwargs['data']
+    	fake_obs_icov = kwargs['data_icov']
+
+        data_nbar , data_wp = fake_obs[0] , fake_obs[1]
+        nbar_var , wp_cov = fake_obs_icov[0] , fake_obs_icov[1]
+
+    	kwargs.pop('data', None)
+    	kwargs.pop('data_icov', None)
+    	prior_range = kwargs['prior_range']
+    	# Likelihood
+    	model_obvs = generator(theta, prior_range)
+        model_nbar , model_wp = model_obvs[0] , model_obvs[1]
+        
+        res_nbar = model_nbar - data_nbar
+        res_wp = model_wp - data_wp
+
+        f_vol = Data.load_Volume_corrector(Mr)**-1.
+
+        f_bias = (400. - len(res_wp) -2.)/(400. - 1.)
+
+        neg_chisq_nbar = -0.5*(res_nbar**2.)/(nbar_var)
+        neg_chisq_wp = -0.5 * f_bias * f_vol * np.sum(np.dot(res_wp , solve(wp_cov , res_wp)))
+    	neg_chisq = neg_chisq_nbar + neg_chisq_wp
+
+        print "neg_chi_tot" , neg_chisq
+        return neg_chisq
+
[…]

### 2016-05-13 code/data.py

@@ -102,10 +102,21 @@ def load_nbar_variance(Mr):
     return nbarerr ** 2.
 
 def load_hod_random_guess(Mr):
-    ''' load initial positions of MCMC chains,
-        hardcoded for now '''
-    pos = [12.59 , 0.49 , 12.78 , 1.14 , 13.99 , 0.1]
-    
+    '''random guess for the walkers'''
+
+    if Mr == 21.:
+        pos = [12.59 , 0.49 , 12.78 , 1.14 , 13.99]
+    if Mr == 20.5:
+        pos = [11.84 , 0.39 , 12.79 , 1.12 , 13.58]
+    if Mr == 19.5:
+        pos = [12.59 , 0.49 , 12.78 , 1.14 , 13.99]
+    if Mr == 20.:
+        pos = [11.38 , 0.26 , 12.02 , 1.06 , 13.31]
+    if Mr == 19.5:
+        pos = [11.69 , 0.28 , 11.75 , 1.05 , 13.01]
+    if Mr == 19.:
+        pos = [11.49 , 0.26 , 11.6 , 1.02 , 12.83]
+
     return pos
 
 def load_dechod_random_guess(Mr):

### 2016-05-13 code/hod.py

@@ -1,0 +1,67 @@
+'''
+model without galaxy assembly bias
+'''
+import numpy as np
+import os.path as path
+
+from Corrfunc import _countpairs
+from Corrfunc.utils import read_catalog
+
+from halotools.sim_manager import CachedHaloCatalog
+from halotools.empirical_models import PrebuiltHodModelFactory
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+from halotools.empirical_models import enforce_periodicity_of_box
+
+def single_model(Mr):
+
+    model = PrebuiltHodModelFactory("zheng07" , threshold = -1.*Mr)
+
+    return model
+
+class MCMC_model(object):
+
+    def __init__(self, Mr):
+        
+        self.Mr = Mr
+        self.model = single_model(Mr)
+        self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+
+        ###pair counter settings ###
+
+        self.boxsize = self.halocat.Lbox
+        self.nthreads = 1
+        self.pimax = 40.0
+        self.binfile = path.join(path.dirname(path.abspath(__file__)),
+                        "../", "bin")
+        self.autocorr = 1
+
+    def __call__(self, theta, prior_range):
+        return self._sum_stat(theta, prior_range=prior_range)
+
+    def _sum_stat(self, theta, prior_range=None):
+        
+        self.model.param_dict['logM0'] = theta[0]
+        self.model.param_dict['sigma_logM'] = theta[1]
+        self.model.param_dict['logMmin'] = theta[2]
+        self.model.param_dict['alpha'] = theta[3]
+        self.model.param_dict['logM1'] = theta[4]
+
+        self.model.populate_mock(self.halocat) 
+        x = self.model.mock.galaxy_table['x']
+        y = self.model.mock.galaxy_table['y']
+        z = self.model.mock.galaxy_table['z']
+        vz = self.model.mock.galaxy_table['vz']
+        # applying RSD
+        pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
+        # enforcing PBC
+        pos = enforce_periodicity_of_box(pos, self.boxsize)
+        pos = pos.astype(np.float32)
+        x, y, z = pos[:,0] , pos[:,1] , pos[:,2]
[…]

### 2016-06-15 text/ms.tex
just pushing the text that already lives in overleaf

--- 2016-02-05 text/ms.tex
@@
 \documentclass[12pt, preprint]{aastex}
+\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{graphicx}	% For figures
@@
 \usepackage{amsmath}	% for \iint
+\usepackage{mathtools}
 \usepackage{bm}
@@
 \usepackage{hyperref}
+\usepackage{algorithmic,algorithm}
 \hypersetup{colorlinks}
@@
 urlcolor=darkred,
-citecolor=darkblue }
+citecolor=darkblue}
 
@@
 
+\newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}
 \newcommand{\beq}{\begin{equation}}
 \newcommand{\eeq}{\end{equation}}
-
+\newcommand{\lang}{\langle}
+\newcommand{\ra}{\rangle}
+\newcommand{\vep}{\bm{\epsilon}}
+\newcommand{\ep}{\epsilon}
+\newcommand{\pars}{\vec{\theta}}
+\newcommand{\dev}{\mathrm{d}}
 \begin{document}
 
-\title{Constraining galaxy assembly bias with galaxy-galaxy measurements of Sloan Digital Sky Survey}
+\title{Can we detect galaxy assembly bias with group and clustering statistics of SDSS main sample of galaxies?}
+\author{Mohammadjavad Vakili , others}
 
 \begin{abstract}
+
+The standard halo occupation modeling approach in large scale structure 
+studies assumes that the halo mass alone suffices in characterizing the 
+galaxy-halo connection. Galaxy assembly bias, the hypothesis that properties beyond 
+halo mass influences the galaxy-halo connection, can potentially affect the 
+statistical summaries of galaxy populations. The degree to which, assembly bias can 
+can be constrained with the statistical distribution of galaxies remains largely 
+untested. In this investigation, we make use of the recently proposed assembly bias decoration 
+of the HOD modeling in order to find constraints on the strength of the assembly bias from the most up-to-date and publicly available measurements of the group multiplicity function and the projected two-point correlation function of the Volume-limited luminosity threshold sample of SDSS
+galaxies.
+We find that the available GMF measurements cannot constrain galaxy assembly bias in any of the Luminosity thresholds.
+On the other hand, we find non-zero constraints on the satellite galaxy assembly bias for the $M_{r}<-18$ and $M_{r}<-19$ samples, nonzero constraints on the central galaxy assembly bias for the $M_{r}<-20$ samples, and constraints consistent with zero for the assembly bias of galaxies in the $M_{r}<-21$ sample.
+Furthermore, we provide a model comparison between the standard HOD approach and the decorated HOD in modeling of the GMF and the projected 2PCF measurements.
 
@@
 \section{Introduction}
+The assumption that galaxies reside dark matter halos 
+is the central tenet of the modern cosmology and 
+large-scale structure formation theories. 
+One of the most powerful methods for describing 
+the galaxy-halo connection is the halo occupation modeling. 
+The underlying assumption of the traditional HOD framework is 
+that the halo mass alone is sufficient in determining the
+population of galaxies inside halos. That is, the statistical properties of 
+galaxies is governed by the halo mass. Mathematically, this assumption can be 
+written as $P(N_g|M_h,\{x\})=P(N_g|M_h)$ where $\{x\}$ is the set of all 
+possible halo properties beyond mass $M_{h}$.
 
-Throughout this paper, unless stated otherwise, all radii and densities are in comoving units.
-Standard flat $\lambda$CDM is assumed, and all cosmological parameters are set to the planck 
-2015 best-fit estimates.
+Despite this very simplifying assumption, the galaxy-halo connection models such as HOD and CLF
+have been widely and successfully used in modeling the measurements of a wide range of the 
+statistical properties of galaxies such as . However, the assumption that the statistical 
+distribution of galaxies can be determined by halo mass is not a derived characteristic of 
+accurate and high resolution hydrodynamic simulations, but rather a theoretical assumption 
+that needs to be scrutinized. In recent years, the idea that the
 
-\section{Galaxy assembly bias}
-
-The assumption that galaxies reside dark matter halos is the bedrock of the modern cosmology and 
-large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
-connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
-that the halo mass alone is sufficient in determining the population of halos. Despite its simplifying 
-assumption, this model has ben widely used in fitting the measurements of galaxy clustering an galaxy-galaxy lensing.
-
-\section{Galaxy-Galaxy Lensing}
-
-In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
-the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
-as the ensemble average of the product of galaxy over densities and matter overdensities
-\beq
-\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
-\eeq
-where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
-assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
-and galaxies.
-
-This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
-lenses,
-\begin{eqnarray}
-\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
-          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
-\end{eqnarray}
-
-\section{Concentration-dependence of galaxy-halo connection}
+In this investigation, we explore the notion that how the dependence of 
+galaxy-halo connection on halo properties beyond mass (e.g. concentration, age).
+Throughout this paper, unless stated otherwise, 
+all radii and densities are in comoving units. Standard flat $\Lambda$CDM is assumed, 
+and all cosmological parameters are set to the Planck 2013 best-fit estimates.
 
 \section{Method}
+For our standard HOD modeling, cite[zheng07] HOD parameterization is assumed according to which, 
+the occupation of the central galaxies follows a nearest-integer distribution, 
+and the occupation of the satellite galaxies follows a Poisson distribution. 
+The expected number of centrals and satellites as a function of the host halo 
+mass of $M_{\rm h}$ given by 
+\begin{eqnarray}
+\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \\ 
+\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \rangle \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}.
+\end{eqnarray}
+For placing galaxies inside halos, we follow the procedure described in CITE[HEARIN ETAL], CITE[CHANG ETAL].
+We refer the readers to those papers for a more comprehensive discussion of the forward modeling of the 
+galaxy mock catalogs. Now let us provide a brief overview of the assembly bias decorated HOD modeling 
+In fixed halo mass $M_{\rm h}$, halos are split into two groups of 0.5 percentile highest-concentration 
+and 0.5 lowest-concentration halos. Following CITE[HEARIN ETAL], the centrals
 
-\section{SDSS measurements}
+For sampling from the likelihood given, we use the affine-invariant MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+
+\section{Data}
+
+In this work, we focus on two sets of measurements made on the volume limited luminosity threshold main sample of galaxies 
+in the SDSS spectroscopic survey. The first set consists of the number density $n_{g}$ (measured in units of $h^{3}\rm{Mpc}^{-3}$) 
+and the projected two point correlation function of galaxies $w_{\rm{p}}(r_{\rm{p}})$ (measured in units of $h^{-1}\rm{Mpc}$), 
+and their corresponding covariance matrices constructed using 400 jackknife sub-samples. 
+The 2PCFs are measured in 12 logarithmic bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, 
+starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$. $w_{\rm{p}}(r_{\rm{p}})$s are measured by integrating the two dimensional 
+2PCF $\xi(r_{\rm{p}} , \pi)$ along the line-of-sight up to $\pi_{max}=40 h^{-1}\rm{Mpc}$. The advantage of using these measurements 
+is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, they provide very 
+accurate small scale clustering measurements [see CITE GUO 2015].
+
+The Second set of measurements used in our work are the group multiplicity functions described in [CITE BERLIND 2006]. These measurements are made 
+for the three Volume limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$. 
+Group multiplicity function $g(N)$ (with units of $h^{3}\rm{Mpc}^{-3}$) is defined as the abundance of the galaxy groups as a 
+function of group richness (the number of galaxies in groups) per richness width, measured in bins of richness. 
+Galaxy groups in [CITE BERLIND etal] are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF]. 
+The FoF group finder places two galaxies in a group if the projected (line-of-sight) distance between the two galaxies 
+is less than a specified projected (line-of-sight) linking length in units of the mean inter-particle distance ($n_{\rm g}^{-1/3}$).
+The projected linking and the line-of-sight linking lengths are denoted by $b_{\perp}$ and $b_{\parallel}$ respectively. 
+In order to minimize the discrepancy between the groups found from the group finder and the halos in a suite of simulations, 
+[CITE BERLIND] set $b_{\perp}$ and $b_{\parallel}$ to 0.15 and 0.74 respectively.
+The measurements are accompanied by two sets of uncertainty measurements. 
+The first one is the error in $g(N)$ measured from dispersion between $g(N)$s 
+of different mock catalogs, and the second source of error is the Poisson error measured 
+from the number of groups in each richness bin. Finally, these two uncertainties are added in quadrature 
+to estimate the total error on $g(N)$ measurements.
+
+\section{Simulation}
+For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the Bolshoi-Planck high 
+resolution $N$-body simulation CITE[Klypin2014]. This simulation was carried out using the adaptive refinement tree code 
+(ART, see cite[Kravstov]) code, following the Planck $\Lambda$CDM cosmological parameters 
+$\Omega_{\rm m} = 0.307$, $\Omega_{\rm b} = 0.048$, $\Omega_{\Lambda} = 0.693$, $\sigma_{8} = 0.823$, $n_{\rm s}=0.96$, 
+$h=0.678$. The Box size for this $N$-body simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, 
+the mass per simulation particle $m_{\rm p}$ is $1.5 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length 
+$\epsilon$ is 1 $h^{-1} \rm{kpc}$.
 
@@
 
-\begin{thebibliography}{70}
-
-\end{thebibliography}
-
 \end{document}

### 2016-06-16 text/ms.tex
just updating the text

@@
 \section{Method}
-For our standard HOD modeling, cite[zheng07] HOD parameterization is assumed according to which, 
-the occupation of the central galaxies follows a nearest-integer distribution, 
+For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
 and the occupation of the satellite galaxies follows a Poisson distribution.
-The expected number of centrals and satellites as a function of the host halo 
-mass of $M_{\rm h}$ given by 
+The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the folllowing equations
 \begin{eqnarray}
-\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \\ 
-\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \rangle \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}.
+\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
+\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
 \end{eqnarray}
-For placing galaxies inside halos, we follow the procedure described in CITE[HEARIN ETAL], CITE[CHANG ETAL].
-We refer the readers to those papers for a more comprehensive discussion of the forward modeling of the 
-galaxy mock catalogs. Now let us provide a brief overview of the assembly bias decorated HOD modeling 
-In fixed halo mass $M_{\rm h}$, halos are split into two groups of 0.5 percentile highest-concentration 
-and 0.5 lowest-concentration halos. Following CITE[HEARIN ETAL], the centrals
+
+For populating the halos with galaxies, we follow the procedure described in CITE[HEARIN ETAL], CITE[CHANG ETAL].
+The central galaxies are assumed to be at the center of the host dark matter halos.
+We place the satellite galaxies are within the virial radius of the halo following an NFW profile [CITE NFW].
+The concentration of the NFW profile is given by the empirical mass-concentration relation provided by [CITE MACCIO].
+The velocities of the satellite galaxies are given by two components.
+The first component is the velocity of the host halo.
+The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations [CITE MORE].
+We refer the readers to [CITE HEARIN 15] and \url{http://halotools.readthedocs.io} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+
+Now let us provide a brief overview of HOD modeling decorated with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ introduced in [CITE HEARIN2015].
+At a fixed halo mass $M_{\rm h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.We call the first population "type 1" halos, and the second population "type 2 halos.
+Following In the decorated HOD model, the expected number of central and satellite galaxies in the two populations is given by
+
+\begin{eqnarray}
+\langle N_{c,i} | M_{h},c\rangle &=& \langle N_{c} | M_{h}\rangle + \delta N _{c,i}, \; i=1,2 \label{eq:decoratedcentral} \\
+\langle N_{s,i} | M_{h},c\rangle &=& \langle N_{s} | M_{h}\rangle + \delta N _{s,i}, \; i=1,2 \label{eq:decoratedsatellite}
+\end{eqnarray}
+where $\langle N_{c} | M_{h}\rangle$ and $\langle N_{s} | M_{h}\rangle$ are given by Eqs \ref{hod:central} and \ref{hod:satellite} respectively, and we have $\delta N_{s,0} + \delta N_{s,1} = 0$, and $\delta N_{c,0} + \delta N_{c,1} = 0$.
+These two conditions ensure the conservation of HOD.
+At a given host hale mass $M_{h}$, the central occupation of the the two populations follows a Nearest-integer distribution with the first moment given by \ref{eq:decoratedcentral}; and the central occupation of the the two populations follows a Poisson distribution with the first moment given by \ref{eq:decoratedsatellite}.
+
+Following CITE[HEARIN ETAL], the centrals
 

### 2016-06-17 text/ms.tex
more text

@@
 
-\title{Can we detect galaxy assembly bias with group and clustering statistics of SDSS main sample of galaxies?}
+\title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
 \author{Mohammadjavad Vakili , others}
@@
 \section{Method}
+\subsection{Occupation modeling}
 For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
@@
 
-Following CITE[HEARIN ETAL], the centrals
+In this decorated occupation model, the allowable range for the quantities $\delta N_{c,1}$ and $\delta N_{s,1}$ is given by 
+\begin{eqnarray}
+-\langle N_{c} | M_{h}\rangle \leq \delta N_{c} \leq \langle N_{c} | M_{h}\rangle
+ , \label{eq:cen-bounds} \\
+-\langle N_{s} | M_{h}\rangle \leq \delta N_{s} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
+\end{eqnarray}
+Afterwards, CITE[HEARIN2015] defines the assembly bias parameter $\mathcal{A}$ in the following way:
+\begin{eqnarray}
+\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \\
+\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0,
+\end{eqnarray}
+where the subscript $\alpha = c , s$ for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs.
+\ref{eq:cen-bounds} and \ref{eq:sat-bounds}.
+\subsection{Observables}
 
+\subsection{}
 For sampling from the likelihood given, we use the affine-invariant MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).

### 2016-06-17 text/ms.tex
moar texttt

@@
 \newcommand{\dev}{\mathrm{d}}
+\newcommand{\wpp}{w_{\rm p}}
+\newcommand{\ngal}{n_{g}}
+\newcommand{\gmf}{g(N)}
+\newcommand{\mr}{M_{\rm r}}
+\newcommand{\rpp}{r_{\rm p}}
+\newcommand{\mzero}{\log M_{0}}
+\newcommand{\mone}{\log M_{1}}
+\newcommand{\mmin}{\log M_{\rm min}}
+\newcommand{\sigmam}{\sigma_{\log \rm M}} 
+\newcommand{\acen}{\mathcal{A}_{\rm cen}}
+\newcommand{\asat}{\mathcal{A}_{\rm sat}}
+
 \begin{document}
@@
 \section{Method}
-\subsection{Occupation modeling}
+\subsection{Halo occupation modeling}
+\subsubsection{standard HOD modeling}\label{subsubsec:hod}
 For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
@@
 
+\subsubsection{Assembly bias HOD modeling}\label{subsubsec:decorated}
 Now let us provide a brief overview of HOD modeling decorated with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ introduced in [CITE HEARIN2015].
@@
 \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.
-\subsection{Observables}
 
-\subsection{}
-For sampling from the likelihood given, we use the affine-invariant MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+At a given halo mass $M_{h}$, once the first moments of occupation statistics for the $type$-1 and $type$-2 halos are determined, the same procedure described in \ref{subsubsec:hod} is done to populate the halos with mock galaxies.
 
-\section{Data}
+\subsubsection{Redshift-space distortion}
 
-In this work, we focus on two sets of measurements made on the volume limited luminosity threshold main sample of galaxies 
-in the SDSS spectroscopic survey. The first set consists of the number density $n_{g}$ (measured in units of $h^{3}\rm{Mpc}^{-3}$) 
-and the projected two point correlation function of galaxies $w_{\rm{p}}(r_{\rm{p}})$ (measured in units of $h^{-1}\rm{Mpc}$), 
-and their corresponding covariance matrices constructed using 400 jackknife sub-samples. 
-The 2PCFs are measured in 12 logarithmic bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, 
-starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$. $w_{\rm{p}}(r_{\rm{p}})$s are measured by integrating the two dimensional 
-2PCF $\xi(r_{\rm{p}} , \pi)$ along the line-of-sight up to $\pi_{max}=40 h^{-1}\rm{Mpc}$. The advantage of using these measurements 
-is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, they provide very 
-accurate small scale clustering measurements [see CITE GUO 2015].
+Once the halo catalogs are populated with galaxies, the real-space positions and velocities of all mock galaxies are obtained.
+The next step is applying a redshift-space distortion transformation.
+Assuming the $\hat{z}$ axis for the direction of the RSD, the transformation $(x,y,z) \rightarrow (s_x,s_y,s_z) = (x , y ,z + v_z/cH_{0})$ is done to obtain the redshift-space coordinate of the produced mock galaxies.
 
-The Second set of measurements used in our work are the group multiplicity functions described in [CITE BERLIND 2006]. These measurements are made 
-for the three Volume limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$. 
-Group multiplicity function $g(N)$ (with units of $h^{3}\rm{Mpc}^{-3}$) is defined as the abundance of the galaxy groups as a 
+\subsection{Model Observables}
+\subsubsection{group multiplicity function}
+Group multiplicity function $g(N)$ is defined as the abundance of the galaxy groups as a 
 function of group richness (the number of galaxies in groups) per richness width, measured in bins of richness. 
-Galaxy groups in [CITE BERLIND etal] are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF]. 
-The FoF group finder places two galaxies in a group if the projected (line-of-sight) distance between the two galaxies 
-is less than a specified projected (line-of-sight) linking length in units of the mean inter-particle distance ($n_{\rm g}^{-1/3}$).
-The projected linking and the line-of-sight linking lengths are denoted by $b_{\perp}$ and $b_{\parallel}$ respectively. 
-In order to minimize the discrepancy between the groups found from the group finder and the halos in a suite of simulations, 
-[CITE BERLIND] set $b_{\perp}$ and $b_{\parallel}$ to 0.15 and 0.74 respectively.
-The measurements are accompanied by two sets of uncertainty measurements. 
-The first one is the error in $g(N)$ measured from dispersion between $g(N)$s 
-of different mock catalogs, and the second source of error is the Poisson error measured 
-from the number of groups in each richness bin. Finally, these two uncertainties are added in quadrature 
-to estimate the total error on $g(N)$ measurements.
+Galaxy groups in are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF]. 
+The FoF group finder algorithm links to galaxy $i$ and galaxy $j$ to each other, if the projected distance between the two galaxies $D_{\perp , i,j}$ is less than a specified projected linking length $b{_\perp}$, and the line-of-sight distance between the two galaxies $D_{\parallel, i,j}$ is less than a specified line-of-sight linking length $b{_\parallel}$.
+These linking lengths are measured in units of the mean inter-particle distance ($n_{\rm g}^{-1/3}$).
+In order to be consistent with the [CITE BERLIND] measurements, the linking lengths $b_{\perp}$ and $b_{\parallel}$ are set to to 0.15 and 0.74 respectively.
 
-\section{Simulation}
+After populating the dark matter halo catalogs with galaxies, we use the $\mathtt{Halotools}$ implementation of the FoF group-finder algorithm to identify the FoF groups with the mentioned linking lengths.
+Afterwards, we compute the number density of the galaxy groups in bins of richness to measure the group multiplicity function.
+Note that $g(N)$ is measured in units of $h^{3}\rm{Mpc}^{-3}$.
+\subsubsection{projected two-point correlation function}
+The projected two point correlation function $w_{\rm{p}}(r_{\rm{p}})$ can be computed by integrating the 3D redshift space 2PCF $\xi(r_{\rm{p}} , \pi)$ along the line-of-sight
+\beq
+w_{\rm{p}}(r_{\rm{p}}) = 2 \int_{0}^{\infty} d\pi \;\xi(r_{\rm{p}} , \pi)
+\eeq
+For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ [CITE CORRFUNC].
+To be consistent with the SDSS measurements described in \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
+Note that $w_{\rm{p}}(r_{\rm{p}})$ is measured in units of $h^{-1}\rm{Mpc}$.
+
+\subsection{Simulation}
+
 For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the Bolshoi-Planck high 
@@
 
+\section{Data}\label{sec:data}
+
+We focus on two sets of measurements made on the volume limited luminosity threshold main sample of galaxies in the SDSS spectroscopic survey.
+In this section, we briefly describe the measurements used in our study for finding constraints on the assembly bias parameters.
+
+\subsection{group multiplicity function}
+
+The first set of measurements consists of the galaxy number densities $n_{g}$ and the group multiplicity functions $g(N)$ described in [CITE BERLIND 2006]. These measurements are made 
+for the three Volume limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$.
+Galaxy groups in [CITE BERLIND etal] are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF].
+[CITE BERLIND ETAL] sets $b_{\perp}$ to 0.15 and $b_{\parallel}$ to 0.74 to minimize the discrepancy between the multiplicity function, projected size, and the number of FoF groups and those of the halos in a suite of simulations.
+
+The measurements are accompanied by two sets of uncertainty measurements.
+The first one is the error on $g(N)$ that stems from the dispersion between $g(N)$ measurements of different mock catalogs.
+The second source of error is the Poisson error that results from the number of groups in each richness bin.
+Finally, these two uncertainties are added in quadrature
+to estimate the total error on [CITE BERLIND ETAL] $g(N)$ measurements.
+
+\subsection{projected 2PCF}
+
+The second set consists of the number density $n_{g}$ and the projected 2PCF $w_{\rm{p}}(r_{\rm{p}})$.
+The project 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
+These measurements are accompanied by their corresponding covariance matrices constructed using 400 jackknife sub-samples of the data.
+The advantage of using these measurements is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, they provide very accurate small scale clustering measurements [see CITE GUO 2015].
+As [CITE HEARIN2015] demonstrates the satellite assembly bias $\mathcal{A}_{\rm sat}$ can have 10 $\%$ level impact on the small scale galaxy clustering.
+
+\section{Analysis and Results}
+
+We aim to constrain the parameters of the HOD model described in \ref{subsubsec:hod}, and the parameters of the assembly bias HOD model described in \ref{subsubsec:decorated}, given two sets of SDSS measurements described in \ref{sec:data}.
+We sample from the posterior probability distribution $p(\theta|d) \propto p(d|\theta).\pi(\theta)$.
+Here, $\theta$ denotes $\{ \log M_{\rm min}, \sigma_{\log M}, \log M_{0}, \alpha, \log M_{1} \}$ in the HOD modeling, and $\{ \log M_{\rm min}, \sigma_{\log M}, \log M_{0}, \alpha, \log M_{1}, \mathcal{A}_{\rm cen}, \mathcal{A}_{\rm sat}\}$ in the assembly bias HOD modeling.
+Furthermore, $d$ denotes the combination $[n_{g},g(N)]$ when the group multiplicity function is used, and $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$ when 2PCF is used.
+
+Now we need to specify the likelihood function $p(d|\theta)$. In the case where the observables are the number density and the GMF are used the negative log-likelihood is given by
+\begin{eqnarray}
+-2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} \nonumber \\ &+& \sum_{N} \frac{[ g^{\rm data}(N)-g^{\rm model}(N)]^{2}}{\sigma^{2}_{N}} \; + \; \rm{const.},
+\end{eqnarray}
+where the summation is over the group richness bins, and $\sigma_{N}$ is the uncertainty associated with the richness bin $N$.
+In the case, where the number density and 2PCF are used, the negative log-likelihood is given by
+\begin{eqnarray}
+-2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} \nonumber \\  
+&+&  \sum_{\rm p} \Delta \wpp^{\rm T}C^{-1}\Delta \wpp \; + \; \rm{const.},
+\end{eqnarray}
+where $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $C^{-1}$ is inverse of the estimate of the jackknife covariance matrix provided by [CITE GUO2015]. 
+Another important ingradient of our analysis is specification of the prior probabilities over the parameters of the two halo occupation models.
+For both model, we use uniform flat priors for all the parameters.
+
+\begin{table*}
+\begin{center}
+  \label{tab:prior}
+  \caption{{\bf Prior Specifications}: The prior probability distribution 
+  and its range for each of the parameters. 
+  All mass parameters are in unit of $h^{-1}M_\odot$}
+\begin{tabular}{@{}lllll}
+\\ \hline 
+    HOD Parameter & & Prior & & Range \\ \hline
+  $\alpha$ & & Uniform & & [0.8, 1.3] \\
+  $\sigma_{\rm \log M}$ & & Uniform & &  [0.1, 0.7] \\
+   $\log M_{0}$   & & Uniform & &  [10.0, 13.0] \\
+  $\log M_{min}$ & &   Uniform & &  [11.02, 13.02] \\
+  $\log M_{1}$ & & Uniform & & [13.0, 14.0] \\
+  $\acen$ & & Uniform & & [-1.0, 1.0] \\
+  $\asat$ & & Uniform & & [-1.0, 1.0] \\
+ \hline
+  \end{tabular}
+\end{center}
+\end{table*}
+
+For sampling from the posterior probability, we use the affine-invariant ensemble MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+
 \section{Results}

### 2016-06-20 code/diagnosis/gelman-rubin.py
cleaner version of the gelman-rubin test

@@ -1,0 +1,20 @@
+import numpy as np
+import h5py
+
+def gelman_rubin(chain):
+    ssq = np.var(chain, axis=1, ddof=1)
+    W = np.mean(ssq, axis=0)
+    xb = np.mean(chain, axis=1)
+    xbb = np.mean(xb, axis=0)
+    m = chain.shape[0]
+    n = chain.shape[1]
+    B = n / (m - 1.) * np.sum((xbb - xb)**2., axis=0)
+    var_x = (n - 1.) / n * W + 1. / n * B
+    Rhat = np.sqrt(var_x / W)
+    return Rhat
+
+if __name__=='__main__':
+   directory = "/export/bbq2/mj/chains/"
+   filename = directory+"group_mcmc_chain_Mr18.0.hdf5"
+   chain = h5py.File(filename)["mcmc"][500:2100]
+   print gelman_rubin(chain)

### 2016-06-20 text/ms.tex

@@
 
-For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the Bolshoi-Planck high 
+For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the $z=0$ Bolshoi-Planck high 
 resolution $N$-body simulation CITE[Klypin2014]. This simulation was carried out using the adaptive refinement tree code 
@@
 
+\subsection{Inference setup}
+
 We aim to constrain the parameters of the HOD model described in \ref{subsubsec:hod}, and the parameters of the assembly bias HOD model described in \ref{subsubsec:decorated}, given two sets of SDSS measurements described in \ref{sec:data}.
-We sample from the posterior probability distribution $p(\theta|d) \propto p(d|\theta).\pi(\theta)$.
-Here, $\theta$ denotes $\{ \log M_{\rm min}, \sigma_{\log M}, \log M_{0}, \alpha, \log M_{1} \}$ in the HOD modeling, and $\{ \log M_{\rm min}, \sigma_{\log M}, \log M_{0}, \alpha, \log M_{1}, \mathcal{A}_{\rm cen}, \mathcal{A}_{\rm sat}\}$ in the assembly bias HOD modeling.
-Furthermore, $d$ denotes the combination $[n_{g},g(N)]$ when the group multiplicity function is used, and $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$ when 2PCF is used.
+For the tests with group multiplicity function as observable, we use measurements with maximum absolute luminosity $M_{\rm r , max}$ of -18, -19, and -20.
+Finally, for the tests with the projected 2PCF, we use measurements with $M_{\rm r , max}$ of -18, -19, -20, and -21.
+
+We sample from the posterior probability distribution $p(\theta|d) \propto p(d|\theta) \pi(\theta)$. In the standard HOD modeling 
+\beq
+\theta = \{ \mmin, \sigmam, \mzero, \alpha, \mone \},
+\eeq
+and in the Heaviside assembly bias modeling we have 
+\beq
+\theta = \{ \mmin, \sigmam, \mzero, \alpha, \mone, \acen, \asat \},
+\eeq
+Furthermore, data (denoted by $d$) is the combination $[n_{g},g(N)]$ when GMF is used, and $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$ when 2PCF is used.
 
@@
 -2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} \nonumber \\ &+& \sum_{N} \frac{[ g^{\rm data}(N)-g^{\rm model}(N)]^{2}}{\sigma^{2}_{N}} \; + \; \rm{const.},
+\label{eq:lnlike_group}
 \end{eqnarray}
@@
 &+&  \sum_{\rm p} \Delta \wpp^{\rm T}C^{-1}\Delta \wpp \; + \; \rm{const.},
+\label{eq:lnlike_wp}
 \end{eqnarray}
 where $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $C^{-1}$ is inverse of the estimate of the jackknife covariance matrix provided by [CITE GUO2015]. 
-Another important ingradient of our analysis is specification of the prior probabilities over the parameters of the two halo occupation models.
+Another important ingredient of our analysis is specification of the prior probabilities over the parameters of the two halo occupation models.
 For both model, we use uniform flat priors for all the parameters.
+The prior ranges are specified in the Table \ref{tab:prior}.
 
@@
   and its range for each of the parameters. 
-  All mass parameters are in unit of $h^{-1}M_\odot$}
+  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
 \begin{tabular}{@{}lllll}
@@
     HOD Parameter & & Prior & & Range \\ \hline
-  $\alpha$ & & Uniform & & [0.8, 1.3] \\
-  $\sigma_{\rm \log M}$ & & Uniform & &  [0.1, 0.7] \\
-   $\log M_{0}$   & & Uniform & &  [10.0, 13.0] \\
-  $\log M_{min}$ & &   Uniform & &  [11.02, 13.02] \\
-  $\log M_{1}$ & & Uniform & & [13.0, 14.0] \\
+  $\alpha$ & & Uniform & & [0.85, 1.45] \\
+  $\sigmam$ & & Uniform & &  [0.05, 1.5] \\
+   $\mzero$   & & Uniform & &  [10.0, 14.5] \\
+  $\mmin$ & &   Uniform & &  [10.0, 14.0] \\
+  $\mone$ & & Uniform & & [11.5, 15.0] \\ 
   $\acen$ & & Uniform & & [-1.0, 1.0] \\
@@
 
-For sampling from the posterior probability, we use the affine-invariant ensemble MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+For sampling from the posterior probability, given the likelihood function (see Eqs.
+\ref{eq:lnlike_group}, \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+In particular, we run the $\mathtt{emcee}$ code with 140 walkers and we run the chains for at least 15000 iterations until the convergence of the MCMC chains is ensured.
+For testing the convergence of the chains, we perform Gelman-Rubin convergence test [CITE GELMANANDRUBIN and the other paper].
 
-\section{Results}
+\subsection{results}
+
+\subsection{model comparison}
+
+Now that we have presented constraints on the parameters of the Heaviside assembly bias HOD model and those of the standard HOD model using the group and clustering measurements of the SDSS galaxies, it is necessary to make comparison between the the two models in terms of the goodness of fit.
+There are various methods for model comparison.
+In this work we make use of two information criteria: \emph{Akaike Information Criteria} (AIC), and \emph{Bayesian Information Criteria} (BIC).
+AIC and BIC are two widely used methods for assessing the relative quality of models given a set of observations.
+
+Suppose that $\mathcal{L}_{\rm max}$ is the maximum likelihood of the data given a model, $N_{\rm par}$ is the number of parameters of a given model, and $N_{\rm data}$ is the number of data points.
+Then we have
+
+\begin{eqnarray}
+AIC&=& -2\ln \mathcal{L}_{\rm max} + 2N_{\rm par}, \\
+BIC&=& -2\ln \mathcal{L}_{\rm max} + N_{\rm par}.\ln N_{\rm data}
+\end{eqnarray}
 
@@
 
+%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%
+
 \end{document}

### 2016-06-21 code/adhoc_mcmc_group.py
turning off poisson

@@ -82,7 +82,7 @@ def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try'):
         Number of MCMC chains   
     '''
     #data and covariance matrix
-    fake_obs_icov = Data.load_covariance(Mr , pois = 'True')
+    fake_obs_icov = Data.load_covariance(Mr , pois = False)
     fake_obs = Data.load_data(Mr)
         
     # True HOD parameters
@@ -96,7 +96,7 @@ def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try'):
     prior_range[:,1] = prior_max
     
     # mcmc chain output file 
-    chain_file_name = ''.join([util.mcmc_dir(),'adhoc_group_mcmc_chain_Mr',str(Mr),'.hdf5'])
+    chain_file_name = ''.join([util.mcmc_dir(),'adhoc_group_nopoisson_mcmc_chain_Mr',str(Mr),'.hdf5'])
  
 
     if os.path.isfile(chain_file_name) and continue_chain:   

### 2016-06-21 code/mcmc_group.py

@@ -73,7 +73,7 @@ def lnPost(theta, **kwargs):
     return lp + lnlike(theta, **kwargs)
 
 
-def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try', pois = True): 
+def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try', pois = False): 
     '''
     Parameters
     -----------
@@ -83,7 +83,7 @@ def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try', pois = True):
         Number of MCMC chains   
     '''
     #data and covariance matrix
-    fake_obs_icov = Data.load_covariance(Mr , pois = 'True')
+    fake_obs_icov = Data.load_covariance(Mr , pois = False)
     fake_obs = Data.load_data(Mr)
         
     # True HOD parameters
@@ -97,7 +97,7 @@ def mcmc_mpi(Nwalkers, Niters, Mr, prior_name = 'first_try', pois = True):
     prior_range[:,1] = prior_max
     
     # mcmc chain output file 
-    chain_file_name = ''.join([util.mcmc_dir(),'group_mcmc_chain_Mr',str(Mr),'.hdf5'])
+    chain_file_name = ''.join([util.mcmc_dir(),'group_nopoisson_mcmc_chain_Mr',str(Mr),'.hdf5'])
  
 
     if os.path.isfile(chain_file_name) and continue_chain:   

### 2016-06-21 code/plot_model.py
module for paper plots

@@ -1,0 +1,318 @@
+'''
+Plotting modules
+'''
+from halotools.sim_manager import CachedHaloCatalog
+import os.path as path
+
+from Corrfunc import _countpairs
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+from halotools.empirical_models import enforce_periodicity_of_box
+from halotools.empirical_models import HodModelFactory
+from halotools.empirical_models import TrivialPhaseSpace, AssembiasZheng07Cens
+from halotools.empirical_models import AssembiasZheng07Sats , HeavisideAssembias
+from halotools.empirical_models import PrebuiltHodModelFactory
+from halotools.mock_observables import tpcf
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables import FoFGroups
+from halotools.mock_observables.pair_counters import npairs_3d
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+import matplotlib.pyplot as plt
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models import NFWPhaseSpace
+from matplotlib import lines as mlines
+
+halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+import os
+import os.path as path 
+
+import h5py
+import corner
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from matplotlib.ticker import MaxNLocator
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
[…]

### 2016-06-21 code/plot_model.py
fixed a bug in plotting models

@@ -43,29 +43,27 @@ from ChangTools.plotting import prettyplot
 from ChangTools.plotting import prettycolors
 plt.switch_backend("Agg")
 
-import hod_group.MCMC_model as hod_gmf 
-import hod.MCMC_model as hod_wp
-import biased_hod_group.MCMC_model as dec_gmf
-import biased_hod.MCMC_model as dec_wp 
+from hod_group import MCMC_model as hod_gmf 
+from hod import MCMC_model as hod_wp
+from biased_hod_group import MCMC_model as dec_gmf
+from biased_hod import MCMC_model as dec_wp 
 
 def model_predictions(filename, Mr, nburnins, nchains , obs = "wp", model = "dec"):
 
     if obs == "wp":
        if model == "dec":
           mod = dec_wp(Mr)
-       if mdoel == "hod":
+       if model == "hod":
           mod = dec_gmf(Mr)
     
     if obs == "gmf":
        if model == "dec":
           mod = dec_wp(Mr)
-       if mdoel == "hod":
+       if model == "hod":
           mod = hod_gmf(Mr)
 
-    sample = h5py.File(filename , "r")["mcmc"][nburnins:nchains].flatten()
-    npars = sample.shape[2]
-    nwalkers = sample.shape[1]
-   
+    sample = h5py.File(filename , "r")["mcmc"][nburnins:nchains]
+    sample = sample.reshape(sample.shape[0]*sample.shape[1] , sample.shape[2]) 
     model_obs = []
  
     for i in xrange(len(sample)):
@@ -310,7 +308,7 @@ if __name__=='__main__':
    directory = "/export/bbq2/mj/chains/"
    filename = "mcmc_chain_Mr19.0.hdf5"
    filename = directory+filename
-   Mr = 19.
+   Mr = 19.0
    obs , model = "wp" , "dec"
    nchains = 22000
    nburnins = 21998

### 2016-06-22 code/plot_model.py
updating posterior model prediction plots

@@ -3,7 +3,7 @@ Plotting modules
 '''
 from halotools.sim_manager import CachedHaloCatalog
 import os.path as path
-
+import util as ut
 from Corrfunc import _countpairs
 from Corrfunc.utils import read_catalog
 from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
@@ -26,6 +26,13 @@ from ChangTools.plotting import prettycolors
 from Corrfunc.utils import read_catalog
 from halotools.empirical_models import NFWPhaseSpace
 from matplotlib import lines as mlines
+import matplotlib.pyplot as plt
+from matplotlib import lines as mlines
+from matplotlib import gridspec
+from scipy.stats import norm
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
 
 halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
 import os
@@ -47,18 +54,19 @@ from hod_group import MCMC_model as hod_gmf
 from hod import MCMC_model as hod_wp
 from biased_hod_group import MCMC_model as dec_gmf
 from biased_hod import MCMC_model as dec_wp 
-
+import data
+import data_group
 def model_predictions(filename, Mr, nburnins, nchains , obs = "wp", model = "dec"):
 
     if obs == "wp":
        if model == "dec":
           mod = dec_wp(Mr)
        if model == "hod":
-          mod = dec_gmf(Mr)
+          mod = hod_wp(Mr)
     
     if obs == "gmf":
        if model == "dec":
-          mod = dec_wp(Mr)
+          mod = dec_gmf(Mr)
        if model == "hod":
           mod = hod_gmf(Mr)
 
@@ -68,8 +76,8 @@ def model_predictions(filename, Mr, nburnins, nchains , obs = "wp", model = "dec
  
     for i in xrange(len(sample)):
         print i
-        model_obs.append(mod._sum_stat(sample[i] , prior_range = None))
-    np.savetxt(obs+"_"+model+"_"+str(Mr)+".dat" , np.array(model_obs)) 
[…]

### 2016-06-22 code/plot_occupation.py
expected occupation plots

@@ -1,0 +1,233 @@
+'''
+Plotting modules
+'''
+from halotools.sim_manager import CachedHaloCatalog
+import os.path as path
+
+from Corrfunc import _countpairs
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+from halotools.empirical_models import enforce_periodicity_of_box
+from halotools.empirical_models import HodModelFactory
+from halotools.empirical_models import TrivialPhaseSpace, AssembiasZheng07Cens
+from halotools.empirical_models import AssembiasZheng07Sats , HeavisideAssembias
+from halotools.empirical_models import PrebuiltHodModelFactory
+from halotools.mock_observables import tpcf
+from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
+from halotools.mock_observables import FoFGroups
+from halotools.mock_observables.pair_counters import npairs_3d
+from halotools.mock_observables.catalog_analysis_helpers import return_xyz_formatted_array
+import matplotlib.pyplot as plt
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models import NFWPhaseSpace
+from matplotlib import lines as mlines
+
+halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+import os
+import os.path as path 
+
+import h5py
+import corner
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from matplotlib.ticker import MaxNLocator
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+plt.switch_backend("Agg")
+
+from hod_group import MCMC_model as hod_gmf 
[…]

### 2016-06-23 code/plot_occupation.py
tweaking paper occupation figures

@@ -27,10 +27,12 @@ from Corrfunc.utils import read_catalog
 from halotools.empirical_models import NFWPhaseSpace
 from matplotlib import lines as mlines
 
+from matplotlib import lines as mlines
+from matplotlib import gridspec
 halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
 import os
 import os.path as path 
-
+import util as ut
 import h5py
 import corner
 import numpy as np
@@ -69,10 +71,10 @@ def occupation_predictions(filename, Mr, nburnins, nchains , obs = "wp", model =
         
     	ncen_old = []
     	ncen_young = []
-        ncen_all = []
+        #ncen_all = []
         nsat_old = []
    	nsat_young = []
-        nsat_all = []
+        #nsat_all = []
         for i in xrange(len(sample)):
          
           print i
@@ -85,19 +87,19 @@ def occupation_predictions(filename, Mr, nburnins, nchains , obs = "wp", model =
           mod.param_dict['mean_occupation_centrals_assembias_param1'] = sample[i][5]
           mod.param_dict['mean_occupation_satellites_assembias_param1'] = sample[i][6]
           
-          ncen_old.append(model.mean_occupation_centrals(prim_haloprop = mass, sec_haloprop_percentile=0))
-          ncen_young.append(model.mean_occupation_centrals(prim_haloprop = mass, sec_haloprop_percentile=1))
-          ncen_all.append(model.mean_occupation_centrals(mass))
-          nsat_old.append(model.mean_occupation_satellites(prim_haloprop = mass, sec_haloprop_percentile=0))
-          nsat_young.append(model.mean_occupation_satellites(prim_haloprop = mass, sec_haloprop_percentile=1))
-          nsat_all.append(model.mean_occupation_satellites(mass))
+          ncen_old.append(mod.mean_occupation_centrals(prim_haloprop = mass, sec_haloprop_percentile=0))
+          ncen_young.append(mod.mean_occupation_centrals(prim_haloprop = mass, sec_haloprop_percentile=1))
[…]

### 2016-06-25 code/plot_model.py
finalizing the plot formats

@@ -1,5 +1,11 @@
 '''
-Plotting modules
+Genrating posterior model prediction figures for the paper
+
+author: MJ
+
+pretty_colors[1] for decorated model and 
+pretty_colors[5] for standard hod models
+
 '''
 from halotools.sim_manager import CachedHaloCatalog
 import os.path as path
@@ -157,8 +163,8 @@ def plot_model_prediction(obs = "wp", model= "dec", clotter = True):
         a, b, c, d, e = np.percentile(file18, [2.5, 16, 50, 84, 97.5], axis=0) 
         
         print a.shape
-        ax.fill_between(rbin18, a, e, color=pretty_colors[5], alpha=0.4, edgecolor="none") 
-        ax.fill_between(rbin18, b, d, color=pretty_colors[5], alpha=0.7, edgecolor="none")
+        ax.fill_between(rbin18, a, e, color=pretty_colors[1], alpha=0.4, edgecolor="none") 
+        ax.fill_between(rbin18, b, d, color=pretty_colors[1], alpha=0.7, edgecolor="none")
 
         ax.errorbar(rbin18, data18, yerr=err18, fmt="o", color='k', markersize=0, lw=0, capsize=3, elinewidth=1.5)
         ax.scatter(rbin18, data18, c='k', s=10, lw=0)
@@ -178,15 +184,15 @@ def plot_model_prediction(obs = "wp", model= "dec", clotter = True):
           ax.set_ylabel(r'$g(N) \; [\mathrm{Mpc}^{-3}\; h^{3}]$', fontsize=27)
           ax.set_yscale('log') 
           ax.set_xscale('log')
-          ax.set_xlim([1., 99.])
+          ax.set_xlim([1.5, 99.])
           ax.set_ylim([10**-8., 10**-2.])
-          plt.xticks(fontsize=20)
+          plt.xticks([2 , 10, 50],[2,10,50],fontsize=20)
           plt.yticks(fontsize=20)
           ax.text(20, .002, r'$M_{r}<-18$', fontsize=25) 
         ax = plt.subplot(gs[1])
         a, b, c, d, e = np.percentile(file19, [2.5, 16, 50, 84, 97.5], axis=0) 
-        ax.fill_between(rbin19, a, e, color=pretty_colors[5], alpha=0.4, edgecolor="none") 
-        ax.fill_between(rbin19, b, d, color=pretty_colors[5], alpha=0.7, edgecolor="none")
[…]

### 2016-06-27 code/plot_model.py
added model comparison stuff

@@ -43,7 +43,7 @@ from ChangTools.plotting import prettycolors
 halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
 import os
 import os.path as path 
-
+from numpy.linalg import solve
 import h5py
 import corner
 import numpy as np
@@ -398,8 +398,8 @@ def plot_wp_prediction(obs = "wp", model= "dec", clotter = True):
         ax = plt.subplot(gs[0,2]) #Mr19.
 
         a, b, c, d, e = np.percentile(file19, [2.5, 16, 50, 84, 97.5], axis=0) 
-        ax.fill_between(rbin19, a, e, color=pretty_colors[5], alpha=0.4, edgecolor="none") 
-        ax.fill_between(rbin19, b, d, color=pretty_colors[5], alpha=0.7, edgecolor="none")
+        ax.fill_between(rbin19, a, e, color=pretty_colors[1], alpha=0.4, edgecolor="none") 
+        ax.fill_between(rbin19, b, d, color=pretty_colors[1], alpha=0.7, edgecolor="none")
         ax.errorbar(rbin19, data19, yerr=err19, fmt="o", color='k', markersize=0, lw=0, capsize=3, elinewidth=1.5)
         ax.scatter(rbin19, data19, c='k', s=10, lw=0)
         if obs == "wp":
@@ -427,8 +427,8 @@ def plot_wp_prediction(obs = "wp", model= "dec", clotter = True):
         ax = plt.subplot(gs[1,0]) #Mr19.5
 
         a, b, c, d, e = np.percentile(file195, [2.5, 16, 50, 84, 97.5], axis=0) 
-        ax.fill_between(rbin195, a, e, color=pretty_colors[5], alpha=0.4, edgecolor="none") 
-        ax.fill_between(rbin195, b, d, color=pretty_colors[5], alpha=0.7, edgecolor="none")
+        ax.fill_between(rbin195, a, e, color=pretty_colors[1], alpha=0.4, edgecolor="none") 
+        ax.fill_between(rbin195, b, d, color=pretty_colors[1], alpha=0.7, edgecolor="none")
         ax.errorbar(rbin195, data195, yerr=err195, fmt="o", color='k', markersize=0, lw=0, capsize=3, elinewidth=1.5)
         ax.scatter(rbin195, data195, c='k', s=10, lw=0)
         if obs == "wp":
[…]

### 2016-06-27 code/tests/overlay.py
hack for merging postrior plots

@@ -1,0 +1,53 @@
+import corner
+import matplotlib.pyplot as plt
+import numpy as np
+
+ndim, nsamples = 3, 50000
+
+# Generate some fake data.
+np.random.seed(42)
+data1 = np.random.randn(ndim * 4 * nsamples // 5).reshape([4 * nsamples // 5, ndim])
+data2 = (4*np.random.rand(ndim)[None, :] + np.random.randn(ndim * nsamples // 5).reshape([nsamples // 5, ndim]))
+data = np.vstack([data1, data2])
+
+import matplotlib.lines as mlines
+
+#blue_line = mlines.Line2D([], [], color='blue', label='SGM')
+#red_line = mlines.Line2D([], [], color='red', label='GMM')
+
+data2 = data.copy()
+#data2[:,2] = data2[:,2] + 10.
+data[:,2] = data[:,2] * 0.
+print data[:,:2] - data2[:,:2]
+#plt.legend(handles=[blue_line,red_line], bbox_to_anchor=(0., 1.0, 1., .0), loc=4)
+
+prior_range = [[-4. , 10],[-3.,3.],[-3.,3.]]
+
+# Plot it.
+figure = corner.corner(data, labels=[r"$x$", r"$y$", r"$\log \alpha$", r"$\Gamma \, [\mathrm{parsec}]$"],
+                       title_kwargs={"fontsize": 12}, 
+                       range=prior_range,
+                       quantiles=[0.16,0.5,0.84],
+                       show_titles=False,
+                       title_args={"fontsize": 12},
+                       plot_datapoints=False,
+                       fill_contours=True,
+                       levels=[0.68, 0.95],
+                       color='#ee6a50',
+                       bins=50,
+                       smooth=1.0)
+
+
+corner.corner(data2, labels=[r"$x$", r"$y$", r"$\log \alpha$", r"$\Gamma \, [\mathrm{parsec}]$"],
+                       title_kwargs={"fontsize": 12}, 
+                       range=prior_range,
+                       quantiles=[0.16,0.5,0.84],
+                       show_titles=False,
+                       title_args={"fontsize": 12},
+                       plot_datapoints=False,
+                       fill_contours=True,
+                       levels=[0.68, 0.95],
+                       color='blue',
+                       bins=50,
+                       smooth=1.0 , fig = figure)
+plt.show()

### 2016-06-28 code/diagnosis/plotter.py
AB and HOD posterior pdfs on the same plots

@@ -115,7 +115,7 @@ def plot_time_mcmc(Nwalkers, Nchains, filename):
     for i in xrange(npars):
         axes[i].plot(sample[:, :, i], color="b", alpha=.4 , lw = .5)
 	axes[i].yaxis.set_major_locator(MaxNLocator(5))
-        #axes[i].set_ylim([plot_range[i,0], plot_range[i,1]])
+        axes[i].set_ylim([prior_min[i], prior_max[i]])
         axes[i].set_xlim(0, Nchains)
         #axes[i].set_ylabel(labels[i], fontsize=25)
 
@@ -125,7 +125,83 @@ def plot_time_mcmc(Nwalkers, Nchains, filename):
     plt.savefig(fig_file)
     plt.close()
 
-def plot_corner_mcmc(Nchains , Nburns, Mr , filename):
+def plot_overlay_corner(Nchains1 , Nchains2, Nburns1, Nburns2, Mr , style , filename1, filename2):
+
+
+    sample1 = h5py.File(filename1 , "r")["mcmc"]
+    sample1 = sample1[Nburns1:Nchains1, : , :]
+    sample1 = sample1.reshape(sample1.shape[0]*sample1.shape[1] , sample1.shape[2])
+   
+    sample2 = h5py.File(filename2 , "r")["mcmc"]
+    sample2 = sample2[Nburns2:Nchains2, : , :]
+    sample2 = sample2.reshape(sample2.shape[0]*sample2.shape[1] , sample2.shape[2])
+
+    sample3 = np.zeros((sample2.shape[0] , sample1.shape[1]))
+    sample3[:,0:5] = sample2
+    sample3[:,5:7] += 110 
+    prior_range = np.zeros((len(prior_min),2))
+    prior_range[:,0] = np.array(prior_min)
+    prior_range[:,1] = np.array(prior_max) 
+    prior_range2 = prior_range.copy()
+    prior_range2[5,0] = 100
+    prior_range2[5,1] = 120
+    prior_range2[6,0] = 100
+    prior_range2[6,1] = 120
+    
+    fig = corner.corner(
+            sample3,
+            labels=[
+                r'$\log\;\mathcal{M}_{0}}$',
+                r'$\sigma_\mathtt{log\;M}}$',
+                r'$\log\;\mathcal{M}_\mathtt{min}}$',
+                r'$\alpha$',
+                r'$\log\;\mathcal{M}_{1}}$',
+                r'$\mathcal{A}_{\rm cen}}$',
[…]

### 2016-06-28 code/diagnosis/plotter.py
tweaked the posterior plots and pushing the posteriors

@@ -127,6 +127,9 @@ def plot_time_mcmc(Nwalkers, Nchains, filename):
 
 def plot_overlay_corner(Nchains1 , Nchains2, Nburns1, Nburns2, Mr , style , filename1, filename2):
 
+    from truth import truth
+
+    
 
     sample1 = h5py.File(filename1 , "r")["mcmc"]
     sample1 = sample1[Nburns1:Nchains1, : , :]
@@ -166,7 +169,7 @@ def plot_overlay_corner(Nchains1 , Nchains2, Nburns1, Nburns2, Mr , style , file
             plot_datapoints=False,
             fill_contours=True,
             levels=[0.68, 0.95],
-            color='darkorchid',
+            color='#FF7F0E' ,
             scale_hist = False,
             bins=20,
             smooth = 1.)
@@ -189,10 +192,18 @@ def plot_overlay_corner(Nchains1 , Nchains2, Nburns1, Nburns2, Mr , style , file
             plot_datapoints=False,
             fill_contours=True,
             levels=[0.68, 0.95],
-            color='darkcyan',
+            color = '#1F77B4',
             scale_hist = False,
             bins=20,
             smooth=1. , fig = fig)
+ 
+    import matplotlib.lines as mlines
+
+    blue_line = mlines.Line2D([], [], color='#1F77B4' , label=r'$Heaviside \; \; AB$')
+    red_line = mlines.Line2D([], [], color='#FF7F0E' , label=r'$Standard \; \; HOD$')
+
+    #plt.legend(handles=[blue_line,red_line], bbox_to_anchor=(0., 2.0, 2., .0), loc= 5 )
+
 
     fig_name = ''.join(['post',
          str(Mr),str(style),  
@@ -463,14 +474,14 @@ if __name__=='__main__':
    #filename = "Mr19.0-f.hdf5"
    #filename = "Mr20.0-group.hdf5"
 
-   filename1 = dire+"mcmc_chain_Mr18.0.hdf5"
-   filename2 = dire+"adhoc_mcmc_chain_Mr18.0.hdf5"
+   filename1 = dire+"group_mcmc_chain_Mr20.0.hdf5"
+   filename2 = dire+"adhoc_group_mcmc_chain_Mr20.0.hdf5"
 
-   Nchains1 , Nburns1 = 6500 , 4500
-   Nchains2 , Nburns2 = 2500 , 500
[…]

### 2016-06-28 text/ms.tex
more text

@@
-\documentclass[12pt, preprint]{aastex}
+%%\documentclass[12pt, preprint]{aastex}
+\documentclass[12pt, preprint]{emulateapj}
 \usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 and the occupation of the satellite galaxies follows a Poisson distribution.
-The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the folllowing equations
+The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the following equations
 \begin{eqnarray}
@@
 \beq
-\theta = \{ \mmin, \sigmam, \mzero, \alpha, \mone \},
+\theta = \{ \mmin, \; \sigmam, \; \mzero, \; \alpha, \; \mone \},
 \eeq
@@
 \beq
-\theta = \{ \mmin, \sigmam, \mzero, \alpha, \mone, \acen, \asat \},
+\theta = \{ \mmin, \; \sigmam, \; \mzero, \; \alpha, \; \mone, \; \acen, \; \asat \},
 \eeq
@@
 
+\begin{table*}
+\begin{center}
+  \label{tab:prior}
+  \caption{{\bf Constraints}: The prior probability distribution 
+  and its range for each of the parameters. 
+  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
+\begin{tabular}{@{}lllllllllllllllllllllllll}
+\\ \hline 
+    Model & & Observables & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
+  \\
+  Standard HOD & & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+   Heaviside-AB & & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $-$ & $-$ \\ \\
+
+Standard HOD & & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ \\ \\
+
+      Heaviside-AB & & $\gmf$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+       Heaviside-AB & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+         Heaviside-AB & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+           Heaviside-AB & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+             Heaviside-AB & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Heaviside-AB & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Standard HOD & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
+Heaviside-AB & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\
+
+ \hline
+  \end{tabular}
+\end{center}
+\end{table*}
+
 For sampling from the posterior probability, given the likelihood function (see Eqs.
@@
 
-Now that we have presented constraints on the parameters of the Heaviside assembly bias HOD model and those of the standard HOD model using the group and clustering measurements of the SDSS galaxies, it is necessary to make comparison between the the two models in terms of the goodness of fit.
+Now that we have presented constraints on the parameters of the Heaviside assembly bias HOD model and those found from the standard HOD model using the group and clustering measurements of the SDSS galaxies, it is necessary to make comparison between the the two models in terms of the goodness of fit.
+Evidently, the Heaviside Assembly bias model has more complexity for modeling the halo occupation.
+The question that arises is whether this higher level of model complexity is more preferable by the group statistics and the clustering data used in this study.
+
 There are various methods for model comparison.
-In this work we make use of two information criteria: \emph{Akaike Information Criteria} (AIC), and \emph{Bayesian Information Criteria} (BIC).
+In this work we make use of two model comparison criteria: \emph{Akaike Information Criterion} (AIC, see CITE ...
+), and \emph{Bayesian Information Criteria} (BIC, see CITE ....).
 AIC and BIC are two widely used methods for assessing the relative quality of models given a set of observations.
-
 Suppose that $\mathcal{L}_{\rm max}$ is the maximum likelihood of the data given a model, $N_{\rm par}$ is the number of parameters of a given model, and $N_{\rm data}$ is the number of data points.
@@
 \begin{eqnarray}
-AIC&=& -2\ln \mathcal{L}_{\rm max} + 2N_{\rm par}, \\
-BIC&=& -2\ln \mathcal{L}_{\rm max} + N_{\rm par}.\ln N_{\rm data}
+AIC&=& -2\;\ln \mathcal{L}_{\rm max} + 2N_{\rm par} + 2\;\frac{N_{\rm par}(N_{\rm par}+1)}{N_{\rm data}-N_{\rm par}-1} \; , \label{eq:aic}\\
+BIC&=& -2\;\ln \mathcal{L}_{\rm max} + N_{\rm par}\;\ln N_{\rm data} \; . \label{eq:bic}
 \end{eqnarray}
+Models that deliver lower values of information criteria are more favorable.
+In Eqs.
+(\ref{eq:aic}) and (\ref{eq:bic}) $N_{\rm par}$ is 5 when the standard HOD model is used, and 7 when the Heaviside assembly bias model is used.
+When the observables are $\ngal$ and $\wpp$, $N_{\rm data}$ is 13 for all luminosity thresholds, and when the observables are $\ngal$ and $\gmf$, $N_{\rm data}$ is 16 for the $\mr < -18$ luminosity threshold, 23 for the $\mr < -19$ luminosity threshold, and 25 for the $\mr < -20$ luminosity threshold.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-Mr18-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post18_0gmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-Mr19-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post19_0gmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-Mr20-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post20_0gmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-Mr18-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post18_0wp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-Mr19-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post19_0wp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-Mr20-posterior 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{post20_0wp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-abhod-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_model_decgmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-hod-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_model_hodgmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-ncen
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abhod_ncengmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-nsat
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abhod_nsatgmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-all
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abvshod_gmf.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-abhod-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_model_decwp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-hod-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_model_hodwp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-ncen
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abhod_ncenwp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-nsat
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abhod_nsatwp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-all
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{paper_abvshod_wp.pdf}
+\caption{hello world}
+\label{fig:abc_converge}
+\end{center}
+\end{figure*}
+\section*{Acknowledgments}
+We would like to thank Michael R. Blanton,  
+Boris Leidstadt, Geoffrey~S.~Ryan, and the Blanton-Hogg group meeting for insightful discussions. MV was supported by NSF grant AST-1517237. DWH was supported 
+by NSF (grants IIS-1124794 and AST-1517237), NASA (grant NNX12AI50G), and the Moore-Sloan 
+Data Science Environment at NYU. Computations 
+were performed using computational resources at NYU-HPC. We thank Shenglong Wang, the 
+administrator of NYU-HPC computational facility, for his consistent and continuous support 
+throughout the development of this project. We also thanks Dan Foreman-Mackey for providing some of the computational resources at the early stages of this work.
+
 \end{document}

### 2016-06-29 text/ms.tex
done with all the plots and figures

@@
 %%\documentclass[12pt, preprint]{aastex}
-\documentclass[12pt, preprint]{emulateapj}
+\documentclass[14pt, preprint]{emulateapj}
 \usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
   and its range for each of the parameters. 
-  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
+  All mass parameters are in unit of $h^{-1}M_\odot$. The parameters marked by $*$ are only used in the Heaviside Assembly bias modeling.}
 \begin{tabular}{@{}lllll}
 \\ \hline 
-    HOD Parameter & & Prior & & Range \\ \hline
+    Parameter & & Prior & & Range \\ \hline
   $\alpha$ & & Uniform & & [0.85, 1.45] \\
@@
   $\mone$ & & Uniform & & [11.5, 15.0] \\ 
-  $\acen$ & & Uniform & & [-1.0, 1.0] \\
-  $\asat$ & & Uniform & & [-1.0, 1.0] \\
+  $\acen^{*}$ & & Uniform & & [-1.0, 1.0] \\
+  $\asat^{*}$ & & Uniform & & [-1.0, 1.0] \\
  \hline
@@
 \\ \hline 
-    Model & & Observables & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
+    Model & Data & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
   \\
-  Standard HOD & & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-   Heaviside-AB & & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $-$ & $-$ \\ \\
+  HOD & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ & 5.55/1 & 21.55 & 19.42\\ \\
 
-Standard HOD & & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ \\ \\
+  AB & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $0.13^{+0.63}_{-0.75}$ & $-0.01^{+0.60}_{-0.59}$ & 6.46/1 & 34.46 & 25.87\\ \\
 
-      Heaviside-AB & & $\gmf$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-       Heaviside-AB & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-         Heaviside-AB & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-           Heaviside-AB & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-             Heaviside-AB & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Heaviside-AB & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Standard HOD & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
-Heaviside-AB & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\
+HOD & $\gmf$, $\bar{n}$ & 19 & $11.87^{+0.32}_{-0.23}$ &  $0.70^{+0.53}_{-0.47}$ & $10.93^{+0.74}_{-0.65}$ & $0.99^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ & 5.19/1 & 18.72 & 20.87\\ \\
+
+AB & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $0.13^{+0.62}_{-0.73}$ & $-0.03^{+0.63}_{-0.59}$ & 6.66/1 & 28.13 & 28.61\\ \\
+
+HOD  & $\gmf$, $\bar{n}$ & 20 & $12.16^{+0.36}_{-0.20}$ &  $0.58^{+0.50}_{-0.36}$ & $10.94^{+0.80}_{-0.66}$ & $0.98^{+0.09}_{-0.08}$ &  $13.07^{+0.07}_{-0.06}$ & $-$ & $-$ & 5.16/1 & 18.32 & 21.26\\ \\
+
+AB  & $\gmf$, $\bar{n}$ & 20 & $12.14^{+0.34}_{-0.19}$ &  $0.56^{+0.47}_{-0.35}$ & $10.95^{+0.72}_{-0.64}$ & $0.96^{+0.10}_{-0.07}$ &  $13.08^{+0.07}_{-0.06}$ & $0.04^{+0.68}_{-0.70}$ & $-0.04^{+0.63}_{-0.58}$ & 6.04/1 & 26.63 & 28.57\\ \\
+
+%%%%%%%wp%%%%%
+
+HOD  & $\wpp$, $\bar{n}$ & 18 & $11.46^{+0.16}_{-0.17}$ &  $1.11^{+0.28}_{-0.47}$ & $10.85^{+0.74}_{-0.59}$ & $1.03^{+0.05}_{-0.06}$ &  $12.54^{+0.10}_{-0.10}$ & $-$ & $-$ & 31.72/13 & 50.29 & 44.55\\ \\
+
+AB & $\wpp$, $\bar{n}$ & 18 & $11.44^{+0.15}_{-0.15}$ &  $1.20^{+0.21}_{-0.35}$ & $10.91^{+0.79}_{-0.64}$ & $1.02^{+0.06}_{-0.06}$ &  $12.61^{+0.11}_{-0.11}$ & $-0.82^{+0.27}_{-0.14}$ & $0.19^{+0.67}_{-0.73}$ & 31.81/13 & .55 & 19.42 \\ \\
+
+HOD & $\wpp$, $\bar{n}$ & 18.5 & $11.64^{+0.23}_{-0.24}$ &  $0.89^{+0.43}_{-0.55}$ & $10.75^{+0.65}_{-0.51}$ & $1.06^{+0.05}_{-0.05}$ &  $12.72^{+0.09}_{-0.08}$ & $-$ & $0.37^{+0.44}_{-0.52}$ & 18.11/13 & 36.69 & 30.94\\ \\
+
+AB & $\wpp$, $\bar{n}$ & 18.5 & $11.59^{+0.24}_{-0.21}$ &  $0.85^{+0.44}_{-0.54}$ & $10.77^{+0.63}_{-0.52}$ & $1.06^{+0.05}_{-0.06}$ &  $12.78^{+0.10}_{-0.10}$ & $-0.14^{+0.69}_{-0.56}$ & $0.37^{+0.44}_{-0.52}$ & 19.53/13 & 55.93 & 37.48\\ \\
+
+HOD & $\wpp$, $\bar{n}$ & 19 & $11.84^{+0.28}_{-0.27}$ &  $0.89^{+0.41}_{-0.51}$ & $10.79^{+0.65}_{-0.54}$ & $1.08^{+0.04}_{-0.04}$ &  $12.89^{+0.09}_{-0.09}$ & $-$ & $-$ & 24.20/13 & 42.77 & 37.03\\ \\
+
+AB & $\wpp$, $\bar{n}$ & 19 & $11.78^{+0.30}_{-0.24}$ &  $0.81^{+0.48}_{-0.51}$ & $10.77^{+0.66}_{-0.53}$ & $1.07^{+0.04}_{-0.05}$ &  $12.95^{+0.10}_{-0.10}$ & $0.15^{+0.52}_{-0.61}$ & $0.52^{+0.33}_{-0.44}$ & 22.80/13 & 59.20 & 40.75\\ \\
+
+HOD & $\wpp$, $\bar{n}$ & 19.5 & $11.85^{+0.31}_{-0.19}$ &  $0.66^{+0.46}_{-0.40}$ & $10.88^{+0.67}_{-0.59}$ & $1.13^{+0.04}_{-0.04}$ &  $13.07^{+0.07}_{-0.07}$ & $-$ & $-$ & 15.89/13 & 34.46 & 28.72\\ \\
+
+AB & $\wpp$, $\bar{n}$ & 19.5 & $11.82^{+0.38}_{-0.18}$ &  $0.63^{+0.55}_{-0.40}$ & $10.83^{+0.74}_{-0.57}$ & $1.10^{+0.04}_{-0.05}$ &  $13.07^{+0.08}_{-0.08}$ & $0.35^{+0.40}_{-0.52}$ & $0.03^{+0.59}_{-0.41}$ & 23.17/13 & 37.17 & 41.12\\ \\
+
+HOD & $\wpp$, $\bar{n}$ & 20 & $11.99^{+0.15}_{-0.08}$ &  $0.36^{+0.28}_{-0.21}$ & $11.05^{+0.76}_{-0.71}$ & $1.17^{+0.04}_{-0.04}$ &  $13.34^{+0.07}_{-0.07}$ & $-$ & $-$ & 18.71/13 & 37.28 & 31.54\\ \\
+
+AB & $\wpp$, $\bar{n}$ & 20 & $12.13^{+0.39}_{-0.18}$ &  $0.65^{+0.47}_{-0.38}$ & $11.14^{+0.80}_{-0.77}$ & $1.11^{+0.06}_{-0.06}$ &  $13.31^{+0.09}_{-0.09}$ & $0.71^{+0.21}_{-0.41}$ & $0.02^{+0.49}_{-0.33}$ & 15.22/13 & 51.62 & 33.17\\ \\
 

### 2016-06-30 text/ms.tex
done with captions + fancier font

@@
 \documentclass[14pt, preprint]{emulateapj}
+\usepackage{microtype}
 \usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 \title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
-\author{Mohammadjavad Vakili , others}
-
+\author{Mohammadjavad Vakili \altaffilmark{1,$\dagger$}, David W. Hogg, ChangHoon~Hahn, Unspecified contributors}
+\altaffiltext{$\dagger$}{\url{mjvakili@nyu.edu}}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, 
+                 Department of Physics, New York University, 4 Washington Pl., New York, NY} 
 \begin{abstract}
@@
 written as $P(N_g|M_h,\{x\})=P(N_g|M_h)$ where $\{x\}$ is the set of all 
-possible halo properties beyond mass $M_{h}$.
+possible halo properties beyond mass $M_{h}$. HOD provides an analytical prescription for the
 
-Despite this very simplifying assumption, the galaxy-halo connection models such as HOD and CLF
-have been widely and successfully used in modeling the measurements of a wide range of the 
-statistical properties of galaxies such as . However, the assumption that the statistical 
+Despite this very simplifying assumption, the galaxy-halo connection models such as HOD and CLF have been widely and successfully used in modeling the measurements of a wide range of the statistical properties of galaxies such as .
+However, the assumption that the statistical
 distribution of galaxies can be determined by halo mass is not a derived characteristic of 
@@
 The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations [CITE MORE].
-We refer the readers to [CITE HEARIN 15] and \url{http://halotools.readthedocs.io} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+We refer the readers to [CITE HEARIN 15] for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
 
@@
 \beq
-w_{\rm{p}}(r_{\rm{p}}) = 2 \int_{0}^{\infty} d\pi \;\xi(r_{\rm{p}} , \pi)
+w_{\rm{p}}(r_{\rm{p}}) = 2 \int_{0}^{\pi_{max}} d\pi \;\xi(r_{\rm{p}} , \pi)
 \eeq
@@
 \includegraphics[width=\textwidth]{post18_0gmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{We present the constraints on the Heaviside assembly bias HOD model parameters (blue) and the standard HOD model parameters (yellow) obtained from our analysis using $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -18$.
+The diagonal panels plot the marginalized posterior distribution of each parameter with vertical dashed lines marking the $50\%$ quantile and of the distribution.
+The off-diagonal panels plot the degeneracies between parameter pairs.
+The range of each panel corresponds to the range of our prior choice.
+The parameters $\acen$ and $\asat$ are only defined for the Assembly bias model.
+For both models, the parameter $\sigmam$ remains unconstrained.
+In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
+The parameter $\alpha$ does not have a  lower bound constraint in both models.
+The constraints on the parameters $\mzero$, $\mmin$, $\alpha$, $\mone$ found from the two models are in strong agreement.}
+\label{fig:post_gmf_18}
 \end{center}
@@
 \includegraphics[width=\textwidth]{post19_0gmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{Same as Figure \ref{fig:post_gmf_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -19$.
+Again, For both models, the parameter $\sigmam$ remains unconstrained.
+In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
+The  marginalized posterior pdf over the parameter $\alpha$ found from the standard HOD model is peaked at a slightly higher value of $\alpha$ than the one found from the assembly bias HOD model.
+The constraints on the parameters $\mzero$, $\mmin$, and $\mone$ found from the two models are in strong agreement.}
+\label{fig:post_gmf_19}
 \end{center}
@@
 \includegraphics[width=\textwidth]{post20_0gmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{Same as Figure \ref{fig:post_gmf_20} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -20$.
+In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
+The  marginalized posterior pdf over the parameter $\alpha$ found from the standard HOD model is peaked at a slightly higher value of $\alpha$ than the one found from the assembly bias HOD model.
+The constraints on the parameters $\sigmam$, $\mzero$, $\mmin$, and $\mone$ found from the two models are in strong agreement.}
+\label{fig:post_gmf_20}
 \end{center}
@@
 \includegraphics[width=\textwidth]{post18_0wp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{We present the constraints on the Heaviside assembly bias HOD model parameters (blue) and the standard HOD model parameters (yellow) obtained from our analysis using $\bar{n}$ and $\wpp$ measurements of galaxies with $\mr < -18$.
+The diagonal panels plot the marginalized posterior distribution of each parameter with vertical dashed lines marking the $50\%$ quantile and of the distribution.
+The off-diagonal panels plot the degeneracies between parameter pairs.
+The range of each panel corresponds to the range of our prior choice.
+The parameters $\acen$ and $\asat$ are only defined for the Assembly bias model.
+For both models, the parameter $\sigmam$ remains unconstrained.
+In The assembly bias model, $\asat$ remains largely unconstrained.
+The constraint on the parameter $\acen$ however, indicates that negative values of this parameter are strongly favored.
+Specifically the best-fit value of $\acen$ is -0.82 with its 68$\%$ confidence interval being less than -0.55.
+The constraints on $\mzero$ and $\mmin$ found from the two models strongly agree.
+The constraints on $\alpha$ and $\mone$ found from the two model in overall agreement with a slightly higher value of $\alpha$ and a slightly lower value of $\mone$ in the standard HOD model.}
+\label{fig:post_wp_18}
 \end{center}
@@
 \includegraphics[width=\textwidth]{post19_0wp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{Same as Figure \ref{fig:post_wp_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -19$.
+Once again, the parameter $\sigmam$ remains unconstrained.
+$\acen$ is not constrained in the assembly bias model, but constraints on $\asat$ show that positive values of $\asat$ are strongly favored.
+The best-fit value of $\asat$ is 0.52 and its 68$\%$ confidence interval is larger than 0.08.
+The constraints on $\mzero$, $\mmin$, $\alpha$, and $\mone$ found from the two models are in good agreement, with $\alpha$ being slightly higher and $\mone$ being slightly lower in the standard HOD model.}
+\label{fig:post_wp_19}
 \end{center}
@@
 \includegraphics[width=\textwidth]{post20_0wp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\caption{Same as Figure \ref{fig:post_wp_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -20$.
+For this sample of galaxies, the parameter $\sigmam$ is better constrained by the two models, with the constraints coming from the standard HOD model being tighter.
+$\asat$ is not constrained in the assembly bias model and is consistent with zero, but constraints on $\acen$ show that positive values of $\acen$ are strongly favored.
+The best-fit value of $\acen$ is 0.71 and its 68$\%$ confidence interval is larger than 0.30.
+The constraints on $\mzero$ and $\mone$ found from the two models are in good agreement.
+There is some discrepancy between the constraints on $\mmin$ and $\alpha$ from the standard HOD model and  the ones from the HOD model with assembly bias.
+In the standard HOD model, the constraints on $\alpha$ are slightly narrower and favor larger values of $\alpha$.
+The best-fit and the 1-sigma uncertainties of $\alpha$ are 1.17$^{+0.04}_{-0.04}$ and 1.11$^{+0.06}_{-0.06}$ for the standard and the assembly bias model respectively.
+In the standard model, the constraint on $\mmin$ is narrower and favors smaller values of $\mmin$.
+The best-fit and the 1-sigma uncertainties of $\mmin$ are 11.99$^{+0.15}_{-0.08}$ and 12.13$^{+0.39}_{-0.18}$ for the standard and the assembly bias model respectively.}
+\label{fig:post_wp_20}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-abhod-prediction
+% gmf-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{paper_model_decgmf.pdf}
+\includegraphics[width=\textwidth]{paper_model_hodgmf.pdf}
+\caption{We compare the posterior prediction for the observable $\gmf$ to the Berlind+06 measurements in three Luminosity threshold samples: $\mr<-18$, $\mr<-19$, and $\mr<-20$.
+The darker and the lighter shaded regions represent the 68$\%$ and the 95$\%$ confidence regions of the posterior predictions.
+$\bf{Top \; panel}$: 1-sigma and 2-sigma posterior prediction of the Heaviside Assembly bias HOD model.
+$\bf{Bottom \; panel}$: 1-sigma and 2-sigma posterior predictions of the the standard HOD model.}
+\label{fig:gmf-predictions}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% gmf-occupation-prediction
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{paper_abhod_ncengmf.pdf}
+\includegraphics[width=\textwidth]{paper_abhod_nsatgmf.pdf}
+\includegraphics[width=\textwidth]{paper_abvshod_gmf.pdf}
+
+\caption{We demonstrate the posterior predictions for the expected occupation statistics of galaxies.
+The shaded regions mark the 68 $\%$ confidence region of the posterior predictions.
+The observables used in fitting are $\bar{n}$ and $\gmf$.
+$\bf{Top \; panel}$: posterior predictions for the expected number of centrals as a function of halos for the two population of halos: $type$-1 (high concentration, sown with blue) and $type$-2 (low concentration, shown with yellow) halos.
+}
+\label{fig:gmf-hod-predictions}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% wp-prediction
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\includegraphics[width=\textwidth]{paper_model_decgmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
+\includegraphics[scale = 0.3]{paper_model_decwp.pdf} \\
+\includegraphics[scale = 0.3]{paper_model_hodwp.pdf}
+\caption{We compare the posterior prediction for the observable $\wpp$ to the Guo+15 measurements in five Luminosity threshold samples: $\mr<-18$, $\mr<-18.5$, $\mr<-19$, $\mr<-19.5$, and $\mr<-20$.
+The darker and the lighter shaded regions represent the 68$\%$ and the 95$\%$ confidence regions of the posterior predictions.
+$\bf{Top\;panel}$: 1-sigma and 2-sigma posterior prediction of the Heaviside Assembly bias HOD model.
+$\bf{Bottom\;panel}$: 1-sigma and 2-sigma predictions of the the standard HOD model.}
+\label{fig:wp-predictions}
 \end{center}
 \end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-hod-prediction
+% wp-occupation-prediction
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_model_hodgmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
+\includegraphics[width=\textwidth]{paper_abhod_ncenwp.pdf}
+\includegraphics[width=\textwidth]{paper_abhod_nsatwp.pdf}
+\includegraphics[width=\textwidth]{paper_abvshod_wp.pdf}
+
+\caption{}
+\label{fig:wp-hod-predictions}
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-ncen
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abhod_ncengmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-nsat
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abhod_nsatgmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-all
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abvshod_gmf.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-abhod-prediction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_model_decwp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-hod-prediction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_model_hodwp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-ncen
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abhod_ncenwp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-nsat
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abhod_nsatwp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-all
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{paper_abvshod_wp.pdf}
-\caption{hello world}
-\label{fig:abc_converge}
-\end{center}
-\end{figure*}
+
 \section*{Acknowledgments}

### 2016-07-01 text/ms.tex
updating the text

@@
 %%\documentclass[12pt, preprint]{aastex}
-\documentclass[14pt, preprint]{emulateapj}
+\documentclass[12pt, preprint]{emulateapj}
 \usepackage{microtype}
@@
 \title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
-\author{Mohammadjavad Vakili \altaffilmark{1,$\dagger$}, David W. Hogg, ChangHoon~Hahn, Unspecified contributors}
+\author{Mohammadjavad Vakili  \altaffilmark{1,$\dagger$}, ChangHoon~Hahn \altaffilmark{1}, Unspecified contributors \altaffilmark{1}}
 \altaffiltext{$\dagger$}{\url{mjvakili@nyu.edu}}
@@
 large-scale structure formation theories.
-One of the most powerful methods for describing 
-the galaxy-halo connection is the halo occupation modeling. 
-The underlying assumption of the traditional HOD framework is 
+The study of galaxy-halo connection is an essential tool for constraining the cosmology via small scale clustering and galaxy formation physics.
+One of the most powerful methods for describing the galaxy-halo connection is the halo occupation distribution (HOD, see \citealt{seljak2000, berlind_weinberg2002, scoccimarro2001, zheng2005, zheng2007}) and conditional luminosity function (CLF, see \citealt{clf_vdBosch}).
+
+HOD provides an analytical prescription for the statistical properties of galaxies within dark matter halos by specifying a probability distribution function $P(N|x)$ where $N$ is the number of galaxies and $x$ is a property of the dark matter halo.
+The underlying assumption of the standard HOD framework is
 that the halo mass alone is sufficient in determining the
-population of galaxies inside halos. That is, the statistical properties of 
+population of galaxies inside halo. That is, the statistical properties of 
 galaxies is governed by the halo mass. Mathematically, this assumption can be 
 written as $P(N_g|M_h,\{x\})=P(N_g|M_h)$ where $\{x\}$ is the set of all 
-possible halo properties beyond mass $M_{h}$. HOD provides an analytical prescription for the
+possible halo properties beyond mass $M_{h}$. In a similar fashion, CLF ties the luminosity of galaxies to the host halo mass.
 
-Despite this very simplifying assumption, the galaxy-halo connection models such as HOD and CLF have been widely and successfully used in modeling the measurements of a wide range of the statistical properties of galaxies such as .
+Despite this very simplifying assumption, the galaxy-halo connection models based on HOD and CLF have been used in fitting the measurements of a wide range of statistics such as correlation function of galaxies and galaxy-galaxy lensing.
+HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy lensing in SDSS main sample of galaxies (\citealt{vdb03,cacciato13,more13,vdb13}), and galaxy-galaxy lensing in the BOSS galaxies (\citealt{miyatake15,more15}).
+It has also been used in galaxy evolution studies (\citealt{conroy09,leauthaud12,behroozi13}).
+
+It has been shown by the $N$-body simulations that the halo clustering is correlated with the formation history of halos.
+That is, at a fixed halo mass, the halo bias is correlated with properties of halos beyond mass such as the concentration, formation time, spin, and etc.
+This phenomenon is known as the halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}).
+From the observational standpoint, this phenomenon has been confirmed
+(\citealt{miyatake2016,more2016}).
+
+If the galaxy properties are tied to the formation history of their host halos, we expect the occupation statistics of galaxies to be coupled to the properties as the concentration of halos, environment, and etc.
+This is called galaxy assembly bias.
+In the context of the semi-analytic models of galaxy formation, \citealt{croton2007} shows that
+
 However, the assumption that the statistical 
-distribution of galaxies can be determined by halo mass is not a derived characteristic of 
-accurate and high resolution hydrodynamic simulations, but rather a theoretical assumption 
-that needs to be scrutinized. In recent years, the idea that the
+distribution of galaxies can be determined by halo mass is not a derived characteristic of accurate and high resolution hydrodynamic simulations, but rather a theoretical assumption that needs to be scrutinized.
+In recent years, the idea that the
 
@@
 
-For populating the halos with galaxies, we follow the procedure described in CITE[HEARIN ETAL], CITE[CHANG ETAL].
+For populating the halos with galaxies, we follow the procedure described in \citealt{decorated}, \todo{HAHN+VAKILI 16 preparation}.
 The central galaxies are assumed to be at the center of the host dark matter halos.
-We place the satellite galaxies are within the virial radius of the halo following an NFW profile [CITE NFW].
-The concentration of the NFW profile is given by the empirical mass-concentration relation provided by [CITE MACCIO].
+We place the satellite galaxies are within the virial radius of the halo following an NFW profile (\citealt{nfw}).
+The concentration of the NFW profile is given by the empirical mass-concentration relation provided by (\citealt{nfw_c(M)}).
 The velocities of the satellite galaxies are given by two components.
 The first component is the velocity of the host halo.
-The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations [CITE MORE].
-We refer the readers to [CITE HEARIN 15] for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations (\citealt{more2010}).
+We refer the readers to \citealt{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+
+As described in \citealt{decorated} and \todo{HAHN+VAKILI in prep}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF.
+The accuracy of these fitting functions is limited (\citealt{tinker08,tinker10,watson13}).
+This approach also does not face the known issues of properly treatment of halo exclusion and scale-dependent bias that can lead to significant inaccuracies (\citealt{vdb13}).
+
+Another added advantage of this forward modeling approach is that it permits us to take advantage of observables beyond the traditionally used 2PCF.
+One of these observables is the group multiplicity function which characterizes the abundance of galaxy groups.
+There is no fitting function for calculation of this observable, and therefore, our approach of direct population of dark matter halos allows us to use these unconventional measurements for constraining the parameters governing the galaxy-halo collection.
 
 \subsubsection{Assembly bias HOD modeling}\label{subsubsec:decorated}
-Now let us provide a brief overview of HOD modeling decorated with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ introduced in [CITE HEARIN2015].
-At a fixed halo mass $M_{\rm h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.We call the first population "type 1" halos, and the second population "type 2 halos.
-Following In the decorated HOD model, the expected number of central and satellite galaxies in the two populations is given by
+Now let us provide a brief overview of HOD modeling decorated with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ introduced in \citealt{decorated}.
+At a fixed halo mass $M_{\rm h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.We call the first population "type-1" halos, and the second population "type-2 halos.
+In the decorated HOD model, the expected number of central and satellite galaxies in the two populations is given by
 
@@
 \end{eqnarray}
-Afterwards, CITE[HEARIN2015] defines the assembly bias parameter $\mathcal{A}$ in the following way:
+Afterwards, the assembly bias parameter $\mathcal{A}$ is defined in the following way:
 \begin{eqnarray}
@@
 function of group richness (the number of galaxies in groups) per richness width, measured in bins of richness. 
-Galaxy groups in are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF]. 
+Galaxy groups in are found by Friends-of-Friends (hereafter FoF) group finder algorithm (\citealt{fof}). 
 The FoF group finder algorithm links to galaxy $i$ and galaxy $j$ to each other, if the projected distance between the two galaxies $D_{\perp , i,j}$ is less than a specified projected linking length $b{_\perp}$, and the line-of-sight distance between the two galaxies $D_{\parallel, i,j}$ is less than a specified line-of-sight linking length $b{_\parallel}$.
 These linking lengths are measured in units of the mean inter-particle distance ($n_{\rm g}^{-1/3}$).
-In order to be consistent with the [CITE BERLIND] measurements, the linking lengths $b_{\perp}$ and $b_{\parallel}$ are set to to 0.15 and 0.74 respectively.
+In order to be consistent with the \citealt{berlind2006} measurements described in section \ref{sec:data}, the linking lengths $b_{\perp}$ and $b_{\parallel}$ are set to to 0.15 and 0.74 respectively.
 
@@
 \eeq
-For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ [CITE CORRFUNC].
+For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ (\citealt{corrfunc}).
 To be consistent with the SDSS measurements described in \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
@@
 
-For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the $z=0$ Bolshoi-Planck high 
-resolution $N$-body simulation CITE[Klypin2014]. This simulation was carried out using the adaptive refinement tree code 
-(ART, see cite[Kravstov]) code, following the Planck $\Lambda$CDM cosmological parameters 
+For the simulations used in this work, we make use of the Rockstar (\citealt{rockstar}) halo catalogs in the $z=0$ Bolshoi-Planck high 
+resolution $N$-body simulation (\citealt{bolshoi}). This simulation was carried out using the adaptive refinement tree code 
+(ART, see \citealt{art}) code, following the Planck $\Lambda$CDM cosmological parameters 
 $\Omega_{\rm m} = 0.307$, $\Omega_{\rm b} = 0.048$, $\Omega_{\Lambda} = 0.693$, $\sigma_{8} = 0.823$, $n_{\rm s}=0.96$, 
@@
 
-The first set of measurements consists of the galaxy number densities $n_{g}$ and the group multiplicity functions $g(N)$ described in [CITE BERLIND 2006]. These measurements are made 
-for the three Volume limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$.
-Galaxy groups in [CITE BERLIND etal] are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF].
-[CITE BERLIND ETAL] sets $b_{\perp}$ to 0.15 and $b_{\parallel}$ to 0.74 to minimize the discrepancy between the multiplicity function, projected size, and the number of FoF groups and those of the halos in a suite of simulations.
+The first set of measurements consists of the galaxy number densities $n_{g}$ and the group multiplicity functions $g(N)$ described in \citealt{berlind2006}.
+These measurements are made in three Volume-limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$.
+These galaxy groups are found by Friends-of-Friends (hereafter FoF) group finder algorithm (\citealt{fof}).
+\citealt{berlind2006} sets $b_{\perp}$ to 0.15 and $b_{\parallel}$ to 0.74 to minimize the discrepancy between the multiplicity function, projected size, and the number of FoF groups and those of the halos in a suite of $N$-body simulations.
 
@@
 Finally, these two uncertainties are added in quadrature
-to estimate the total error on [CITE BERLIND ETAL] $g(N)$ measurements.
+to estimate the total error on these $g(N)$ measurements.
 
@@
 
-The second set consists of the number density $n_{g}$ and the projected 2PCF $w_{\rm{p}}(r_{\rm{p}})$.
+The second set consists of the number density $n_{g}$ and the projected 2PCF $w_{\rm{p}}(r_{\rm{p}})$ made by \citealt{guo2015} for Volume-limited sample of galaxies in SDSS DR7 galaxy catalog.
 The project 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
 These measurements are accompanied by their corresponding covariance matrices constructed using 400 jackknife sub-samples of the data.
-The advantage of using these measurements is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, they provide very accurate small scale clustering measurements [see CITE GUO 2015].
-As [CITE HEARIN2015] demonstrates the satellite assembly bias $\mathcal{A}_{\rm sat}$ can have 10 $\%$ level impact on the small scale galaxy clustering.
+The advantage of using these measurements is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, these measurements provide very accurate small scale clustering measurements (\citealt{guo2012,guo2015}).
+As \citealt{hearin15} demonstrates, the satellite assembly bias $\mathcal{A}_{\rm sat}$ can lead to 10 $\%$ level impact on the small scale galaxy clustering.
 
@@
 \end{eqnarray}
-where $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $C^{-1}$ is inverse of the estimate of the jackknife covariance matrix provided by [CITE GUO2015]. 
+where $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $C^{-1}$ is inverse of the estimate of the jackknife covariance matrix provided by \citealt{guo15}. 
 Another important ingredient of our analysis is specification of the prior probabilities over the parameters of the two halo occupation models.
@@
 For sampling from the posterior probability, given the likelihood function (see Eqs.
-\ref{eq:lnlike_group}, \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
+\ref{eq:lnlike_group}, \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler (\citealt{goodmanweare}) and its implementation $\mathtt{emcee}$ (\citealt{emcee}).
 In particular, we run the $\mathtt{emcee}$ code with 140 walkers and we run the chains for at least 15000 iterations until the convergence of the MCMC chains is ensured.
-For testing the convergence of the chains, we perform Gelman-Rubin convergence test [CITE GELMANANDRUBIN and the other paper].
+For testing the convergence of the chains, we perform Gelman-Rubin convergence test (\citealt{grtest}).
 
@@
 There are various methods for model comparison.
-In this work we make use of two model comparison criteria: \emph{Akaike Information Criterion} (AIC, see CITE ...
-), and \emph{Bayesian Information Criteria} (BIC, see CITE ....).
+In this work we make use of two model comparison criteria: \emph{Akaike Information Criterion} (AIC, \citealt{aic} , see \citealt{gelmanic} for detailed discussion in AIC), and \emph{Bayesian Information Criteria} (BIC, \citealt{bic}).
 AIC and BIC are two widely used methods for assessing the relative quality of models given a set of observations.
@@
 \begin{eqnarray}
-AIC&=& -2\;\ln \mathcal{L}_{\rm max} + 2N_{\rm par} + 2\;\frac{N_{\rm par}(N_{\rm par}+1)}{N_{\rm data}-N_{\rm par}-1} \; , \label{eq:aic}\\
-BIC&=& -2\;\ln \mathcal{L}_{\rm max} + N_{\rm par}\;\ln N_{\rm data} \; . \label{eq:bic}
+\rm{AIC}&=& -2\;\ln \mathcal{L}_{\rm max} + 2N_{\rm par} \nonumber \\
+         &+& 2\;\frac{N_{\rm par}(N_{\rm par}+1)}{N_{\rm data}-N_{\rm par}-1} \; , \label{eq:aic}\\
+\rm{BIC}&=& -2\;\ln \mathcal{L}_{\rm max} + N_{\rm par}\;\ln N_{\rm data} \; . \label{eq:bic}
 \end{eqnarray}
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{paper_abhod_ncengmf.pdf}
-\includegraphics[width=\textwidth]{paper_abhod_nsatgmf.pdf}
-\includegraphics[width=\textwidth]{paper_abvshod_gmf.pdf}
+\begin{center}
+\includegraphics[scale=0.5]{paper_abhod_ncengmf.pdf}\\
+\includegraphics[scale=0.5]{paper_abhod_nsatgmf.pdf}\\
+\includegraphics[scale=0.5]{paper_abvshod_gmf.pdf}
 
-\caption{We demonstrate the posterior predictions for the expected occupation statistics of galaxies.
+\caption{We present the posterior predictions for the expected number of galaxies as a function of host halo mass in three luminosity threshold samples: $\mr<-18$, $\mr<-19$, and $\mr<-20$.
 The shaded regions mark the 68 $\%$ confidence region of the posterior predictions.
 The observables used in fitting are $\bar{n}$ and $\gmf$.
-$\bf{Top \; panel}$: posterior predictions for the expected number of centrals as a function of halos for the two population of halos: $type$-1 (high concentration, sown with blue) and $type$-2 (low concentration, shown with yellow) halos.
-}
+$\bf{Top \; panel}$: posterior predictions for the expected number of centrals as a function of host halo mass for the two population of halos: $type$-1 (high-$c$, shown with blue) and $type$-2 (low-$c$, shown with yellow) halos.
+The expected number of centrals in $type$-1 and $type$-2 halos at a fixed halo mass are in agreement.
+$\bf{Middle \; panel}$: posterior predictions for the expected number of satellites as a function of host halo mass for the two population of halos.
+The expected number of satellites in two population of halos at a fixed halo mass are in agreement.$\bf{Bottom \; panel}$: posterior predictions for the expected number of galaxies as a function of host halo mass for two models: the standard HOD (shown in red), and decorated HOD model (shown in blue).
+The prediction of the two models for the expected number of galaxies as a function of host halo mass are in agreement.}
 \label{fig:gmf-hod-predictions}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{paper_abhod_ncenwp.pdf}
-\includegraphics[width=\textwidth]{paper_abhod_nsatwp.pdf}
-\includegraphics[width=\textwidth]{paper_abvshod_wp.pdf}
-
-\caption{}
+\begin{center}
+\includegraphics[scale=0.45]{paper_abhod_ncenwp.pdf}\\
+\includegraphics[scale=0.45]{paper_abhod_nsatwp.pdf}\\
+\includegraphics[scale=0.45]{paper_abvshod_wp.pdf}
+\caption{We present the posterior predictions for the expected number of galaxies as a function of host halo mass for three luminosity threshold samples: $\mr<-18$, $\mr<-19$, $\mr<-20$.
+The shaded regions mark the 68 $\%$ confidence region of the posterior predictions.
+The observables used in fitting are $\bar{n}$ and $\wpp$.
+$\bf{Top \; panel}$: posterior predictions for $\langle N_{\rm cen}\rangle$ as a function of host halo mass for the two population of halos: $type$-1 (high-$c$, shown with blue) and $type$-2 (low-$c$, shown with yellow) halos.
+In the $\mr<-18$ sample and at a fixed host halo mass $M_{h}$, the expected number of centrals in the $type$-2 population of halos is larger than the expected number of centrals in the $type$-1 population.
+In the $\mr<-19$ sample and at a fixed $M_{h}$, $\langle N_{\rm cen}\rangle$ of the two populations are in agreement.
+In the $\mr<-20$ sample and at a fixed $M_{h}$, $\langle N_{\rm cen}\rangle$ is larger for $type$-1 population of halos.
+$\bf{Middle \; panel}$: posterior predictions for the expected number of satellites $\langle N_{\rm sat}\rangle$ as a function of host halo mass for the two population of halos.
+In the $\mr<-18$ sample and at a fixed host halo mass $M_{h}$, $\langle N_{\rm sat}\rangle$ for the the two populations are in agreement.
+In the $\mr<-19$ sample and at a fixed $M_{h}$, $\langle N_{\rm sat}\rangle$ of the $type$-2 population is enhanced with respect to that of the $type$-1 halos.
+In the $\mr<-20$ sample and at a fixed $M_{h}$, $\langle N_{\rm sat}\rangle$ of the two populations are largely in agreement.
+$\bf{Bottom \; panel}$: posterior predictions for the expected total number of galaxies $\langle N_{\rm g}\rangle$ as a function of host halo mass for two models: the standard HOD (shown in red), and decorated HOD model (shown in blue).
+In the $\mr<-18$ sample and the high mass end, there is slight tension between $\langle N_{\rm g}\rangle$ derived from standard HOD posterior and the decorated HOD posterior.
+In the $\mr<-19$ sample, the tension at the high mass end persists but it is less significant.
+In the $\mr<-20$ sample, there is some tension between the predictions of the two models at the low mass end.}
 \label{fig:wp-hod-predictions}
+\end{center}
 \end{figure*}
@@
 administrator of NYU-HPC computational facility, for his consistent and continuous support 
-throughout the development of this project. We also thanks Dan Foreman-Mackey for providing some of the computational resources at the early stages of this work.
+throughout the development of this project.
+We also thanks Dan Foreman-Mackey for providing some of the computational resources at the early stages of this work.
+The posterior probability plots in this paper where made using the software corner (\citealt{corner}).
 
+\bibliographystyle{yahapj}
+\bibliography{ab}
 \end{document}

### 2016-09-15 code/SHAM_clustering.py
abundance mathcing plots

@@ -1,6 +1,5 @@
 '''
 Module for handling the SHAM catalogs 
-made by ChangHoon Hahn
 '''
 import h5py
 import numpy as np
@@ -16,7 +15,8 @@ def read_catalog():
     '''read SHAM catalog
     '''
 
-    filename =  util.dat_dir()+'bolshoi_a1.00231.mag_r.source_blanton.scatter0.2.Vpeak.hdf5'
+    filename =  '/export/bbq2/mj/smdpl_a1.00000.mag_r.source_blanton.scatter0.0.tailored.hdf5'
+    #filename =  '/export/bbq2/mj/smdpl_a1.00000.mag_r.source_blanton.scatter0.17.tailored.hdf5'
     cat = h5py.File(filename, "r")['data']
     length_file = len(cat['x'][:])
     cat_file = np.zeros((length_file , 7))
@@ -45,7 +45,7 @@ def save_luminosity_threshold(Mr):
        luminosity threshold'''
 
     reduced_cat = impose_luminosity_threshold(Mr)
-    filename = util.dat_dir()+'SHAM_Mr'+str(Mr)+'dat'
+    filename = util.dat_dir()+'SHAM_smdpl_Mr'+str(Mr)+'dat'
     np.savetxt(filename , reduced_cat)
 
     return None
@@ -56,14 +56,16 @@ def measure_nbar_clustering(Mr):
 
     #Corrfunc settings for wp measurements:
 
-    boxsize = 250
+    #boxsize = 250
+    boxsize = 400
     nthreads = 4
     pimax = 40.0
     binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
     autocorr = 1
 
-    filename = util.dat_dir()+'SHAM_Mr'+str(Mr)+'dat'
+    #filename = util.dat_dir()+'SHAM_Mr'+str(Mr)+'dat'
+    filename = util.dat_dir()+'SHAM_smdpl_Mr'+str(Mr)+'dat'
     cat = np.loadtxt(filename)
     pos = cat[:,0:3]
     x, y, z = pos[:,0], pos[:,1], pos[:,2] 
@@ -208,8 +210,9 @@ def save_jackknife_covariance(Mr , nsub):
 
 if __name__ == "__main__":
 
-     Mr = 19
+     Mrs = [21.0 + 0.5 * x for x in range(2)]
      nsub = 3
-     save_luminosity_threshold(Mr)    
-     save_nbar_clustering(Mr)
[…]

### 2016-09-15 code/biased_vs_erased.py

@@ -1,0 +1,171 @@
+import util as ut
+import data
+import matplotlib.pyplot as plt
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+from Corrfunc.utils import read_catalog
+from halotools.empirical_models import NFWPhaseSpace
+from matplotlib import lines as mlines
+import matplotlib.pyplot as plt
+from matplotlib import lines as mlines
+from matplotlib import gridspec
+from scipy.stats import norm
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+import os
+import os.path as path 
+from numpy.linalg import solve
+import h5py
+import corner
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from matplotlib.ticker import MaxNLocator
+from matplotlib.colors import colorConverter
+from ChangTools.plotting import prettyplot
+from ChangTools.plotting import prettycolors
+plt.switch_backend("Agg")
+
+
+
+def plot_wprandom(obs = "wp", clotter = True):
+
+    if clotter == False:
+
+        print "running compute_model_prediction first"
+
+    else:
+
+        #### loading the model predictions for the observables ######         
+
+        file20 = np.loadtxt("../dat/wp_AGEMATCHING_Mr-20.0.dat")
+        file205 = np.loadtxt("../dat/wp_AGEMATCHING_Mr-20.5.dat")
+        file21 = np.loadtxt("../dat/wp_AGEMATCHING_Mr-21.0.dat")
+
+        rand20 = np.loadtxt("../dat/wp_AGEMATCHING_randomized_Mr-20.0.dat")
+        rand205 = np.loadtxt("../dat/wp_AGEMATCHING_randomized_Mr-20.5.dat")
+        rand21 = np.loadtxt("../dat/wp_AGEMATCHING_randomized_Mr-21.0.dat")
+        #### loading the observables in Mr 18,19,20
+
+
+        if obs == "wp":
+
[…]

### 2016-09-15 text/ms.tex

@@
 
-\title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
-\author{Mohammadjavad Vakili  \altaffilmark{1,$\dagger$}, ChangHoon~Hahn \altaffilmark{1}, Unspecified contributors \altaffilmark{1}}
-\altaffiltext{$\dagger$}{\url{mjvakili@nyu.edu}}
-\altaffiltext{1}{Center for Cosmology and Particle Physics, 
-                 Department of Physics, New York University, 4 Washington Pl., New York, NY} 
+\author{Mohammadjavad Vakili\altaffilmark{1}, David~W.~Hogg\altaffilmark{1,2,3,4}, and ChangHoon~Hahn\altaffilmark{1}}
+\affil{Center for Cosmology and Particle Physics, New York University, 4 Washington Pl, New York, NY, 10003}
+\email{mjvakili@nyu.edu}
+
+\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University, 4 Washington Pl, New York, NY, 10003}
+\altaffiltext{2}{Simons Center for Data Analysis, 160 Fifth Avenue, New York, NY}
+\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, New York, NY}
+\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 \begin{abstract}
+Analyses of the $N$-body simulations have demonstrated that the clustering of dark matter halos depend on the halo properties beyond mass such as halo concentration.
+Standard halo occupation distribution (HOD) modeling approach in large scale structure studies assumes that the halo mass alone is sufficient in characterizing the galaxy-halo connection.
+Galaxy assembly bias hypothesizes that properties beyond halo mass influence the galaxy-halo connection, and can lead to systematic effects on the modeling of galaxy clustering.
 
-The standard halo occupation modeling approach in large scale structure 
-studies assumes that the halo mass alone suffices in characterizing the 
-galaxy-halo connection. Galaxy assembly bias, the hypothesis that properties beyond 
-halo mass influences the galaxy-halo connection, can potentially affect the 
-statistical summaries of galaxy populations. The degree to which, assembly bias can 
-can be constrained with the statistical distribution of galaxies remains largely 
-untested. In this investigation, we make use of the recently proposed assembly bias decoration 
-of the HOD modeling in order to find constraints on the strength of the assembly bias from the most up-to-date and publicly available measurements of the group multiplicity function and the projected two-point correlation function of the Volume-limited luminosity threshold sample of SDSS
-galaxies.
-We find that the available GMF measurements cannot constrain galaxy assembly bias in any of the Luminosity thresholds.
-On the other hand, we find non-zero constraints on the satellite galaxy assembly bias for the $M_{r}<-18$ and $M_{r}<-19$ samples, nonzero constraints on the central galaxy assembly bias for the $M_{r}<-20$ samples, and constraints consistent with zero for the assembly bias of galaxies in the $M_{r}<-21$ sample.
-Furthermore, we provide a model comparison between the standard HOD approach and the decorated HOD in modeling of the GMF and the projected 2PCF measurements.
+Using the Small MultiDark Planck high resolution $N$- body simulation and the measurements of the projected two-point correlation function as well as the number density of the DR7 main galaxy sample of the Sloan Digital Sky Survey, we constrain the concentration-dependence of HOD.
+This concentration dependence is modeled within the framework of the proposed decorated HOD model.
 
+For fainter samples, we find non-zero albeit poor constraints on the strength of the assembly bias.
+Furthermore, we find that the assembly bias remains largely unconstrained in the brighter galaxy samples that live in massive dark matter halos.
+
+By comparison between the 2PCF measured from the mock galaxy catalogs using our best-fit model and the randomized galaxy catalogs in which the assembly bias is erased, we note that the effect of assembly bias on galaxy clustering is qualitatively similar to its effect on galaxy catalogs created from a certain class of subhalo abundance matching models.
+\end{abstract}
+\keywords{Cosmology: large-scale-structure, galaxy: galaxies}
 \end{abstract}

### 2016-09-16 text/ms.tex
newest draft

--- 2016-06-30 text/ms.tex
@@
-%%\documentclass[12pt, preprint]{aastex}
-\documentclass[14pt, preprint]{emulateapj}
-\usepackage{microtype}
-\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\documentclass[12pt, preprint]{aastex}
+\usepackage[breaklinks,colorlinks, 
+urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{graphicx}	% For figures
@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-
-\newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}
 \newcommand{\beq}{\begin{equation}}
@@
 \newcommand{\dev}{\mathrm{d}}
-\newcommand{\wpp}{w_{\rm p}}
 \newcommand{\ngal}{n_{g}}
@@
 \newcommand{\sigmam}{\sigma_{\log \rm M}} 
+\newcommand{\wpp}{w_{\rm p}}
+
 \newcommand{\acen}{\mathcal{A}_{\rm cen}}
 \newcommand{\asat}{\mathcal{A}_{\rm sat}}
+%\newcommand{\comment}[1]{{\bf \textcolor{red}{ #1}}}
+\newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}
+
+%% preprint2 produces a double-column, single-spaced document:
+
+%% \documentclass[preprint2]{aastex}
+
+%% Sometimes a paper's abstract is too long to fit on the
+%% title page in preprint2 mode. When that is the case,
+%% use the longabstract style option.
+
+%% \documentclass[preprint2,longabstract]{aastex}
+
+%% If you want to create your own macros, you can do so
+%% using \newcommand. Your macros should appear before
+%% the \begin{document} command.
+%%
+%% If you are submitting to a journal that translates manuscripts
+%% into SGML, you need to follow certain guidelines when preparing
+%% your macros. See the AASTeX v5.x Author Guide
+%% for information.
+
+%% You can insert a short comment on the title page using the command below.
+
+%\slugcomment{Not to appear in Nonlearned J., 45.}
+
+%% If you wish, you may supply running head information, although
+%% this information may be modified by the editorial offices.
+%% The left head contains a list of authors,
+%% usually a maximum of three (otherwise use et al.).  The right
+%% head is a modified title of up to roughly 44 characters.
+%% Running heads will not print in the manuscript style.
+
+%\shorttitle{Collapsed Cores in Globular Clusters}
+%\shortauthors{Djorgovski et al.}
+
+%% This is the end of the preamble.  Indicate the beginning of the
+%% paper itself with \begin{document}.
 
@@
 
-\title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
-\author{Mohammadjavad Vakili \altaffilmark{1,$\dagger$}, David W. Hogg, ChangHoon~Hahn, Unspecified contributors}
-\altaffiltext{$\dagger$}{\url{mjvakili@nyu.edu}}
-\altaffiltext{1}{Center for Cosmology and Particle Physics, 
-                 Department of Physics, New York University, 4 Washington Pl., New York, NY} 
+%% LaTeX will automatically break titles if they run longer than
+%% one line. However, you may use \\ to force a line break if
+%% you desire.
+\title{How do galaxies get assigned to halos? \\ Searching for the assembly bias in the SDSS galaxy clustering}
+
+%%\title{Collapsed Cores in Globular Clusters, \\
+%%    Gauge-Boson Couplings, and AAS\TeX\ Examples}
+
+%% Use \author, \affil, and the \and command to format
+%% author and affiliation information.
+%% Note that \email has replaced the old \authoremail command
+%% from AASTeX v4.0. You can use \email to mark an email address
+%% anywhere in the paper, not just in the front matter.
+%% As in the title, use \\ to force line breaks.
+
+\author{Mohammadjavad Vakili\altaffilmark{1}}
+
+\email{mjvakili@nyu.edu}
+
+\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University, 4 Washington Pl, New York, NY, 10003}
+
 \begin{abstract}
 
-The standard halo occupation modeling approach in large scale structure 
-studies assumes that the halo mass alone suffices in characterizing the 
-galaxy-halo connection. Galaxy assembly bias, the hypothesis that properties beyond 
-halo mass influences the galaxy-halo connection, can potentially affect the 
-statistical summaries of galaxy populations. The degree to which, assembly bias can 
-can be constrained with the statistical distribution of galaxies remains largely 
-untested. In this investigation, we make use of the recently proposed assembly bias decoration 
-of the HOD modeling in order to find constraints on the strength of the assembly bias from the most up-to-date and publicly available measurements of the group multiplicity function and the projected two-point correlation function of the Volume-limited luminosity threshold sample of SDSS
-galaxies.
-We find that the available GMF measurements cannot constrain galaxy assembly bias in any of the Luminosity thresholds.
-On the other hand, we find non-zero constraints on the satellite galaxy assembly bias for the $M_{r}<-18$ and $M_{r}<-19$ samples, nonzero constraints on the central galaxy assembly bias for the $M_{r}<-20$ samples, and constraints consistent with zero for the assembly bias of galaxies in the $M_{r}<-21$ sample.
-Furthermore, we provide a model comparison between the standard HOD approach and the decorated HOD in modeling of the GMF and the projected 2PCF measurements.
+Clustering of dark matter halos is shown to depend on halo properties beyond mass such as halo concentration.
+This phenomenon is referred to as halo assembly bias.
+Standard halo occupation modeling in large scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
+Modeling of galaxy clustering can face systematic effects if galaxies are correlated with other halo properties.
+Using the Small MultiDark-Planck high resolution $N$-body simulation and the measurements of the projected two-point correlation function and the number density of Sloan Digital Sky Survey (SDSS) DR7 main galaxy sample, we investigate the extent to which the dependence of halo occupation on halo concentration can be constrained, and to what extent this can improve our modeling of galaxy clustering.
+
+Given the SDSS clustering data, our constraints on HOD with assembly bias, suggests that satellite population is not correlated with halo concentration at fixed halo mass.
+Furthermore, in terms of the number of centrals at fixed halo mass, our results favor lack of correlation with halo concentration in the most luminous samples ($M_{\rm r}<-21.5,-21$), modest levels of correlation for $M_{\rm r}<-20.5,-20, -19.5$ samples, lack of correlation for $M_{\rm r}<-19,-18.5$ samples, and anti-correlation for the faintest sample $M_{\rm r}<-18$.
+
+We show that in comparison with abundance matching mock catalogs, our findings suggest more modest levels of assembly bias.
+Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
 
 \end{abstract}
+\keywords{Cosmology: large-scale-structure of the universe, galaxies: halos}
 
 \section{Introduction}
-The assumption that galaxies reside dark matter halos 
-is the central tenet of the modern cosmology and 
-large-scale structure formation theories. 
-One of the most powerful methods for describing 
-the galaxy-halo connection is the halo occupation modeling. 
-The underlying assumption of the traditional HOD framework is 
-that the halo mass alone is sufficient in determining the
-population of galaxies inside halos. That is, the statistical properties of 
-galaxies is governed by the halo mass. Mathematically, this assumption can be 
-written as $P(N_g|M_h,\{x\})=P(N_g|M_h)$ where $\{x\}$ is the set of all 
-possible halo properties beyond mass $M_{h}$. HOD provides an analytical prescription for the
 
-Despite this very simplifying assumption, the galaxy-halo connection models such as HOD and CLF have been widely and successfully used in modeling the measurements of a wide range of the statistical properties of galaxies such as .
-However, the assumption that the statistical
-distribution of galaxies can be determined by halo mass is not a derived characteristic of 
-accurate and high resolution hydrodynamic simulations, but rather a theoretical assumption 
-that needs to be scrutinized. In recent years, the idea that the
+Most theories of cosmology and large scale structure formation under consideration today rely on the central assumption that galaxies reside in dark matter halos.
+Detailed study of the galaxy-halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
+One of the most powerful methods for describing the galaxy-halo connection is the halo occupation
+distribution (HOD, see \citealt{seljak2000, berlind_weinberg2002, scoccimarro2001, zheng2005, zheng07, leauthaud12, tinker2013, decorated, 2016arXiv160701782H}).
 
-In this investigation, we explore the notion that how the dependence of 
-galaxy-halo connection on halo properties beyond mass (e.g. concentration, age).
+HOD is an empirical framework that provides an analytic prescription for the expected number of galaxies $N$ that reside in halos by specifying a probability distribution function $P(N|x)$ where $x$ is a property of the halo.
+Under standard HOD modeling, the assumption is made that the halo mass $M$ alone is sufficient in determining the galaxy population of a halo.
+That is, the statistical properties of galaxies is governed by the halo mass.
+Mathematically, this assumption can be written as $P(N_g|M,\{x\})=P(N_g|M)$ where $\{x\}$ is the set of all possible halo properties beyond halo mass $M$.
+
+Despite this very simplifying assumption, the models of galaxy-halo connection based on HOD modeling have been used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy-galaxy lensing with remarkable success (e.g.
+\citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}).
+HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy lensing (\citealt{vdb03,cacciato13,more13,vdb13}) in the main sample of galaxies
+of the Sloan Digital Sky Survey (hereafter SDSS, \citealt{york2000}), and also the combination of galaxy clustering and galaxy-galaxy lensing (\citealt{more15}) in SDSS III Baryon Oscillation Spectroscopic Survey (BOSS, \citealt{boss}).
+Furthermore, HOD is implemented in producing mock galaxy catalogs in the BOSS survey (\citealt{manera2013,white2014}).
+It has also been used in galaxy evolution studies (\citealt{conroy09,leauthaud12,behroozi13,hudson2015,zu2015,zu2016}).
+
+The simplifying assumption of standard HODs  
+does not sufficiently model the complex small scale clustering and galaxy
+formation. Numerous $N$-body simulations that examine the clustering of 
+dark matter halos argue halo clustering is correlated with the formation 
+history of halos. That is, at a fixed halo mass, the halo bias is correlated 
+with properties of halos beyond mass such as the concentration, formation time, or etc. 
+This phenomenon is known as the halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}). 
+There is even support for halo assembly bias in observations (\citealt{miyatake2016,more2016}).
+
+Furthermore, the properties of galaxies within the halo, may also depend on the halo's formation history.
+Then, we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos, environment, and etc.
+There have been many attempts in the literature in examining the dependence of the galaxy properties on larger scale environment of the halos.
+But the results are mixed and there is very little consensus over this matter.
+\citealt{tinker_void_2009} shows that the properties of the galaxies that reside in voids can be explained by the halo mass in which they live, and their properties are independent of their large scale environment of the halos.
+\citealt{tinker_density_hod} proposes and extension the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
+Based on modeling the clustering and void statistics of the SDSS galaxies, \citealt{tinker_vpf_2008} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
+By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citealt{croton2007} shows that assembly bias significantly impacts the galaxy two-point correlation functions.
+They also show that the effect is different for the faint and the bright samples.
+By applying a group finder to SDSS DR7 galaxies, \citealt{tinker2011} shows that the quenched fraction of galaxies is independent of the large-scale environment.
+
+Based on a group catalog of SDSS galaxies, \citealt{blanton_group_2007} finds that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
+Based on an alternative group catalog, \citealt{wang2013} show that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
+
+Another family of empirical galaxy-halo connection models is \emph{Abundance} \emph{Matching}.
+In the Abundance Matching style models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity/stellar mass
+(\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
+In practice, the standard abundance matching models use host halo properties 
+that trace the depth of the gravitational well of the halo, such as 
+the maximum circular velocity the host halo had in its history, $V_\mathrm{max}$, 
+and assume a scatter in this property's one-to-one mapping with 
+stellar mass/luminosity. With this, 
+they have been successfully used in modeling a wide range of the 
+statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).
+
+It has been shown that the abundance matching mock catalogs that use $V_{\rm max}$ (see \citealt{hw2013,arz2014}), or the ones that use some combination of $V_{\rm max}$ and host halo/subhalo virial mass $M_{\rm vir} $(see \citealt{lehman2015}) exhibit significant levels of assembly bias.
+This has been demonstrated by randomizing the galaxies among host halos of in bins of halo mass, such that the HOD remains constant, and comparing the difference in the 2PCF of the randomized catalog and the original mock catalog.
+
+Abundance Matching models, can be extended to account for even higher orders of galaxy 
+assembly bias. In so called \emph{Age Matching} models, galaxy color is abundance-matched
+to subhalo formation time so that older (redder) galaxies preferentially reside in older halos (\citealt{hw2013}).
+\citealt{hearin2014} demonstrates that such an approach can reproduce a range of color and luminosity-dependent statistics of SDSS galaxies such as the 2PCF and galaxy-galaxy lensing.
+Based on the projected 2PCF measurements of (\citealt{hw2013}) galaxy catalogs, \citealt{arz2014} showed that although the 2PCF measurements of these catalogs can be fit with the standard HOD modeling, the inferred HOD parameters cannot recover the underlying true HOD of these catalogs.
+That is, even in the presence of assembly bias in a galaxy sample, one can fit the clustering of this sample with HOD, but that does not guarantee recovery of the true HOD parameters.
+\citealt{mcewen2016} demonstrated that even with a galaxy catalog that has a significant level of assembly bias such as (\citealt{hw2013}) catalog, it is possible to extract the matter power spectrum more accurately if an environment-dependent HOD ($P(N|M,\delta)$) is used.
+
+In this work, we aim to investigate the dependence of halo occupation on halo concentration, and how this dependence can be constrained in the low-redshift universe with the measurements of the 2PCF of galaxies with a wide range of luminosities in the SDSS DR7 main galaxy sample.
+In order to achieve this goal, we need to adopt a HOD model that takes into account 
+a dependence on halo properties beyond mass.
+There are a number of frameworks in the literature.
+\citealt{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} have proposed environment-dependent HOD modeling methods that take into account the large-scale density contrast.
+The model that we use in this investigation is the decorated HOD modeling (\citealt{decorated}).
+In the decorated HOD framework, at a fixed halo mass, halos are populated with galaxies according to the standard HOD modeling.
+Then, a secondary halo property is selected.
+At a fixed halo mass, halos are split into two populations: halos with the highest and halos with the lowest values of the secondary property.
+The two population receive enhancements (decrements) in their number of galaxies according to a parameter which is the strength of the assembly bias parameter.
+Therefore, the assembly bias parameter will not be degenerate with the rest of the HOD parameters.
+
+The advantage of this framework is that the more complex HOD model is identical to the underlying \emph{mass-only} HOD model in every respect, except that at a fixed halo mass, halos receive enhancement (decrements) in the number of galaxies they host according to the value of their secondary property.
+In order to constrain assembly bias along with the rest of the HOD parameters, we make use of the publicly available measurements of the projected 2PCF and number density measurements made by
+(\citealt{guo2015}). These measurements made use of the NYU value-added galaxy catalog (\citealt{Blanton2005}).
+
+Furthermore, we discuss how and in which galaxy brightness limits, employing a more complex HOD model that takes assembly bias into account can improve our modeling of galaxy clustering.
+We discuss the physical mechanisms that enables the more concentration-dependent HOD model to improve fitting of the galaxy 2PCF.
+Then, we make qualitative comparison between the levels of assembly bias in the mock catalogs created from our constrained on the decorated HOD model, and the \citealt{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
+
+In order to investigate whether more complexity of the decorated HOD model is demanded by the galaxy clustering data, we perform model comparison between the standard HOD model and the HOD model with assembly bias.
+Moreover,  We discuss the effect of our choice of $N$-body simulation on our constraints, and previous works in the literature based on smaller $N$-body simulations (\citealt{zentner2016}).
+
+This paper is structured as follows: In Section \ref{sec:method} we discuss the $N$-body simulation, the two halo occupation modeling methods, and the details of the computation of model observables used in this investigation.
+Then in Section \ref{sec:data}, we discuss the data used in this study.
+In Section \ref{sec:analysis} we discuss the details of our inference analysis as well as the results.
+This includes description of the details of our inference setup.
+In Section \ref{sec:result} we discuss the constraints and their implications.
+This includes presentation of the constraints on the parameters of the two models, interpretation of the predictions of our constraints and their possible physical ramifications, assessment of the levels of assembly bias as predicted by our model constraints and its comparison with abundance matching mock catalogs, and finally model comparison.
+Finally, we discuss and conclude in Section \ref{sec:summary}.
 Throughout this paper, unless stated otherwise, 
-all radii and densities are in comoving units. Standard flat $\Lambda$CDM is assumed, 
-and all cosmological parameters are set to the Planck 2013 best-fit estimates.
+all radii and densities are stated in comoving units. 
+Standard flat $\Lambda$CDM is assumed, and all cosmological 
+parameters are set to the Planck 2015 best-fit estimates.
 
-\section{Method}
+\section{Method}\label{sec:method}
+
+In this section, we discuss the ingredients of our modeling one-by-one.
+First, we discuss the simulation used in this study.
+Afterwards, we talk about the forward modeling of galaxy catalogs in the standard HOD modeling framework as well as the decorated HOD framework.
+Then, we provide an overview of the two summary statistics of the galaxy catalogs that we used in our inference.
+
+\subsection{Simulation}
+
+For the simulations used in this work, we make use of the Rockstar (\citealt{rockstar}) halo catalogs in the $z=0$ snapshot of the Small MultiDark of Planck cosmology (referred to as $\mathtt{SMDP}$) (\citealt{smallmultidark}).
+This high resolution $N$-body simulation (publicly available at \url{https://www.cosmosim.org}) was carried out using the GADGET-2 code
+(see \citealt{smallmultidark} and references therein) code, following the Planck $\Lambda$CDM cosmological parameters 
+$\Omega_{\rm m} = 0.307$, $\Omega_{\rm b} = 0.048$, $\Omega_{\Lambda} = 0.693$, $\sigma_{8} = 0.823$, $n_{\rm s}=0.96$, 
+$h=0.678$.
+The Box size for this $N$-body simulation is 0.4 $h^{-1} \rm{Gpc}$, the number of simulation particles is 3840$^3$, the mass per simulation particle $m_{\rm p}$ is $9.6 \times 10^{7} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1.5 $h^{-1} \rm{kpc}$.
+
+In the $\mathtt{SMDP}$ simulation, as discussed in \citealt{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.
+The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy-halo connection.
+Fainter galaxy samples reside in lower mass halos, and the more luminous galaxy samples considered in this investigation occupy higher comoving volumes.
+Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos.
+In the context of Subhalo-Abundance matching modeling---whose accuracy hinges upon subhalo completeness especially in the low mass limit---of the galaxy-halo connection in the SDSS data, $\mathtt{SMDP}$ has been previously used to model the faint galaxy samples with absolute luminosity in the r-band $M_{\rm r}$ less -18, -18.5, and -19 (see \citealt{hod_vs_sham}).
+The added advantage of using the $\mathtt{SMDP}$ simulation over some industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its comoving volume which makes it more suitable for performing inference with $L_{\star}$ (corresponding to $M_{\rm r} \sim -20.44$, see \citealt{blanton2003}) and more luminous than $L_{\star}$ galaxy samples.
+
 \subsection{Halo occupation modeling}
-\subsubsection{standard HOD modeling}\label{subsubsec:hod}
-For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
+\subsubsection{standard model without assembly bias}\label{subsubsec:hod}
+
+For our standard HOD model, we assume the HOD parameterization from \citealt{zheng07}. 
+According to this model, a dark matter halo can host a central galaxy and some number of satellite galaxies. The occupation of the central galaxies follows a nearest-integer distribution, 
 and the occupation of the satellite galaxies follows a Poisson distribution.
@@
 
-For populating the halos with galaxies, we follow the procedure described in CITE[HEARIN ETAL], CITE[CHANG ETAL].
+For populating the halos with galaxies, we follow the procedure described in \citealt{2016arXiv160701782H,decorated}.
 The central galaxies are assumed to be at the center of the host dark matter halos.
-We place the satellite galaxies are within the virial radius of the halo following an NFW profile [CITE NFW].
-The concentration of the NFW profile is given by the empirical mass-concentration relation provided by [CITE MACCIO].
+We assume that the central galaxies are at rest with respect to the bulk motion of the halos and their velocities are given by the velocity of the center of mass of their host halo.
+Note that this assumption is shown to be violated in brighter than $L_{\star}$ galaxies (see \citealt{guo2015}).
+But since we are not considering the redshift space 2PCF multipoles in our study, we do not expect this velocity bias to impact our inference.
+We place the satellite galaxies within the virial radius of the halo following a Navarro-Frenk-White profile (hereafter NFW; \citealt{nfw}).
+This approach is different from other simulation-based halo occupation modeling techniques (see \citealt{hod_vs_sham,zheng_guo}) in that the positions of the satellites are not assigned to the dark matter particles in the $N$-body simulation.
+The concentration of the NFW profile is given by the empirical mass-concentration relation provided by (\citealt{nfw_c(M)}).
 The velocities of the satellite galaxies are given by two components.
 The first component is the velocity of the host halo.
-The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations [CITE MORE].
-We refer the readers to [CITE HEARIN 15] for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations (\citealt{more2010}).
+We refer the readers to \citealt{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
 
-\subsubsection{Assembly bias HOD modeling}\label{subsubsec:decorated}
-Now let us provide a brief overview of HOD modeling decorated with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ introduced in [CITE HEARIN2015].
-At a fixed halo mass $M_{\rm h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.We call the first population "type 1" halos, and the second population "type 2 halos.
-Following In the decorated HOD model, the expected number of central and satellite galaxies in the two populations is given by
+\subsubsection{Model with Assembly bias}\label{subsubsec:decorated}
+Now let us provide a brief overview of HOD modeling with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ (known as the decorated HOD) introduced in \citealt{decorated}.
+At a fixed halo mass $M_{h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.
+For simplicity, we call the first population ``type-1'' halos, and the second population ``type-2'' halos.
+In the decorated HOD model, the expected number of central and satellite galaxies in the two populations are given by
 
@@
 \end{eqnarray}
-where $\langle N_{c} | M_{h}\rangle$ and $\langle N_{s} | M_{h}\rangle$ are given by Eqs \ref{hod:central} and \ref{hod:satellite} respectively, and we have $\delta N_{s,0} + \delta N_{s,1} = 0$, and $\delta N_{c,0} + \delta N_{c,1} = 0$.
+where $\langle N_{c} | M_{h}\rangle$ and $\langle N_{s} | M_{h}\rangle$ are given by Eqs \ref{hod:central} and \ref{hod:satellite} respectively, and we have $\delta N_{s,1} + \delta N_{s,2} = 0$, and $\delta N_{c,1} + \delta N_{c,2} = 0$.
 These two conditions ensure the conservation of HOD.
-At a given host hale mass $M_{h}$, the central occupation of the the two populations follows a Nearest-integer distribution with the first moment given by \ref{eq:decoratedcentral}; and the central occupation of the the two populations follows a Poisson distribution with the first moment given by \ref{eq:decoratedsatellite}.
+At a given host halo mass $M_{h}$, the central occupation of the the two populations follows a nearest-integer distribution with the first moment given by \ref{eq:decoratedcentral}; and the satellite occupation of the the two populations follows a Poisson distribution with the first moment given by \ref{eq:decoratedsatellite}.
 
-In this decorated occupation model, the allowable range for the quantities $\delta N_{c,1}$ and $\delta N_{s,1}$ is given by 
+In this occupation model, the allowable range that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take is given by 
 \begin{eqnarray}
--\langle N_{c} | M_{h}\rangle \leq \delta N_{c} \leq \langle N_{c} | M_{h}\rangle
+-\langle N_{c} | M_{h}\rangle \leq \delta N_{c,i} \leq \langle N_{c} | M_{h}\rangle
  , \label{eq:cen-bounds} \\
--\langle N_{s} | M_{h}\rangle \leq \delta N_{s} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
+-\langle N_{s} | M_{h}\rangle \leq \delta N_{s,i} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
 \end{eqnarray}
-Afterwards, CITE[HEARIN2015] defines the assembly bias parameter $\mathcal{A}$ in the following way:
+Afterwards, the assembly bias parameter $\mathcal{A}$ is defined in the following way:
+
 \begin{eqnarray}
-\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \\
-\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0,
+\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \label{positive_A} \\
+\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0, \label{negative_A}
 \end{eqnarray}
@@
 
-At a given halo mass $M_{h}$, once the first moments of occupation statistics for the $type$-1 and $type$-2 halos are determined, the same procedure described in \ref{subsubsec:hod} is done to populate the halos with mock galaxies.
+For a given $\mathcal{A}_{\alpha}$, once $\delta N_{\alpha,1}$ is computed using equation (\ref{positive_A})---if $\mathcal{A}_{\alpha}>0$---or equation (\ref{negative_A})---if $\mathcal{A}_{\alpha}<0$---, $\delta N_{\alpha,2} = 1 - \delta N_{\alpha,1}$ is computed.
+At a fixed halo mass $M_{h}$, once the first moments of occupation statistics for the $type$-1 and $type$-2 halos are determined, we perform the same procedure described in \ref{subsubsec:hod} to populate the halos with mock galaxies.
 
@@
 Once the halo catalogs are populated with galaxies, the real-space positions and velocities of all mock galaxies are obtained.
-The next step is applying a redshift-space distortion transformation.
-Assuming the $\hat{z}$ axis for the direction of the RSD, the transformation $(x,y,z) \rightarrow (s_x,s_y,s_z) = (x , y ,z + v_z/cH_{0})$ is done to obtain the redshift-space coordinate of the produced mock galaxies.
+The next step is applying a redshift-space distortion transformation by assuming plane-parallel approximation.
+Our use of plane parallel approximation is justified because of the shallow depth of the SDSS main galaxy sample considered in this study.
+If we assume that the $\hat{z}$ axis is the line-of-sight direction, then with the transformation $(X,Y,Z) \rightarrow (S_x,S_y,S_z) = (X , Y ,Z + v_{z}(1+z)/H(z))$
+for each galaxy with the real space coordinates $(X,Y,Z)$, velocities $(v_x,v_y,v_z)$, and redshift $z$, we obtain the redshift-space coordinate of the produced mock galaxies.
+Here we assume $z \simeq 0$, and therefore transformation is given by $(X,Y,Z) \rightarrow (X,Y,Z+v_{z}/H_{0})$.
 
 \subsection{Model Observables}
-\subsubsection{group multiplicity function}
-Group multiplicity function $g(N)$ is defined as the abundance of the galaxy groups as a 
-function of group richness (the number of galaxies in groups) per richness width, measured in bins of richness. 
-Galaxy groups in are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF]. 
-The FoF group finder algorithm links to galaxy $i$ and galaxy $j$ to each other, if the projected distance between the two galaxies $D_{\perp , i,j}$ is less than a specified projected linking length $b{_\perp}$, and the line-of-sight distance between the two galaxies $D_{\parallel, i,j}$ is less than a specified line-of-sight linking length $b{_\parallel}$.
-These linking lengths are measured in units of the mean inter-particle distance ($n_{\rm g}^{-1/3}$).
-In order to be consistent with the [CITE BERLIND] measurements, the linking lengths $b_{\perp}$ and $b_{\parallel}$ are set to to 0.15 and 0.74 respectively.
 
-After populating the dark matter halo catalogs with galaxies, we use the $\mathtt{Halotools}$ implementation of the FoF group-finder algorithm to identify the FoF groups with the mentioned linking lengths.
-Afterwards, we compute the number density of the galaxy groups in bins of richness to measure the group multiplicity function.
-Note that $g(N)$ is measured in units of $h^{3}\rm{Mpc}^{-3}$.
-\subsubsection{projected two-point correlation function}
-The projected two point correlation function $w_{\rm{p}}(r_{\rm{p}})$ can be computed by integrating the 3D redshift space 2PCF $\xi(r_{\rm{p}} , \pi)$ along the line-of-sight
+As described in \citealt{decorated} and \citealt{2016arXiv160701782H}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF.
+The accuracy of these fitting functions is limited (\citealt{tinker08,tinker10,watson13}).
+Our approach also does not face the known issues of the treatment of halo exclusion and scale-dependent bias that can lead to significant inaccuracies in halo occupation modeling (see \citealt{vdb13}).
+
+The projected 2PCF $w_{p}(r_{p})$ can be computed by integrating the 3D redshift space 2PCF $\xi(r_{p} , \pi)$ along the line-of-sight (where $r_{\rm p}$ and $\pi$ denote the projected and line-of-sight separation of galaxy pairs respectively):
 \beq
-w_{\rm{p}}(r_{\rm{p}}) = 2 \int_{0}^{\pi_{max}} d\pi \;\xi(r_{\rm{p}} , \pi)
+w_{p}(r_{p}) = 2 \int_{0}^{\pi_{max}}\xi(r_{p} , \pi)\; d\pi
+\label{los}
 \eeq
-For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ [CITE CORRFUNC].
+For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ (\citealt{corrfunc} , available at \url{https://github.com/manodeep/Corrfunc}).
 To be consistent with the SDSS measurements described in \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
-Note that $w_{\rm{p}}(r_{\rm{p}})$ is measured in units of $h^{-1}\rm{Mpc}$.
-
-\subsection{Simulation}
-
-For the simulations used in this work, we make use of the Rockstar (cite[Behroozi]) halo catalogs in the $z=0$ Bolshoi-Planck high 
-resolution $N$-body simulation CITE[Klypin2014]. This simulation was carried out using the adaptive refinement tree code 
-(ART, see cite[Kravstov]) code, following the Planck $\Lambda$CDM cosmological parameters 
-$\Omega_{\rm m} = 0.307$, $\Omega_{\rm b} = 0.048$, $\Omega_{\Lambda} = 0.693$, $\sigma_{8} = 0.823$, $n_{\rm s}=0.96$, 
-$h=0.678$. The Box size for this $N$-body simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, 
-the mass per simulation particle $m_{\rm p}$ is $1.5 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length 
-$\epsilon$ is 1 $h^{-1} \rm{kpc}$.
+Note that $w_{p}(r_{p})$ is measured in units of $h^{-1}\rm{Mpc}$.
+To be consistent with \citealt{guo2015}, we use the same binning (as specified in Section \ref{sec:data}) to measure $w_{\rm p}$.
+In addition to the projected 2PCF, we use the number density given by the number of mock galaxies divided by the comoving volume of the $\mathtt{SMDP}$ simulation.
 
@@
 
-We focus on two sets of measurements made on the volume limited luminosity threshold main sample of galaxies in the SDSS spectroscopic survey.
-In this section, we briefly describe the measurements used in our study for finding constraints on the assembly bias parameters.
+We focus on the measurements made on the volume-limited luminosity-threshold main sample of galaxies in the SDSS spectroscopic survey.
+In this section, we briefly describe the measurements used in our study for finding constraints on the assembly bias as well as the HOD parameters.
 
-\subsection{group multiplicity function}
+The measurements consist of the number density $n_{g}$ and the projected 2PCF $w_{p}(r_{p})$ made by \citealt{guo2015} for volume-limited sample of galaxies in NYU value added galaxy catalog (\citealt{Blanton2005}) constructed from the SDSS DR7 main galaxy sample (\citealt{abazajian2009}).
+In particular, eight volume limited luminosity-threshold samples are constructed with maximum absolute luminosity in $r$-band ($M_{\rm r,max}$) of -18, 18.5, -19, -19.5, -20, -20.5, -21, and -21.5.
+Qualitatively, these samples are constructed in a similar way to those constructed in \citealt{zehavi2011}.
+For detailed differences between the samples in \citealt{guo2015} and \citealt{zehavi2011}, we refer the reader to the Table 1 and Table 2 in these two papers respectively.
 
-The first set of measurements consists of the galaxy number densities $n_{g}$ and the group multiplicity functions $g(N)$ described in [CITE BERLIND 2006]. These measurements are made 
-for the three Volume limited samples of the SDSS galaxies with luminosity thresholds of $M_{r}<-18$, $M_{r}<-19$, and $M_{r}<-20$.
-Galaxy groups in [CITE BERLIND etal] are found by Friends-of-Friends (hereafter FoF) group finder algorithm [CITE FOF].
-[CITE BERLIND ETAL] sets $b_{\perp}$ to 0.15 and $b_{\parallel}$ to 0.74 to minimize the discrepancy between the multiplicity function, projected size, and the number of FoF groups and those of the halos in a suite of simulations.
+The projected 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
+For all luminosity threshold samples, the integration along the line-of-sight (\ref{los}) are performed to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
 
-The measurements are accompanied by two sets of uncertainty measurements.
-The first one is the error on $g(N)$ that stems from the dispersion between $g(N)$ measurements of different mock catalogs.
-The second source of error is the Poisson error that results from the number of groups in each richness bin.
-Finally, these two uncertainties are added in quadrature
-to estimate the total error on [CITE BERLIND ETAL] $g(N)$ measurements.
+The 2PCF measurement of each luminosity threshold sample is accompanied by a covariance matrix constructed using 400 jackknife sub-samples of the data.
+The number density measurements are also accompanied by uncertainties measured using the jackknife method.
+Furthermore, the covariance between the number denisty and the projected 2PCF measurements are neglected.
+As \citealt{norberg} shows, parameter estimation using jackknife covariance matrices is conservative as jackknife overestimate the error in the observations.
 
-\subsection{projected 2PCF}
+The advantage of using these measurements is that the effects of fiber collision systematic errors on the two-point statistics are corrected for (with the method described in \citealt{guo2012}), and therefore, these measurements provide more accurate small scale clustering measurements.
+The assembly bias parameters introduced in section \ref{sec:method} can have a 10-percent level impacts on galaxy clustering (\citealt{decorated}).
+Presence of assembly bias in the satellite population impacts the very small-scale clustering (\citealt{decorated}).
+Moreover as \citealt{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$).
+This scales can be impacted by fiber collision systematics.
+Precise investigation of the possible impact of this signal on the galaxy clustering modeling requires accurate measurements of 2PCF on small scales.
+The method of \citealt{guo2012} is able to recover the true $\wpp$ with  $\sim 6\%$ accuracy in small scales ($r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$) and with $\sim 2.5\%$ at relatively large scales $r_{\rm{p}} \sim 30 \; h^{-1}\rm{Mpc}$.
 
-The second set consists of the number density $n_{g}$ and the projected 2PCF $w_{\rm{p}}(r_{\rm{p}})$.
-The project 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
-These measurements are accompanied by their corresponding covariance matrices constructed using 400 jackknife sub-samples of the data.
-The advantage of using these measurements is that the effects of fiber collision systematics on the two-point statistics are corrected for, and therefore, they provide very accurate small scale clustering measurements [see CITE GUO 2015].
-As [CITE HEARIN2015] demonstrates the satellite assembly bias $\mathcal{A}_{\rm sat}$ can have 10 $\%$ level impact on the small scale galaxy clustering.
+Note that the comoving volume of the $N$-body simulation used in this investigation is 64 $\times 10^{6} \; h^{-3}\rm{Mpc}^{3}$ which is larger than the comoving volume of all the luminosity threshold samples in the SDSS data except the two most luminous samples.
+The comoving volumes of the $M_{\rm r}<-21, \; 21.5$ samples are 71.74 and 134.65 (in units of $10^{6} h^{-3}\rm{Mpc}^{3}$) respectively.
+Since we are only studying not very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.
 
-\section{Analysis and Results}
+\section{Analysis}\label{sec:analysis}
 
-\subsection{Inference setup}
+\subsection{Inference setup}\label{subsec:analysis}
 
-We aim to constrain the parameters of the HOD model described in \ref{subsubsec:hod}, and the parameters of the assembly bias HOD model described in \ref{subsubsec:decorated}, given two sets of SDSS measurements described in \ref{sec:data}.
-For the tests with group multiplicity function as observable, we use measurements with maximum absolute luminosity $M_{\rm r , max}$ of -18, -19, and -20.
-Finally, for the tests with the projected 2PCF, we use measurements with $M_{\rm r , max}$ of -18, -19, -20, and -21.
-
-We sample from the posterior probability distribution $p(\theta|d) \propto p(d|\theta) \pi(\theta)$. In the standard HOD modeling 
+Given the SDSS measurements described in \ref{sec:data}, we aim to constrain the HOD model without assembly bias (described in \ref{subsubsec:hod}), and the HOD model with assembly bias (described in \ref{subsubsec:decorated}) for every luminosity threshold samples, by sampling from the posterior probability distribution $p(\theta|d) \propto p(d|\theta) \pi(\theta)$.
+In the standard HOD modeling
 \beq
-\theta = \{ \mmin, \; \sigmam, \; \mzero, \; \alpha, \; \mone \},
+\theta = \{ \mmin,\;\sigmam,\;\mzero,\; \alpha,\;\mone \},
 \eeq
-and in the Heaviside assembly bias modeling we have 
-\beq
-\theta = \{ \mmin, \; \sigmam, \; \mzero, \; \alpha, \; \mone, \; \acen, \; \asat \},
-\eeq
-Furthermore, data (denoted by $d$) is the combination $[n_{g},g(N)]$ when GMF is used, and $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$ when 2PCF is used.
-
-Now we need to specify the likelihood function $p(d|\theta)$. In the case where the observables are the number density and the GMF are used the negative log-likelihood is given by
+and in the HOD modeling with assembly bias we have 
 \begin{eqnarray}
--2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} \nonumber \\ &+& \sum_{N} \frac{[ g^{\rm data}(N)-g^{\rm model}(N)]^{2}}{\sigma^{2}_{N}} \; + \; \rm{const.},
-\label{eq:lnlike_group}
+\theta = \{\mmin,\; \sigmam, \;\mzero, \;\alpha, \;\mone,\;\acen,\; \asat \},
 \end{eqnarray}
-where the summation is over the group richness bins, and $\sigma_{N}$ is the uncertainty associated with the richness bin $N$.
-In the case, where the number density and 2PCF are used, the negative log-likelihood is given by
+Furthermore, data (denoted by $d$) is the combination of $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$.
+The negative log-likelihood (assuming zero negligible covariance between $n_{g}$ and $w_{\rm{p}}(r_{\rm{p}})$) is given by
 \begin{eqnarray}
--2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} \nonumber \\  
-&+&  \sum_{\rm p} \Delta \wpp^{\rm T}C^{-1}\Delta \wpp \; + \; \rm{const.},
+-2\ln p(d|\theta) &=& \frac{[n^{\rm data}_{g}-n^{\rm model}_{g}]^{2}}{\sigma_{n}^{2}} + \Delta \wpp^{\rm T}\widehat{C^{-1}}\Delta \wpp \; + \; \rm{const.},
 \label{eq:lnlike_wp}
 \end{eqnarray}
-where $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $C^{-1}$ is inverse of the estimate of the jackknife covariance matrix provided by [CITE GUO2015]. 
-Another important ingredient of our analysis is specification of the prior probabilities over the parameters of the two halo occupation models.
-For both model, we use uniform flat priors for all the parameters.
+where $\Delta \wpp$ is a 12 dimensional vector, $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $\widehat{C^{-1}}$ is the estimate of the inverse covariance matrix that is related to the inverse of the jackknife covariance matrix (provided by \citealt{guo2015}) $\widehat{C}^{-1}$, following \citealt{hartlap2007}:
+\beq
+\widehat{C^{-1}} = \frac{N -d - 2}{N -1} \; \widehat{C}^{-1},
+\eeq
+where $N=400$ is the number of the jackknife samples, and $d=12$ is the length of the data vector $w_{p}$.
+Another important ingredient of our analysis is specification of the prior probabilities $\pi(\theta)$ over the parameters of the halo occupation models considered in this study.
+For both models, we use uniform flat priors for all the parameters.
 The prior ranges are specified in the Table \ref{tab:prior}.
-
-\begin{table*}
+Note that a uniform prior between -1 and 1 is chosen for assembly bias parameters, since these parameters are, by definition, bounded between -1 and 1.
+\begin{table}
 \begin{center}
@@
 \end{center}
-\end{table*}
+\end{table}
+
+For sampling from the posterior probability, given the likelihood function (see \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler (\citealt{goodmanweare}) and its implementation $\mathtt{emcee}$ (\citealt{emcee}).
+In particular, we run the $\mathtt{emcee}$ code with 20 walkers and we run the chains for at least 10000 iterations.
+We discard one-third of the chains as burn-in samples and use the reminder of the chains as production MCMC chains.
+Furthermore, we perform Gelman-Rubin convergence test (\citealt{grtest}) to insure that the MCMC chains have reached convergence.
+
+\section{Results and Discussion}\label{sec:result}
+
+\subsection{constraints and interpretations}
+
+Our constraints on the assembly bias parameters fall into two main categories. First, the satellite 
+assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$.
+As shown in Figure \ref{fig:bias}, for all the eight luminosity threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are
+consistent with zero.
+On the other hand, our constraints on the parameter $\acen$---albeit not tightly constrained---show a trend which can be summarized as the following.
+In the most luminous galaxy samples, i.e.
+$M_{\rm r} < -21.5$ and $M_{\rm r} < -21$, $\acen$ is poorly constrained and the constraints are equivalent to zero.
+As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift towards positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$.
+Furthermore, the posterior constraints on the assembly bias parameters in the slightly fainter samples, i.e.
+$M_{\rm r} < -19$ and i.e.
+$M_{\rm r} < -18.5$, are consistent with zero.
+In the faintest galaxy sample, i.e.
+$M_{\rm r} < -18$, our constraints favor negative values of $\acen$.
+
+The underlying theoretical consideration for explaining the assembly bias of the central 
+and satellite galaxies are different.
+The large scale clustering---or the two halo term in the galaxy clustering---is mainly governed by the clustering of the central galaxies.
+The central galaxy clustering can be thought as the weighted average over the halo clustering.
+The large scale bias of the dark matter halo clustering depends not only on mass, but on other the properties of halos beyond mass, such as concentration (\citealt{weschler2006,gao2007,miyatake2016}), spin (\citealt{gao2007}), formation time (\citealt{gao2007, li2008}), and the maximum circular velocity over the accretion history of the halo $V_{\rm max}$ (\citealt{sunayama2016}).
+
+In particular, findings of (\citealt{weschler2006,sunayama2016})
+have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos is larger than that of the low-$V_{\rm max}$ or low-$c$ halos.
+This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$).
+Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}).
+
+Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$.
+From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos at the present time that belonged to higher mass halos at some point in their formation history (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
+Also note that this signal vanishes for the high mass halos.
+
+Consequently, at a fixed halo mass less than $M_{\rm col}$, assignment of more central galaxies to the high-$c$ halos (higher expected number of central galaxies in the high-$c$ halos) gives rise to a boost in the galaxy clustering in the linear scales as well as in regimes corresponding to the one-halo to two-halo transition.
+For the more massive halos ($M \geq M_{\rm col}$), we expect the large-scale clustering boost to reverse sign, and the quasi-linear bump feature to vanish.
+
+Figure \ref{fig:wpmodel} demonstrates the 68$\%$ and 95$\%$ percent posterior predictions for the projected 2PCF $w_{p}$ from the occupation model without assembly bias (shown in red) and the occupation model with assembly bias (shown in blue) for all eight luminosity-threshold samples.
+For the brightest galaxies, $M_{r} < -21.5$ and $M_{r} < -21.0$, the posterior prediction of $w_{p}$ from the two models are consistent with one another.
+Note that these galaxies reside in the most massive halos ($M > M_{\rm col}$) for which the scale-dependence of the halo assembly bias and the difference between the large-scale bias of the high-$c$ and low-$c$ halos become negligible.
+
+Figure \ref{fig:wpres} shows the fractional difference between the 68$\%$ and 95$\%$ percent posterior predictions of $w_p$ and the SDSS data.
+It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the model complex halo occupation model with assembly bias.
+As a result of apportioning more central galaxies to the high-$c$ halos with respect to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and larger scales.
+This can be also noted in significantly lower $\chi^{2}$ values---at the cost more model flexibility and higher degrees of freedom---achieved by the assembly bias model in these luminosity-threshold samples (see Table \ref{tab:constraints}).
+
+In the sample of galaxies with the luminosity threshold $M_{\rm r} < -19, -18.5$, the constraints on $\acen$ become consistent with zero with the tendency towards positive values for the $M_{\rm r}<-19$ sample and towards more negative values for the $M_{\rm r }<-18.5$ sample.
+As shown in Figures \ref{fig:wpmodel} and \ref{fig:wpres}, for the $M_{\rm r}<-19$ ($M_{\rm r}<-18.5$) sample this results in slightly higher (lower) posterior predictions for $w_{p}$ in the intermediate toward large scales.
+Overall, for these two samples, the assembly bias parameters remain largely unconstrained and the decorated HOD model does not yield better $\chi^{2}$ values.
+
+Finally, In the faintest sample ($M_{\rm r} < -18$), negative constraints on the parameter $\acen$ results in higher expected number of centrals in the low-$c$ halos, which at a fixed halo mass, cluster less strongly (in the low mass halos).
+This affects both the large scale bias and the intermediate regimes as a result of the scale-dependent bump feature (see Figures \ref{fig:wpmodel} and \ref{fig:wpres}).
+Furthermore, the model with assembly bias provides better fit to the SDSS data in this luminosity-threshold sample.
+
+The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ (\citealt{prada2012}).
+In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}).
+In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$.
+Note that this is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}).
+The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
+
+The satellite assembly bias can only alter the galaxy clustering at small-to-intermediate scales.
+Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm sat} N_{\rm sat} \rangle$.
+This results in boosting the small-scale clustering, but as pointed out in \citealt{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$.
+Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend halo concentration.
+
+However, our results suggest that for all the 8 luminosity-threshold samples, the satellite assembly bias parameter is largely unconstrained and consistent with zero.
+we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias.
+Group statistics probes the high mass end of the galaxy-halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.
+
+It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range that satisfies the condition $0<\langle N_{\rm cen}|M \rangle<1$.
+As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering.
+As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight.
+This is in keeping with the results of \citealt{guo2015} (which uses the same SDSS data) according to which, the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
+Note that even if $n_{g}$ and $w_{p}$ are used, $\sigmam$ is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end).
+But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter.
+\citealt{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter.
+Tightening of constraints on the scatter parameters leads to reduction of uncertainty in the inferred central assembly bias parameter.
+
+As shown in Table \ref{tab:constraints}, our constraints on the underlying standard HOD model obtained from the model with assembly bias and the model without assembly bias are in good agreement.
+The only cases in which there are (very) mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples.
+However, these tensions are within one-sigma uncertainties.
+For instance, Figure {fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias.
+Also the scatter parameter $\sigmam$ is more tightly constrained in the standard HOD model.
+However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level.
+\citealt{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy-halo connection parameters.
+Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
+
+A few galaxy-halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population.
+\citealt{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
+
+We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$ type galaxies.
+In particular, we consider the abundance matching catalogs produced by \citealt{hw2013}.
+These catalogs have been extensively studies for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences.
+This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}).
+The Box size for this simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, the mass per simulation particle $m_{\rm p}$ is $1.9 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1 $h^{-1} \rm{kpc}$.
+The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}).
+The \citealt{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.
+
+As noted by both \citealt{arz2014},and \citealt{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias.
+This has been shown by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs.
+Randomization is performed in a procedure described in \citealt{arz2014}: the central galaxies among all halos within each of the halo mass bins (with width of 0.1 dex).
+In each mass bin, once the centrals have been shuffled, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo.
+This procedure preserves the HOD, but erases any dependence of the galaxy population on the assembly history of halos such that, assembly bias is erased in the randomized catalog.
+
+For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the \citealt{hw2013} catalogs is shown in Figure \ref{fig:randomized} with the red curves.
+As previously noted by \citealt{arz2014} these catalogs and as it can be seen in Figure $\ref{fig:randomized}$ the difference in $w_{p}$ is only significant in large scales.
+This means that in these catalogs, only the central galaxies are affected by assembly bias which is in agreement with our findings.
+
+Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the origin and catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend.
+That is, we see no difference in the small scale clustering and significant differences as we move towards larger scales.
+Similar to \citealt{hw2013} catalogs, assembly bias becomes less significant as we probe brighter galaxy samples.
+Furthermore, we notice that our mock catalogs favor more modest levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
 
@@
 \begin{center}
-  \label{tab:prior}
-  \caption{{\bf Constraints}: The prior probability distribution 
-  and its range for each of the parameters. 
-  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
-\begin{tabular}{@{}lllllllllllllllllllllllll}
-\\ \hline 
-    Model & Data & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
+  \label{tab:constraints}
+ \caption{{\bf Constraints}: Constraints on the parameters of the HOD models with and without assembly bias. 
+All mass parameters are in unit of $h^{-1}M_\odot$.
+The best-estimates and the error bars correspond to the 50$\%$ quantile and 68$\%$ confidence intervals obtained from the marginalized posterior probability pdfs.
+The last column is $\chi^{2}$ per degrees of freedom ($dof$), where $dof = N_{data} - N_{par}$}
+\begin{tabular}{@{}lllllllllllllllllllllll}
+\hline 
+   $M_{\rm r,lim}$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ \\  \hline
   \\ 
-  HOD & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ & 5.55/1 & 21.55 & 19.42\\ \\
+ -18 & $11.56^{+0.21}_{-0.25}$ &  $1.05^{+0.31}_{-0.52}$ & $10.84^{+0.77}_{-0.59}$ & $0.98^{+0.05}_{-0.05}$ &  $12.50^{+0.10}_{-0.10}$ & $-$ & $-$ & 14.51/8\\\\
 
-  AB & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $0.13^{+0.63}_{-0.75}$ & $-0.01^{+0.60}_{-0.59}$ & 6.46/1 & 34.46 & 25.87\\ \\
+  -18 & $11.53^{+0.23}_{-0.21}$ &  $1.08^{+0.28}_{-0.51}$ & $10.86^{+0.81}_{-0.62}$ & $0.97^{+0.05}_{-0.04}$ &  $12.56^{+0.09}_{-0.10}$ & $-0.67^{+0.55}_{-0.25}$ & $-0.30^{+1.09}_{-0.54}$ & 7.52/6\\ \\
 
-HOD & $\gmf$, $\bar{n}$ & 19 & $11.87^{+0.32}_{-0.23}$ &  $0.70^{+0.53}_{-0.47}$ & $10.93^{+0.74}_{-0.65}$ & $0.99^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ & 5.19/1 & 18.72 & 20.87\\ \\
+-18.5 & $11.67^{+0.29}_{-0.25}$ &  $0.83^{+0.45}_{-0.53}$ & $10.85^{+0.64}_{-0.60}$ & $1.02^{+0.04}_{-0.04}$ &  $12.69^{+0.08}_{-0.08}$ & $-$ & $-$ & 6.17/8\\ \\
 
-AB & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $0.13^{+0.62}_{-0.73}$ & $-0.03^{+0.63}_{-0.59}$ & 6.66/1 & 28.13 & 28.61\\ \\
+-18.5 & $11.60^{+0.31}_{-0.20}$ &  $0.74^{+0.49}_{-0.46}$ & $10.73^{+0.69}_{-0.51}$ & $1.01^{+0.05}_{-0.05}$ &  $12.72^{+0.09}_{-0.10}$ & $0.02^{+0.67}_{-0.62}$ & $0.07^{+0.53}_{-0.59}$ & 6.23/6\\ \\
 
-HOD  & $\gmf$, $\bar{n}$ & 20 & $12.16^{+0.36}_{-0.20}$ &  $0.58^{+0.50}_{-0.36}$ & $10.94^{+0.80}_{-0.66}$ & $0.98^{+0.09}_{-0.08}$ &  $13.07^{+0.07}_{-0.06}$ & $-$ & $-$ & 5.16/1 & 18.32 & 21.26\\ \\
+-19 & $11.74^{+0.37}_{-0.18}$ &  $0.62^{+0.52}_{-0.39}$ & $10.82^{+0.62}_{-0.56}$ & $1.04^{+0.04}_{-0.04}$ &  $12.87^{+0.09}_{-0.09}$ & $-$ & $-$ & 8.69/8\\ \\
 
-AB  & $\gmf$, $\bar{n}$ & 20 & $12.14^{+0.34}_{-0.19}$ &  $0.56^{+0.47}_{-0.35}$ & $10.95^{+0.72}_{-0.64}$ & $0.96^{+0.10}_{-0.07}$ &  $13.08^{+0.07}_{-0.06}$ & $0.04^{+0.68}_{-0.70}$ & $-0.04^{+0.63}_{-0.58}$ & 6.04/1 & 26.63 & 28.57\\ \\
+-19 & $11.71^{+0.37}_{-0.16}$ &  $0.58^{+0.53}_{-0.38}$ & $10.75^{+0.66}_{-0.52}$ & $1.03^{+0.04}_{-0.05}$ &  $12.90^{+0.10}_{-0.09}$ & $0.36^{+0.44}_{-0.62}$ & $-0.01^{+0.56}_{-0.54}$ & 8.87/6\\ \\
 
@@
 
-HOD  & $\wpp$, $\bar{n}$ & 18 & $11.46^{+0.16}_{-0.17}$ &  $1.11^{+0.28}_{-0.47}$ & $10.85^{+0.74}_{-0.59}$ & $1.03^{+0.05}_{-0.06}$ &  $12.54^{+0.10}_{-0.10}$ & $-$ & $-$ & 31.72/13 & 50.29 & 44.55\\ \\
+-19.5 & $11.78^{+0.37}_{-0.13}$ &  $0.51^{+0.53}_{-0.31}$ & $11.09^{+0.69}_{-0.73}$ & $1.06^{+0.03}_{-0.04}$ &  $13.03^{+0.08}_{-0.07}$ & $-$ & $-$ & 6.80/8\\ \\
 
-AB & $\wpp$, $\bar{n}$ & 18 & $11.44^{+0.15}_{-0.15}$ &  $1.20^{+0.21}_{-0.35}$ & $10.91^{+0.79}_{-0.64}$ & $1.02^{+0.06}_{-0.06}$ &  $12.61^{+0.11}_{-0.11}$ & $-0.82^{+0.27}_{-0.14}$ & $0.19^{+0.67}_{-0.73}$ & 31.81/13 & .55 & 19.42 \\ \\
+-19.5 & $11.82^{+0.41}_{-0.17}$ &  $0.62^{+0.54}_{-0.44}$ & $11.11^{+0.68}_{-0.77}$ & $1.03^{+0.04}_{-0.06}$ &  $13.03^{+0.10}_{-0.08}$ & $0.52^{+0.32}_{-0.47}$ & $-0.01^{+0.66}_{-0.49}$ & 5.56/6\\ \\
 
-HOD & $\wpp$, $\bar{n}$ & 18.5 & $11.64^{+0.23}_{-0.24}$ &  $0.89^{+0.43}_{-0.55}$ & $10.75^{+0.65}_{-0.51}$ & $1.06^{+0.05}_{-0.05}$ &  $12.72^{+0.09}_{-0.08}$ & $-$ & $0.37^{+0.44}_{-0.52}$ & 18.11/13 & 36.69 & 30.94\\ \\
+-20 & $12.01^{+0.17}_{-0.08}$ &  $0.32^{+0.32}_{-0.19}$ & $11.69^{+0.54}_{-0.99}$ & $1.08^{+0.03}_{-0.05}$ &  $13.32^{+0.08}_{-0.07}$ & $-$ & $-$ & 13.45/8\\ \\
 
-AB & $\wpp$, $\bar{n}$ & 18.5 & $11.59^{+0.24}_{-0.21}$ &  $0.85^{+0.44}_{-0.54}$ & $10.77^{+0.63}_{-0.52}$ & $1.06^{+0.05}_{-0.06}$ &  $12.78^{+0.10}_{-0.10}$ & $-0.14^{+0.69}_{-0.56}$ & $0.37^{+0.44}_{-0.52}$ & 19.53/13 & 55.93 & 37.48\\ \\
+-20 & $12.23^{+0.39}_{-0.24}$ &  $0.76^{+0.41}_{-0.43}$ & $11.66^{+0.62}_{-0.94}$ & $1.00^{+0.08}_{-0.05}$ &  $13.26^{+0.08}_{-0.09}$ & $0.81^{+0.12}_{-0.26}$ & $-0.15^{+0.33}_{-0.31}$ & 8.12/6\\ \\
 
-HOD & $\wpp$, $\bar{n}$ & 19 & $11.84^{+0.28}_{-0.27}$ &  $0.89^{+0.41}_{-0.51}$ & $10.79^{+0.65}_{-0.54}$ & $1.08^{+0.04}_{-0.04}$ &  $12.89^{+0.09}_{-0.09}$ & $-$ & $-$ & 24.20/13 & 42.77 & 37.03\\ \\
+-20.5 & $12.31^{+0.06}_{-0.06}$ &  $0.21^{+0.14}_{-0.11}$ & $12.36^{+0.27}_{-0.77}$ & $1.11^{+0.08}_{-0.08}$ &  $13.56^{+0.09}_{-0.09}$ & $-$ & $-$ & 11.40/8\\ \\
 
-AB & $\wpp$, $\bar{n}$ & 19 & $11.78^{+0.30}_{-0.24}$ &  $0.81^{+0.48}_{-0.51}$ & $10.77^{+0.66}_{-0.53}$ & $1.07^{+0.04}_{-0.05}$ &  $12.95^{+0.10}_{-0.10}$ & $0.15^{+0.52}_{-0.61}$ & $0.52^{+0.33}_{-0.44}$ & 22.80/13 & 59.20 & 40.75\\ \\
+-20.5 & $12.37^{+0.16}_{-0.09}$ &  $0.44^{+0.28}_{-0.26}$ & $12.38^{+0.27}_{-0.54}$ & $1.05^{+0.08}_{-0.07}$ &  $13.60^{+0.10}_{-0.08}$ & $0.81^{+0.15}_{-0.43}$ & $-0.11^{+0.26}_{-0.27}$ & 6.82/6\\ \\
 
-HOD & $\wpp$, $\bar{n}$ & 19.5 & $11.85^{+0.31}_{-0.19}$ &  $0.66^{+0.46}_{-0.40}$ & $10.88^{+0.67}_{-0.59}$ & $1.13^{+0.04}_{-0.04}$ &  $13.07^{+0.07}_{-0.07}$ & $-$ & $-$ & 15.89/13 & 34.46 & 28.72\\ \\
+-21 & $12.73^{+0.14}_{-0.07}$ &  $0.32^{+0.22}_{-0.17}$ & $12.62^{+0.48}_{-1.36}$ & $1.17^{+0.10}_{-0.16}$ &  $14.01^{+0.08}_{-0.10}$ & $-$ & $-$ & 7.34/8\\ \\
 
-AB & $\wpp$, $\bar{n}$ & 19.5 & $11.82^{+0.38}_{-0.18}$ &  $0.63^{+0.55}_{-0.40}$ & $10.83^{+0.74}_{-0.57}$ & $1.10^{+0.04}_{-0.05}$ &  $13.07^{+0.08}_{-0.08}$ & $0.35^{+0.40}_{-0.52}$ & $0.03^{+0.59}_{-0.41}$ & 23.17/13 & 37.17 & 41.12\\ \\
+-21 & $12.81^{+0.28}_{-0.11}$ &  $0.47^{+0.41}_{-0.25}$ & $12.51^{+0.61}_{-1.17}$ & $1.08^{+0.17}_{-0.13}$ &  $14.02^{+0.08}_{-0.10}$ & $0.33^{+0.51}_{-0.64}$ & $-0.18^{+0.41}_{-0.35}$ & 7.21/6\\ \\
 
-HOD & $\wpp$, $\bar{n}$ & 20 & $11.99^{+0.15}_{-0.08}$ &  $0.36^{+0.28}_{-0.21}$ & $11.05^{+0.76}_{-0.71}$ & $1.17^{+0.04}_{-0.04}$ &  $13.34^{+0.07}_{-0.07}$ & $-$ & $-$ & 18.71/13 & 37.28 & 31.54\\ \\
+-21.5 & $13.44^{+0.11}_{-0.09}$ &  $0.60^{+0.09}_{-0.11}$ & $12.57^{+0.77}_{-1.27}$ & $1.33^{+0.07}_{-0.21}$ &  $14.53^{+0.05}_{-0.07}$ & $-$ & $-$ & 3.29/8\\ \\
 
-AB & $\wpp$, $\bar{n}$ & 20 & $12.13^{+0.39}_{-0.18}$ &  $0.65^{+0.47}_{-0.38}$ & $11.14^{+0.80}_{-0.77}$ & $1.11^{+0.06}_{-0.06}$ &  $13.31^{+0.09}_{-0.09}$ & $0.71^{+0.21}_{-0.41}$ & $0.02^{+0.49}_{-0.33}$ & 15.22/13 & 51.62 & 33.17\\ \\
+-21.5 & $13.43^{+0.12}_{-0.06}$ &  $0.60^{+0.12}_{-0.08}$ & $12.59^{+0.64}_{-1.25}$ & $1.27^{+0.11}_{-0.19}$ &  $14.54^{+0.05}_{-0.05}$ & $-0.24^{+0.50}_{-0.40}$ & $-0.30^{+0.86}_{-0.49}$ & 3.37/6\\ \\
 
@@
 
-For sampling from the posterior probability, given the likelihood function (see Eqs.
-\ref{eq:lnlike_group}, \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
-In particular, we run the $\mathtt{emcee}$ code with 140 walkers and we run the chains for at least 15000 iterations until the convergence of the MCMC chains is ensured.
-For testing the convergence of the chains, we perform Gelman-Rubin convergence test [CITE GELMANANDRUBIN and the other paper].
-
-\subsection{results}
-
 \subsection{model comparison}
 
-Now that we have presented constraints on the parameters of the Heaviside assembly bias HOD model and those found from the standard HOD model using the group and clustering measurements of the SDSS galaxies, it is necessary to make comparison between the the two models in terms of the goodness of fit.
-Evidently, the Heaviside Assembly bias model has more complexity for modeling the halo occupation.
-The question that arises is whether this higher level of model complexity is more preferable by the group statistics and the clustering data used in this study.
+We want to address this question that whether the constraints on the model with assembly bias and the model without assembly bias given the galaxy clustering data lead us to claim that assembly bias is strongly supported by the observations or not.
+Within the standard HOD framework, the distribution of the galaxies is modeled using a simple description based on the $mass$-only ansatz: $P(N|M)$.
+The decorated HOD model however, provides a more complex description of the data by adding a secondary halo property (halo concentration in this study) and a more flexible occupation model: $P(N|M,c)$.
 
-There are various methods for model comparison.
-In this work we make use of two model comparison criteria: \emph{Akaike Information Criterion} (AIC, see CITE ...
-), and \emph{Bayesian Information Criteria} (BIC, see CITE ....).
-AIC and BIC are two widely used methods for assessing the relative quality of models given a set of observations.
-Suppose that $\mathcal{L}_{\rm max}$ is the maximum likelihood of the data given a model, $N_{\rm par}$ is the number of parameters of a given model, and $N_{\rm data}$ is the number of data points.
+In order to investigate whether the higher level of model complexity is demanded by the observations or not, we present model comparison between the models with and without assembly bias.
+In particular, we make use of two simple methods for model comparison: \emph{Akaike Information Criterion} (AIC, \citealt{aic} , see \citealt{gelmanic} for detailed discussion on AIC), and \emph{Bayesian Information Criteria} (BIC, \citealt{bic}).
+BIC and AIC are more computationally tractable than alternatives approaches such as computing the fully marginalized likelihood.
+The underlying assumption of these information criteria is that models that yield higher likelihoods are more preferable, but at the same time, models with more flexibility are penalized.
+
+Suppose that $\mathcal{L}^{\star}$ is the maximum likelihood achieved by the model, $N_{\rm par}$ is the number of free parameters in the model, and $N_{\rm data}$ is the number of data points in the data set.
 Then we have
@@
 \begin{eqnarray}
-AIC&=& -2\;\ln \mathcal{L}_{\rm max} + 2N_{\rm par} + 2\;\frac{N_{\rm par}(N_{\rm par}+1)}{N_{\rm data}-N_{\rm par}-1} \; , \label{eq:aic}\\
-BIC&=& -2\;\ln \mathcal{L}_{\rm max} + N_{\rm par}\;\ln N_{\rm data} \; . \label{eq:bic}
+\rm{BIC}&=& -2\;\ln \mathcal{L}^{\star} + N_{\rm par}\;\ln N_{\rm data} \; , \label{eq:bic} \\
+\rm{AIC}&=& -2\;\ln \mathcal{L}^{\star} + 2N_{\rm par} \; . \label{eq:aic}
+%         &+& 2\;\frac{N_{\rm par}(N_{\rm par}+1)}{N_{\rm data}-N_{\rm par}-1} \; . \label{eq:aic}
 \end{eqnarray}
-Models that deliver lower values of information criteria are more favorable.
-In Eqs.
-(\ref{eq:aic}) and (\ref{eq:bic}) $N_{\rm par}$ is 5 when the standard HOD model is used, and 7 when the Heaviside assembly bias model is used.
-When the observables are $\ngal$ and $\wpp$, $N_{\rm data}$ is 13 for all luminosity thresholds, and when the observables are $\ngal$ and $\gmf$, $N_{\rm data}$ is 16 for the $\mr < -18$ luminosity threshold, 23 for the $\mr < -19$ luminosity threshold, and 25 for the $\mr < -20$ luminosity threshold.
 
-\section{Discussion}
+Given a data set, models with lower value of AIC and BIC are more desired.
+That is, in order for the higher model complexity (given by $N_{\rm par}$) to be justified, $\mathcal{L}^{\star}$ must be sufficiently higher.
+Therefore in this formulation, models that deliver lower information criteria scores are more preferable.
 
-%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%
+Figure \ref{fig:ic} shows that the comparison between the BIC and AIC scores for the model with assembly bias and the model without assembly bias shows that the model without assembly bias is still preferable by the galaxy clustering observations.
+That is, although some improvements to fitting the clustering data cen be achieved as a result of using a more complicated model, these improvements are not significant enough to justify the use of a more complicated model that takes assembly bias into account.
+
+We note that both AIC and BIC scores improve in the luminosity-threshold samples for which, we have tighter constraints over the central assembly bias parameter.
+This supports our intuition that AIC and BIC penalize unconstrained parameters.
+Also note that, the difference between both BIC and AIC scores are marginal.
+That is, although the HOD model is preferred, it is not strongly preferred by the data.
+
+\subsection{choice of simulation}
+
+  We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation.
+The summary of constraints are shown in Figure \ref{fig:bias_comparison}.
+In Figure \ref{fig:bias_comparison}, the constraints from the $\mathtt{SMDP}$ and the $\mathtt{BolshoiP}$ simulations are shown with circles and crosses respectively.
+Furthermore, the upper and lower bounds on the inferred parameters reported by \citealt{zentner2016} in the shaded blue regions.
+In the case of central assembly bias, all three constraints are consistent.
+For the luminosity-thresholds samples $M_{\rm r}<-20.5, -20, -19.5$, where the central assembly bias parameters are strongly positive, the constraints obtained from the $\mathtt{SMDP}$ simulation are tighter.
+
+In the case of the satellite assembly bias parameters however, constraints from the $\mathtt{BolshoiP}$ simulation for the luminosity threshold samples $M_{\rm r}<-20.5, -19$ favor positive values of the parameter, while our constraints from the $\mathtt{SMDP}$ simulation for these two luminosity thresholds are consistent with zero.
+As it is shown in the lower panel of Figure \ref{fig:bias_comparison}, our constraints from the $\mathtt{BolshoiP}$ simulations are consistent with lower and upper bounds (shown with the shaded blue region) reported by \citealt{zentner2016} that uses the same simulation but slightly different $w_{p}$ measurements (\citealt{zehavi2011}).
+
+The marginalized posterior PDFs over $\asat$ are shown in Figure \ref{fig:asat_comparison}.
+Note that $\asat$ is poorly constrained in both simulations and for both samples.
+For the $M_{\rm r}<-19$ sample, given how poorly constrained the parameters are, the discrepancy between the constraints is not very stark.
+Note that the tension between the inferred parameters is still at a one-sigma level.
+The disagreement however, becomes more pronounced in the $M_{\rm r}<-20.5$ sample.
+This can possibly be attributed to the different size and resolution of the simulation boxes.
+
+In terms of the effect of assembly bias on galaxy clustering, note that mocks created using the inferred parameters with the $\mathtt{SMDP}$ simulation show the same behavior as we observe in the abundance matching catalogs of \citealt{hw2013} and \citealt{lehman2015}.
+In those catalogs, the difference in $w_{p}$ between the mock catalogs and the randomized catalogs is mostly on large scales where the clustering is governed by the central galaxies.
+
+\section{Summary and Conclusion}\label{sec:summary}
+
+In this investigation, we provide constraints on the concentration-dependence of halo occupation for a wide range of galaxy luminosities in the SDSS data.
+In particular, the modeling is done in the context of the decorated HOD model \citealt{decorated}, and the data used in this investigation is the projected 2PCF measurements published by \citealt{guo2015}.
+We make use of $\mathtt{SMDP}$ high resolution $N$-body simulation that enables us to reliably perform inference for the faintest galaxy samples in the SDSS DR7 catalog that live in low mass halos, and the brightest galaxy samples that occupy large comoving volumes.
+
+Our findings suggest that the satellite assembly bias remains consistent with zero.
+However, our constraints on the central assembly bias parameter exhibit a trend with the luminosity limits of the galaxy samples.
+For the brightest samples, central assembly bias is consistent with zero, which is in agreement with this picture that the halo assembly bias becomes negligible for the most massive halos.
+
+For the $M_{\rm r}<-20.5, -20, -19.5$ samples, we find positive correlation between the central population and halo concentration at fixed halo mass.
+For $M_{\rm r}<-19, -18.5$ we find no correlation, and for the faintest sample, we find negative correlation.
+Given the large scale halo assembly bias and the scale-dependent feature of it in the quasi-linear scales, these constraints lead to improvement in modeling the galaxy clustering.
+But we do not find these improvements to be sufficient to lower the information criteria scores associated with the more complex models with the exception of $M_{\rm r}<-20,-18$ luminosity-threshold samples for which we find the strongest constraints on the central assembly bias.
+For these two samples, the HOD model with assembly bias yields lower BIC score than the model without assembly bias.
+
+Comparison of the levels of assembly bias in the catalogs predicted from our constraints and \citealt{hw2013} catalogs demonstrates that our mock catalogs support more modest levels of assembly bias which follows the same trend: assembly bias in the central population which vanishes in the brightest samples.
+
+\section*{Acknowledgments}
+
+We are grateful to David~W.~Hogg, Yao~Yun Mao, Andrew Hearin, Chang~Hoon~Hahn, Andrew Zentner, Tomomi Sunayama, Kilian~W.~Walsh, and Chia~Hsun~Chuang for
+discussions related to this work.
+All the computations in this work were carried out in the New York University High Performance Computing Mercer facility.
+We thank Shenglong~Wang, the administrator of the NYU HPC center for his continuous and consistent support throughout the completion of this study.
+
+All of the code written for this project is available in an open-source
+code repository at \url{https://github.com/mjvakili/gambly}. All the MCMC chains of our analysis will be available upon request.
+The SDSS clustering measurements and the covariance matrices used in this work are available at \url{http://sdss4.shao.ac.cn/guoh/files/wpxi_measurements_Guo15.tar.gz}.
+Description of the Small MultiDark Planck halo catalog used in this investigation can be found at \url{https://www.cosmosim.org/cms/simulations/smdpl/smdpl-rockstar/}, and the RockStar halo catalog of the SMDP simulation is publicly available at \url{http://yun.ucsc.edu/sims/SMDPL/hlists/index.html}.
+
+\clearpage
+
+%%%%%%%%%%%%%%%% FIGURES %%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-Mr18-posterior 
+% ACEN and ASAT constraints
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post18_0gmf.pdf}
-\caption{We present the constraints on the Heaviside assembly bias HOD model parameters (blue) and the standard HOD model parameters (yellow) obtained from our analysis using $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -18$.
-The diagonal panels plot the marginalized posterior distribution of each parameter with vertical dashed lines marking the $50\%$ quantile and of the distribution.
-The off-diagonal panels plot the degeneracies between parameter pairs.
-The range of each panel corresponds to the range of our prior choice.
-The parameters $\acen$ and $\asat$ are only defined for the Assembly bias model.
-For both models, the parameter $\sigmam$ remains unconstrained.
-In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
-The parameter $\alpha$ does not have a  lower bound constraint in both models.
-The constraints on the parameters $\mzero$, $\mmin$, $\alpha$, $\mone$ found from the two models are in strong agreement.}
-\label{fig:post_gmf_18}
+\includegraphics[width=0.8\textwidth]{bias2.pdf}
+\caption{Constraints on the central assembly bias $\acen$ (Top panel) and the satellite assembly bias $\asat$ (Bottom panel) parameters. }
+\label{fig:bias}
 \end{center}
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-Mr19-posterior 
+% WP MODEL
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post19_0gmf.pdf}
-\caption{Same as Figure \ref{fig:post_gmf_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -19$.
-Again, For both models, the parameter $\sigmam$ remains unconstrained.
-In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
-The  marginalized posterior pdf over the parameter $\alpha$ found from the standard HOD model is peaked at a slightly higher value of $\alpha$ than the one found from the assembly bias HOD model.
-The constraints on the parameters $\mzero$, $\mmin$, and $\mone$ found from the two models are in strong agreement.}
-\label{fig:post_gmf_19}
+\includegraphics[width=\textwidth]{wpmodel.pdf}
+\caption{Comparison between the posterior predictions of $w_{p}(r_{p})$ and the SDSS $w_{p}(r_{p}$ measurements.
+Predictions from the standard HOD model (HOD model with assembly bias) are shown in red (blue).
+The Dark and light shaded regions mark the 68$\%$ and the 95$\%$ confidence intervals.
+The errorbars are the from the diagonal elements of the covariance matrix.}
+\label{fig:wpmodel}
+\end{center}
+\end{figure*}
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% WPRES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[p]~\\
+\begin{center}
+\includegraphics[width=\textwidth]{wpres.pdf}
+\caption{Same as Figure \ref{fig:wpmodel}, but showing the fractional difference between the posterior predictions and the observed projected 2PCF for all the luminosity threshold.
+In all luminosity threshold samples, predictions of the two models for small scale clustering are consistent.
+In the samples that favor more positive values of the central assembly bias parameter ($M_{\rm r}<-19.5,-19,-20,-20.5$), modeling of the intermediate and large-scale clustering is slightly improved.
+The large-scale clustering modeling of the $M_{\rm r}<-18$ sample is also improved because of negative constraints on $\acen$.}
+\label{fig:wpres}
 \end{center}
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-Mr20-posterior 
+% WP RANDOMIZED
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post20_0gmf.pdf}
-\caption{Same as Figure \ref{fig:post_gmf_20} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -20$.
-In The assembly bias model, $\acen$ and $\asat$ remain largely unconstrained.
-The  marginalized posterior pdf over the parameter $\alpha$ found from the standard HOD model is peaked at a slightly higher value of $\alpha$ than the one found from the assembly bias HOD model.
-The constraints on the parameters $\sigmam$, $\mzero$, $\mmin$, and $\mone$ found from the two models are in strong agreement.}
-\label{fig:post_gmf_20}
+\includegraphics[width=\textwidth]{paper_wprandom.pdf}
+ \caption{Demonstration of the relative difference in $w_{p}$ between randomized and non-randomized catalogs for different luminosity threshold samples: $M_{\mathrm r}<-20,-20.5,-21.5$.
+The errorbars show the diagonal elements of the covariance matrix.
+The blue lines correspond to the random draws from the posterior probability (summarized in Table \ref{tab:constraints}) over the parameters of the HOD model with assembly bias.
+The red line corresponds to the subhalo abundance matching catalog (\citealt{hw2013,hearin2014}).
+Comparison between the level of assembly bias (encoded in the relative difference in $w_p$) shows that the our constraints favor \emph{more} \emph{moderate} levels of assembly bias than the levels seen in the abundance matching mock catalogs.
+Within both models, the small scale clustering remains unaltered after randomizing the catalogs, signaling the lack of correlation between the satellite population and the halo concentration in the two models.}
+\label{fig:randomized}
 \end{center}
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-Mr18-posterior 
+% Information Criteria
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post18_0wp.pdf}
-\caption{We present the constraints on the Heaviside assembly bias HOD model parameters (blue) and the standard HOD model parameters (yellow) obtained from our analysis using $\bar{n}$ and $\wpp$ measurements of galaxies with $\mr < -18$.
-The diagonal panels plot the marginalized posterior distribution of each parameter with vertical dashed lines marking the $50\%$ quantile and of the distribution.
-The off-diagonal panels plot the degeneracies between parameter pairs.
-The range of each panel corresponds to the range of our prior choice.
-The parameters $\acen$ and $\asat$ are only defined for the Assembly bias model.
-For both models, the parameter $\sigmam$ remains unconstrained.
-In The assembly bias model, $\asat$ remains largely unconstrained.
-The constraint on the parameter $\acen$ however, indicates that negative values of this parameter are strongly favored.
-Specifically the best-fit value of $\acen$ is -0.82 with its 68$\%$ confidence interval being less than -0.55.
-The constraints on $\mzero$ and $\mmin$ found from the two models strongly agree.
-The constraints on $\alpha$ and $\mone$ found from the two model in overall agreement with a slightly higher value of $\alpha$ and a slightly lower value of $\mone$ in the standard HOD model.}
-\label{fig:post_wp_18}
+\includegraphics[width=0.8\textwidth]{IC.pdf}
+\caption{Difference in the information criteria between the HOD model with assembly bias and the model without assembly bias.
+$\bf{Top}$: $\Delta$BIC = BIC(with assembly bias) - BIC(without assembly bias).
+$\bf{Bottom}$: $\Delta$AIC = AIC(with assembly bias) - AIC(without assembly bias).
+According to BIC (AIC), the more complex model with assembly bias is favored once $\Delta$BIC$<0$ ($\Delta$AIC$<0$).
+Both $\Delta$BIC and $\Delta$AIC are lower for the samples with tighter constraints over the central assembly bias parameter $\acen$, with $\Delta$BIC being (marginally) negative only for $M_{\rm r}<-20,-18$ samples that yield strongest constraints on $\acen$.}
+\label{fig:ic}
 \end{center}
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-Mr19-posterior 
+% BIAS COMPARISON
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post19_0wp.pdf}
-\caption{Same as Figure \ref{fig:post_wp_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -19$.
-Once again, the parameter $\sigmam$ remains unconstrained.
-$\acen$ is not constrained in the assembly bias model, but constraints on $\asat$ show that positive values of $\asat$ are strongly favored.
-The best-fit value of $\asat$ is 0.52 and its 68$\%$ confidence interval is larger than 0.08.
-The constraints on $\mzero$, $\mmin$, $\alpha$, and $\mone$ found from the two models are in good agreement, with $\alpha$ being slightly higher and $\mone$ being slightly lower in the standard HOD model.}
-\label{fig:post_wp_19}
+\includegraphics[width=0.8\textwidth]{bias_comparison.pdf}
+\caption{Comparison between the constraints on the assembly bias parameters $\acen$ (shown in the top panel) and $\asat$ (shown in the bottom panel) for different simulations: $\mathtt{SMDP}$ (shown with circle), and $\mathtt{BolshoiP}$ (shown with cross).
+The errorbars mark the 68$\%$ uncertainty over the parameters.
+Shaded blue regions show the upper and lower bounds found by \citealt{zentner2016} that uses the $\mathtt{BolshoiP}$ and clustering measurements of \citealt{zehavi2011}.
+The central assembly bias constraints found from the two simulations are consistent, with the constraints for from the $\mathtt{SMDP}$ simulation being tighter for the most luminous samples.
+The constraints on $\asat$ from the two simulations are in agreements with the exception of $M_{\rm r}<-19 ,\; -20.5$ samples that favor more positive values of $\asat$ when the $\mathtt{BolshoiP}$ simulation is used.}
+\label{fig:bias_comparison}
 \end{center}
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-Mr20-posterior 
+% ASAT DISCREPANCY
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[width=\textwidth]{post20_0wp.pdf}
-\caption{Same as Figure \ref{fig:post_wp_18} but for $\bar{n}$ and $\gmf$ measurements of galaxies with $\mr < -20$.
-For this sample of galaxies, the parameter $\sigmam$ is better constrained by the two models, with the constraints coming from the standard HOD model being tighter.
-$\asat$ is not constrained in the assembly bias model and is consistent with zero, but constraints on $\acen$ show that positive values of $\acen$ are strongly favored.
-The best-fit value of $\acen$ is 0.71 and its 68$\%$ confidence interval is larger than 0.30.
-The constraints on $\mzero$ and $\mone$ found from the two models are in good agreement.
-There is some discrepancy between the constraints on $\mmin$ and $\alpha$ from the standard HOD model and  the ones from the HOD model with assembly bias.
-In the standard HOD model, the constraints on $\alpha$ are slightly narrower and favor larger values of $\alpha$.
-The best-fit and the 1-sigma uncertainties of $\alpha$ are 1.17$^{+0.04}_{-0.04}$ and 1.11$^{+0.06}_{-0.06}$ for the standard and the assembly bias model respectively.
-In the standard model, the constraint on $\mmin$ is narrower and favors smaller values of $\mmin$.
-The best-fit and the 1-sigma uncertainties of $\mmin$ are 11.99$^{+0.15}_{-0.08}$ and 12.13$^{+0.39}_{-0.18}$ for the standard and the assembly bias model respectively.}
-\label{fig:post_wp_20}
+\includegraphics[width=\textwidth]{hist_comparison.pdf}
+\caption{Demonstration of constraints over the satellite assembly bias parameters from luminosity threshold samples $M_{\rm r}<-19 ,\; -20.5$, for two different simulations: $\mathtt{BolshoiP}$ (yellow), and $\mathtt{SMDPL}$ (green).
+The $\asat$ constraints found using the $\mathtt{BolshoiP}$ simulation is favor more positive values of $\asat$, while the constraints found using the $\mathtt{SMDP}$ simulation are consistent with no satellite assembly bias.}
+\label{fig:asat_comparison}
 \end{center}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-prediction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{paper_model_decgmf.pdf}
-\includegraphics[width=\textwidth]{paper_model_hodgmf.pdf}
-\caption{We compare the posterior prediction for the observable $\gmf$ to the Berlind+06 measurements in three Luminosity threshold samples: $\mr<-18$, $\mr<-19$, and $\mr<-20$.
-The darker and the lighter shaded regions represent the 68$\%$ and the 95$\%$ confidence regions of the posterior predictions.
-$\bf{Top \; panel}$: 1-sigma and 2-sigma posterior prediction of the Heaviside Assembly bias HOD model.
-$\bf{Bottom \; panel}$: 1-sigma and 2-sigma posterior predictions of the the standard HOD model.}
-\label{fig:gmf-predictions}
-\end{figure*}
+\clearpage
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gmf-occupation-prediction
+% EXAMPLE POSTERIOR PDF
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{paper_abhod_ncengmf.pdf}
-\includegraphics[width=\textwidth]{paper_abhod_nsatgmf.pdf}
-\includegraphics[width=\textwidth]{paper_abvshod_gmf.pdf}
-
-\caption{We demonstrate the posterior predictions for the expected occupation statistics of galaxies.
-The shaded regions mark the 68 $\%$ confidence region of the posterior predictions.
-The observables used in fitting are $\bar{n}$ and $\gmf$.
-$\bf{Top \; panel}$: posterior predictions for the expected number of centrals as a function of halos for the two population of halos: $type$-1 (high concentration, sown with blue) and $type$-2 (low concentration, shown with yellow) halos.
-}
-\label{fig:gmf-hod-predictions}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-prediction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure*}[p]~\\
 \begin{center}
-\includegraphics[scale = 0.3]{paper_model_decwp.pdf} \\
-\includegraphics[scale = 0.3]{paper_model_hodwp.pdf}
-\caption{We compare the posterior prediction for the observable $\wpp$ to the Guo+15 measurements in five Luminosity threshold samples: $\mr<-18$, $\mr<-18.5$, $\mr<-19$, $\mr<-19.5$, and $\mr<-20$.
-The darker and the lighter shaded regions represent the 68$\%$ and the 95$\%$ confidence regions of the posterior predictions.
-$\bf{Top\;panel}$: 1-sigma and 2-sigma posterior prediction of the Heaviside Assembly bias HOD model.
-$\bf{Bottom\;panel}$: 1-sigma and 2-sigma predictions of the the standard HOD model.}
-\label{fig:wp-predictions}
+\includegraphics[width=\textwidth]{post20_5combined.pdf}
+\caption{An example of posterior probability distribution over the parameters of the standard HOD model with no assembly bias (shown with yellow), and the HOD model with assembly bias (shown in blue).
+These constraints are obtained from the clustering measurements of the $M_{\rm r} < -20.5$ luminosity threshold sample.
+The dark (light) blue shaded regions show the 68$\%$ (95 $\%$) confidence intervals.
+The constraints on $\acen$ and $\asat$ show positive correlation between the central fraction and the halo concentration at fixed halo mass, and lack of correlation between the satellite fraction and halo concentration at fixed halo mass.}
+\label{fig:posterior}
 \end{center}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% wp-occupation-prediction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{paper_abhod_ncenwp.pdf}
-\includegraphics[width=\textwidth]{paper_abhod_nsatwp.pdf}
-\includegraphics[width=\textwidth]{paper_abvshod_wp.pdf}
-
-\caption{}
-\label{fig:wp-hod-predictions}
-\end{figure*}
-
-\section*{Acknowledgments}
-We would like to thank Michael R. Blanton,  
-Boris Leidstadt, Geoffrey~S.~Ryan, and the Blanton-Hogg group meeting for insightful discussions. MV was supported by NSF grant AST-1517237. DWH was supported 
-by NSF (grants IIS-1124794 and AST-1517237), NASA (grant NNX12AI50G), and the Moore-Sloan 
-Data Science Environment at NYU. Computations 
-were performed using computational resources at NYU-HPC. We thank Shenglong Wang, the 
-administrator of NYU-HPC computational facility, for his consistent and continuous support 
-throughout the development of this project. We also thanks Dan Foreman-Mackey for providing some of the computational resources at the early stages of this work.
+\bibliographystyle{yahapj}
+\bibliography{assemble}
 
 \end{document}
+
+%%
+%% End of file `sample.tex'.`

### 2016-09-16 text/ms.tex
incorporating comments

@@
-\documentclass[12pt, preprint]{aastex}
+ss[12pt, preprint]{aastex}
 \usepackage[breaklinks,colorlinks, 
@@
 
-\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University, 4 Washington Pl, New York, NY, 10003}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl, New York, NY, 10003}
 
@@
 
-Clustering of dark matter halos is shown to depend on halo properties beyond mass such as halo concentration.
+Clustering of dark matter halos has been shown to depend on halo properties beyond mass such as halo concentration.
 This phenomenon is referred to as halo assembly bias.
-Standard halo occupation modeling in large scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
-Modeling of galaxy clustering can face systematic effects if galaxies are correlated with other halo properties.
-Using the Small MultiDark-Planck high resolution $N$-body simulation and the measurements of the projected two-point correlation function and the number density of Sloan Digital Sky Survey (SDSS) DR7 main galaxy sample, we investigate the extent to which the dependence of halo occupation on halo concentration can be constrained, and to what extent this can improve our modeling of galaxy clustering.
+Standard halo occupation modeling (HOD) in large-scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
+Modeling of galaxy clustering can face systematic effects if the number or properties of galaxies are correlated with other halo properties.
+Using the Small MultiDark-Planck high resolution $N$-body simulation and the measurements of the projected two-point correlation function and the number density of Sloan Digital Sky Survey (SDSS) DR7 main galaxy sample, we investigate the extent to which the dependence of halo occupation on halo concentration can be constrained, and to what extent allowing for this dependence can improve our modeling of galaxy clustering.
 
@@
 
-We show that in comparison with abundance matching mock catalogs, our findings suggest more modest levels of assembly bias.
+We show that in comparison with abundance-matching mock catalogs, our findings suggest modest levels of assembly bias.
 Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
@@
 
-Most theories of cosmology and large scale structure formation under consideration today rely on the central assumption that galaxies reside in dark matter halos.
-Detailed study of the galaxy-halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
+Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark-matter halos.
+Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
 One of the most powerful methods for describing the galaxy-halo connection is the halo occupation
@@
 
-Despite this very simplifying assumption, the models of galaxy-halo connection based on HOD modeling have been used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy-galaxy lensing with remarkable success (e.g.
+Despite this very simplifying assumption, the models of galaxy-halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g.
 \citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}).
-HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy lensing (\citealt{vdb03,cacciato13,more13,vdb13}) in the main sample of galaxies
+HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy weak lensing (\citealt{vdb03,cacciato13,more13,vdb13}) in the main sample of galaxies
 of the Sloan Digital Sky Survey (hereafter SDSS, \citealt{york2000}), and also the combination of galaxy clustering and galaxy-galaxy lensing (\citealt{more15}) in SDSS III Baryon Oscillation Spectroscopic Survey (BOSS, \citealt{boss}).
@@
 formation. Numerous $N$-body simulations that examine the clustering of 
-dark matter halos argue halo clustering is correlated with the formation 
+dark matter halos argue that halo clustering is correlated with the formation 
 history of halos. That is, at a fixed halo mass, the halo bias is correlated 
-with properties of halos beyond mass such as the concentration, formation time, or etc. 
-This phenomenon is known as the halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}). 
+with properties of halos beyond mass, such as the concentration, formation time, or etc. 
+This phenomenon is known as halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}). 
 There is even support for halo assembly bias in observations (\citealt{miyatake2016,more2016}).
 
-Furthermore, the properties of galaxies within the halo, may also depend on the halo's formation history.
-Then, we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos, environment, and etc.
-There have been many attempts in the literature in examining the dependence of the galaxy properties on larger scale environment of the halos.
-But the results are mixed and there is very little consensus over this matter.
-\citealt{tinker_void_2009} shows that the properties of the galaxies that reside in voids can be explained by the halo mass in which they live, and their properties are independent of their large scale environment of the halos.
-\citealt{tinker_density_hod} proposes and extension the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
+Furthermore, the properties of galaxies within the halo may also depend on the halo's formation history.
+Then we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos, environment, and etc.
+There have been many attempts in the literature at examining the dependence of galaxy properties on larger scale environment of the halos.
+But the results are mixed, and there is very little consensus.
+\citet{tinker_void_2009} show that the properties of the galaxies that reside in voids can be explained by the halo mass in which they live, and their properties are independent of their large scale environment of the halos.
+\citealt{tinker_density_hod} proposes an extension of the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
 Based on modeling the clustering and void statistics of the SDSS galaxies, \citealt{tinker_vpf_2008} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
-By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citealt{croton2007} shows that assembly bias significantly impacts the galaxy two-point correlation functions.
+By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citealt{croton2007} show that assembly bias significantly impacts the galaxy two-point correlation functions.
 They also show that the effect is different for the faint and the bright samples.
@@
 
-Based on a group catalog of SDSS galaxies, \citealt{blanton_group_2007} finds that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
-Based on an alternative group catalog, \citealt{wang2013} show that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
+Based on a group catalog of SDSS galaxies, \citet{blanton_group_2007} find that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
+Based on an alternative group catalog, \citet{wang2013} show that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
 
 Another family of empirical galaxy-halo connection models is \emph{Abundance} \emph{Matching}.
-In the Abundance Matching style models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity/stellar mass
+In Abundance Matching models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity or stellar mass
 (\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
-In practice, the standard abundance matching models use host halo properties 
+In practice, the standard abundance-matching models use host-halo properties 
 that trace the depth of the gravitational well of the halo, such as 
@@
 stellar mass/luminosity. With this, 
-they have been successfully used in modeling a wide range of the 
+abundance-matching models have been successfully used in modeling a wide range of the 
 statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).
 
-It has been shown that the abundance matching mock catalogs that use $V_{\rm max}$ (see \citealt{hw2013,arz2014}), or the ones that use some combination of $V_{\rm max}$ and host halo/subhalo virial mass $M_{\rm vir} $(see \citealt{lehman2015}) exhibit significant levels of assembly bias.
+It has been shown that the abundance-matching mock catalogs that use $V_{\rm max}$ (see \citealt{hw2013,arz2014}), or the ones that use some combination of $V_{\rm max}$ and host halo/subhalo virial mass $M_{\rm vir} $(see \citealt{lehman2015}) exhibit significant levels of assembly bias.
+That is, halo occupation in these models depends not only on halo mass, but also on other halo properties.
 This has been demonstrated by randomizing the galaxies among host halos of in bins of halo mass, such that the HOD remains constant, and comparing the difference in the 2PCF of the randomized catalog and the original mock catalog.
 
-Abundance Matching models, can be extended to account for even higher orders of galaxy 
-assembly bias. In so called \emph{Age Matching} models, galaxy color is abundance-matched
+Abundance-Matching models can be extended to account for even higher orders of galaxy 
+assembly bias. In so called \emph{Age-Matching} models, galaxy color is abundance-matched
 to subhalo formation time so that older (redder) galaxies preferentially reside in older halos (\citealt{hw2013}).
-\citealt{hearin2014} demonstrates that such an approach can reproduce a range of color and luminosity-dependent statistics of SDSS galaxies such as the 2PCF and galaxy-galaxy lensing.
-Based on the projected 2PCF measurements of (\citealt{hw2013}) galaxy catalogs, \citealt{arz2014} showed that although the 2PCF measurements of these catalogs can be fit with the standard HOD modeling, the inferred HOD parameters cannot recover the underlying true HOD of these catalogs.
+\citet{hearin2014} demonstrates that such an approach can reproduce a range of color and luminosity-dependent statistics of SDSS galaxies such as the 2PCF and galaxy-galaxy lensing.
+Based on the projected 2PCF measurements of (\citealt{hw2013}) galaxy catalogs, \citet{arz2014} showed that although the 2PCF measurements of these catalogs can be fit with the standard HOD modeling, the inferred HOD parameters cannot recover the underlying true HOD of these catalogs.
 That is, even in the presence of assembly bias in a galaxy sample, one can fit the clustering of this sample with HOD, but that does not guarantee recovery of the true HOD parameters.
-\citealt{mcewen2016} demonstrated that even with a galaxy catalog that has a significant level of assembly bias such as (\citealt{hw2013}) catalog, it is possible to extract the matter power spectrum more accurately if an environment-dependent HOD ($P(N|M,\delta)$) is used.
+\citet{mcewen2016} demonstrated that even with a galaxy catalog that has a significant level of assembly bias (e.g.
+\citealt{hw2013}), it is possible to extract the matter power spectrum more accurately if an environment-dependent HOD ($P(N|M,\delta)$) is used.
 
@@
 There are a number of frameworks in the literature.
-\citealt{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} have proposed environment-dependent HOD modeling methods that take into account the large-scale density contrast.
-The model that we use in this investigation is the decorated HOD modeling (\citealt{decorated}).
+\citet{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} have proposed environment-dependent HOD modeling methods that take into account the large-scale density contrast.
+The model that we use in this investigation is the decorated HOD framework (\citealt{decorated}).
 In the decorated HOD framework, at a fixed halo mass, halos are populated with galaxies according to the standard HOD modeling.
@@
 At a fixed halo mass, halos are split into two populations: halos with the highest and halos with the lowest values of the secondary property.
-The two population receive enhancements (decrements) in their number of galaxies according to a parameter which is the strength of the assembly bias parameter.
-Therefore, the assembly bias parameter will not be degenerate with the rest of the HOD parameters.
+The two population receive enhancements (decrements) in their number of galaxies according to a assembly bias amplitude parameter.
+The assembly bias parameter will not be degenerate with the rest of the HOD parameters.
 
@@
 In order to constrain assembly bias along with the rest of the HOD parameters, we make use of the publicly available measurements of the projected 2PCF and number density measurements made by
-(\citealt{guo2015}). These measurements made use of the NYU value-added galaxy catalog (\citealt{Blanton2005}).
+(\citealt{guo2015}). These measurements made use of the NYU Value-Added Galaxy Catalog (\citealt{Blanton2005}).
 
-Furthermore, we discuss how and in which galaxy brightness limits, employing a more complex HOD model that takes assembly bias into account can improve our modeling of galaxy clustering.
-We discuss the physical mechanisms that enables the more concentration-dependent HOD model to improve fitting of the galaxy 2PCF.
-Then, we make qualitative comparison between the levels of assembly bias in the mock catalogs created from our constrained on the decorated HOD model, and the \citealt{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
+Furthermore, we discuss how taking assembly bias into account in a more complex HOD model can improve our modeling of galaxy clustering in certain brightness limit.
+Then, we make a qualitative comparison between the levels of assembly bias in the mock catalogs created from our constrained on the decorated HOD model, and the \citet{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
 
-In order to investigate whether more complexity of the decorated HOD model is demanded by the galaxy clustering data, we perform model comparison between the standard HOD model and the HOD model with assembly bias.
-Moreover,  We discuss the effect of our choice of $N$-body simulation on our constraints, and previous works in the literature based on smaller $N$-body simulations (\citealt{zentner2016}).
+In order to investigate whether the additional complexity of the decorated HOD model is demanded by the galaxy clustering data, we perform a model comparison between the standard HOD model and the HOD model with assembly bias.
+We also discuss the effect of our choice of $N$-body simulation on our constraints, and previous works in the literature based on smaller $N$-body simulations (\citealt{zentner2016}).
 
@@
 %%
-%% End of file `sample.tex'.`
+%% End of file `sample.tex'.

### 2016-09-26 text/ms.tex
fixed a few typos

@@
-ss[12pt, preprint]{aastex}
+\documentclass[12pt, preprint]{aastex}
 \usepackage[breaklinks,colorlinks, 
@@
 %% you desire.
-\title{How do galaxies get assigned to halos? \\ Searching for the assembly bias in the SDSS galaxy clustering}
+\title{How do galaxies get assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering}
 
@@
 
-We show that in comparison with abundance-matching mock catalogs, our findings suggest modest levels of assembly bias.
+We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of assembly bias.
 Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
@@
 
-The simplifying assumption of standard HODs  
-does not sufficiently model the complex small scale clustering and galaxy
-formation. Numerous $N$-body simulations that examine the clustering of 
-dark matter halos argue that halo clustering is correlated with the formation 
+This simple assumption of standard HODs  
+does not sufficiently model the complexity of structure formation. Numerous $N$-body simulations that examine the clustering of 
+dark matter halos have demonstrated that halo clustering is correlated with the formation 
 history of halos. That is, at a fixed halo mass, the halo bias is correlated 
@@
 (\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
-In practice, the standard abundance-matching models use host-halo properties 
-that trace the depth of the gravitational well of the halo, such as 
-the maximum circular velocity the host halo had in its history, $V_\mathrm{max}$, 
-and assume a scatter in this property's one-to-one mapping with 
-stellar mass/luminosity. With this, 
-abundance-matching models have been successfully used in modeling a wide range of the 
+In practice, the standard abundance-matching models assume a monotonic mapping between the stellar mass/luminosity of galaxies and some host-halo property, such as 
+the maximum circular velocity the host halo $V_\mathrm{max}$ that traces the depth of the gravitational potential well of the halo.
+Furthermore, a scatter is assumed in this one-to-one relation between galaxy property and halo/subhalo property.
+With this framework, abundance-matching models have been successfully used in modeling a wide range of the
 statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).
@@
 Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$.
-From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos at the present time that belonged to higher mass halos at some point in their formation history (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
+From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $\log M \sim 11.7$ (in the units of $h^{-1}M_{\odot}$) the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
+The clustering of these population of halos is therefore dictated by that of the massive halos which cluster more strongly.
 Also note that this signal vanishes for the high mass halos.
@@
 As shown in Table \ref{tab:constraints}, our constraints on the underlying standard HOD model obtained from the model with assembly bias and the model without assembly bias are in good agreement.
-The only cases in which there are (very) mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples.
+The only cases in which there are mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples.
 However, these tensions are within one-sigma uncertainties.
-For instance, Figure {fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias.
+For instance, Figure \ref{fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias.
 Also the scatter parameter $\sigmam$ is more tightly constrained in the standard HOD model.
@@
 
-We are grateful to David~W.~Hogg, Yao~Yun Mao, Andrew Hearin, Chang~Hoon~Hahn, Andrew Zentner, Tomomi Sunayama, Kilian~W.~Walsh, and Chia~Hsun~Chuang for
+We are grateful to David~W.~Hogg, Yao~Yun Mao, Chang~Hoon~Hahn, Andrew Hearin, Andrew Zentner, Tomomi Sunayama, and Chia~Hsun~Chuang for
 discussions related to this work.
@@
 We thank Shenglong~Wang, the administrator of the NYU HPC center for his continuous and consistent support throughout the completion of this study.
+
+The CosmoSim database used in this paper is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
+The MultiDark database was developed in cooperation with the Spanish MultiDark Consolider Project CSD2009-00064.
+The authors gratefully acknowledge the Gauss Centre for Supercomputing e.V.
+(www.gauss-centre.eu) and the Partnership for Advanced Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the MultiDark simulation project by providing computing time on the GCS Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ, www.lrz.de).
 

### 2016-09-28 text/ms.tex
the most updated version of the text

@@
 Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
-One of the most powerful methods for describing the galaxy-halo connection is the halo occupation
+One of the most powerful methods for describing the galaxy--halo connection is the halo occupation
 distribution (HOD, see \citealt{seljak2000, berlind_weinberg2002, scoccimarro2001, zheng2005, zheng07, leauthaud12, tinker2013, decorated, 2016arXiv160701782H}).
@@
 
-Despite this very simplifying assumption, the models of galaxy-halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g.
+Despite this very simplifying assumption, the models of galaxy--halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g.
 \citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}).
@@
 
-Another family of empirical galaxy-halo connection models is \emph{Abundance} \emph{Matching}.
+Another family of empirical galaxy--halo connection models is \emph{Abundance} \emph{Matching}.
 In Abundance Matching models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity or stellar mass
@@
 
-In the $\mathtt{SMDP}$ simulation, as discussed in \citealt{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.
-The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy-halo connection.
+In the $\mathtt{SMDP}$ simulation, as discussed in \citet{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.
+The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy--halo connection in a wide range of luminosity thresholds.
 Fainter galaxy samples reside in lower mass halos, and the more luminous galaxy samples considered in this investigation occupy higher comoving volumes.
 Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos.
-In the context of Subhalo-Abundance matching modeling---whose accuracy hinges upon subhalo completeness especially in the low mass limit---of the galaxy-halo connection in the SDSS data, $\mathtt{SMDP}$ has been previously used to model the faint galaxy samples with absolute luminosity in the r-band $M_{\rm r}$ less -18, -18.5, and -19 (see \citealt{hod_vs_sham}).
-The added advantage of using the $\mathtt{SMDP}$ simulation over some industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its comoving volume which makes it more suitable for performing inference with $L_{\star}$ (corresponding to $M_{\rm r} \sim -20.44$, see \citealt{blanton2003}) and more luminous than $L_{\star}$ galaxy samples.
+In the context of Subhalo-Abundance matching modeling, accuracy of which depends on subhalo completeness especially in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest galaxy samples in the SDSS data (see \citet{hod_vs_sham}).
+The added advantage of using the $\mathtt{SMDP}$ simulation over some of the other industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its larger comoving volume.
+Larger volume makes this simulation more suitable for performing inference with $L_{\star}$ (corresponding to $M_{\rm r} \sim -20.44$, see \citealt{blanton2003}) and more luminous than $L_{\star}$ galaxy samples that occupy larger comoving volumes.
 
@@
 
-For our standard HOD model, we assume the HOD parameterization from \citealt{zheng07}. 
+For our standard HOD model, we assume the HOD parameterization from \citet{zheng07}. 
 According to this model, a dark matter halo can host a central galaxy and some number of satellite galaxies. The occupation of the central galaxies follows a nearest-integer distribution, 
 and the occupation of the satellite galaxies follows a Poisson distribution.
-The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the following equations
+The expected number of centrals and satellites as a function of the host halo mass of $M_{h}$ are given by the following equations
 \begin{eqnarray}
-\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
-\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
+\langle N_{\rm cen}(M_{h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
+\langle N_{\rm sat}(M_{h}) \rangle &=& \Big( \frac{M_{h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
 \end{eqnarray}
 
-For populating the halos with galaxies, we follow the procedure described in \citealt{2016arXiv160701782H,decorated}.
+For populating the halos with galaxies, we follow the procedure described in \citet{2016arXiv160701782H}, and \citet{decorated}.
 The central galaxies are assumed to be at the center of the host dark matter halos.
 We assume that the central galaxies are at rest with respect to the bulk motion of the halos and their velocities are given by the velocity of the center of mass of their host halo.
-Note that this assumption is shown to be violated in brighter than $L_{\star}$ galaxies (see \citealt{guo2015}).
+Note that this assumption is shown to be violated in brighter than $L_{\star}$ galaxy samples (see \citealt{guo2015}).
 But since we are not considering the redshift space 2PCF multipoles in our study, we do not expect this velocity bias to impact our inference.
@@
 This approach is different from other simulation-based halo occupation modeling techniques (see \citealt{hod_vs_sham,zheng_guo}) in that the positions of the satellites are not assigned to the dark matter particles in the $N$-body simulation.
-The concentration of the NFW profile is given by the empirical mass-concentration relation provided by (\citealt{nfw_c(M)}).
+The concentration of the NFW profile is given by the empirical mass-concentration relation provided by \citet{nfw_c(M)}.
 The velocities of the satellite galaxies are given by two components.
@@
 The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations (\citealt{more2010}).
-We refer the readers to \citealt{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
+We refer the readers to \citet{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.
 
 \subsubsection{Model with Assembly bias}\label{subsubsec:decorated}
-Now let us provide a brief overview of HOD modeling with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ (known as the decorated HOD) introduced in \citealt{decorated}.
+Now let us provide a brief overview of HOD modeling with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ (referred to as the decorated HOD) introduced in \citet{decorated}.
 At a fixed halo mass $M_{h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration.
 For simplicity, we call the first population ``type-1'' halos, and the second population ``type-2'' halos.
-In the decorated HOD model, the expected number of central and satellite galaxies in the two populations are given by
+In the decorated HOD model, the expected number of central and satellite galaxies at a fixed halo mass $M_{h}$ in the two populations are given by
 
@@
 
-In this occupation model, the allowable range that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take is given by 
+In this occupation model, the allowable ranges that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take are given by 
 \begin{eqnarray}
@@
 \end{eqnarray}
-where the subscript $\alpha = c , s$ for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs.
+where the subscript $\alpha = c , s$ stands for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs.
 \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.
@@
 The next step is applying a redshift-space distortion transformation by assuming plane-parallel approximation.
-Our use of plane parallel approximation is justified because of the shallow depth of the SDSS main galaxy sample considered in this study.
+Our use of plane parallel approximation is justified because of the narrow redshift range of the SDSS main galaxy sample considered in this study.
 If we assume that the $\hat{z}$ axis is the line-of-sight direction, then with the transformation $(X,Y,Z) \rightarrow (S_x,S_y,S_z) = (X , Y ,Z + v_{z}(1+z)/H(z))$
@@
 
-As described in \citealt{decorated} and \citealt{2016arXiv160701782H}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF.
+As described in \citet{decorated} and \citet{2016arXiv160701782H}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF.
 The accuracy of these fitting functions is limited (\citealt{tinker08,tinker10,watson13}).
-Our approach also does not face the known issues of the treatment of halo exclusion and scale-dependent bias that can lead to significant inaccuracies in halo occupation modeling (see \citealt{vdb13}).
+Our approach also does not face the known issues of the treatment of halo exclusion and scale-dependent bias that can lead to potential inaccuracies in halo occupation modeling (see \citealt{vdb13}).
 
@@
 For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ (\citealt{corrfunc} , available at \url{https://github.com/manodeep/Corrfunc}).
-To be consistent with the SDSS measurements described in \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
+To be consistent with the SDSS measurements described in Section \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
 Note that $w_{p}(r_{p})$ is measured in units of $h^{-1}\rm{Mpc}$.
-To be consistent with \citealt{guo2015}, we use the same binning (as specified in Section \ref{sec:data}) to measure $w_{\rm p}$.
+To be consistent with \citet{guo2015}, we use the same binning (as specified in Section \ref{sec:data}) to measure $w_{\rm p}$.
 In addition to the projected 2PCF, we use the number density given by the number of mock galaxies divided by the comoving volume of the $\mathtt{SMDP}$ simulation.
@@
 
-The measurements consist of the number density $n_{g}$ and the projected 2PCF $w_{p}(r_{p})$ made by \citealt{guo2015} for volume-limited sample of galaxies in NYU value added galaxy catalog (\citealt{Blanton2005}) constructed from the SDSS DR7 main galaxy sample (\citealt{abazajian2009}).
-In particular, eight volume limited luminosity-threshold samples are constructed with maximum absolute luminosity in $r$-band ($M_{\rm r,max}$) of -18, 18.5, -19, -19.5, -20, -20.5, -21, and -21.5.
-Qualitatively, these samples are constructed in a similar way to those constructed in \citealt{zehavi2011}.
-For detailed differences between the samples in \citealt{guo2015} and \citealt{zehavi2011}, we refer the reader to the Table 1 and Table 2 in these two papers respectively.
+The measurements consist of the number density $n_{g}$ and the projected 2PCF $w_{p}(r_{p})$ made by \citet{guo2015} for the volume-limited sample of galaxies in NYU Value Added Galaxy Catalog (\citealt{Blanton2005}) constructed from the SDSS DR7 main galaxy sample (\citealt{abazajian2009}).
+In particular, eight volume-limited luminosity-threshold samples are constructed with maximum absolute luminosity in $r$-band of -18, 18.5, -19, -19.5, -20, -20.5, -21, and -21.5.
+Qualitatively, these samples are constructed in a similar way to those constructed in \citet{zehavi2011}.
+For detailed differences between the samples in \citet{guo2015} and \citet{zehavi2011}, we refer the reader to the Table 1 and Table 2 in those papers respectively.
 
-The projected 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
+The projected 2PCFs are measured in 12 logarithmic $r_{p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$.
 For all luminosity threshold samples, the integration along the line-of-sight (\ref{los}) are performed to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.
 
-The 2PCF measurement of each luminosity threshold sample is accompanied by a covariance matrix constructed using 400 jackknife sub-samples of the data.
+The 2PCF measurement of each luminosity-threshold sample is accompanied by a covariance matrix constructed using 400 jackknife sub-samples of the data.
 The number density measurements are also accompanied by uncertainties measured using the jackknife method.
 Furthermore, the covariance between the number denisty and the projected 2PCF measurements are neglected.
-As \citealt{norberg} shows, parameter estimation using jackknife covariance matrices is conservative as jackknife overestimate the error in the observations.
+As \citet{norberg} shows, parameter estimation using jackknife covariance matrices is conservative as the jackknife method overestimates the errors in the observations.
 
-The advantage of using these measurements is that the effects of fiber collision systematic errors on the two-point statistics are corrected for (with the method described in \citealt{guo2012}), and therefore, these measurements provide more accurate small scale clustering measurements.
+The advantage of using these measurements is that the effects of fiber collision systematic errors on the two-point statistics are corrected for (with the method described in \citealt{guo2012}), and therefore, these measurements provide accurate small scale clustering measurements.
 The assembly bias parameters introduced in section \ref{sec:method} can have a 10-percent level impacts on galaxy clustering (\citealt{decorated}).
 Presence of assembly bias in the satellite population impacts the very small-scale clustering (\citealt{decorated}).
-Moreover as \citealt{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$).
+Moreover as \citet{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$).
 This scales can be impacted by fiber collision systematics.
 Precise investigation of the possible impact of this signal on the galaxy clustering modeling requires accurate measurements of 2PCF on small scales.
-The method of \citealt{guo2012} is able to recover the true $\wpp$ with  $\sim 6\%$ accuracy in small scales ($r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$) and with $\sim 2.5\%$ at relatively large scales $r_{\rm{p}} \sim 30 \; h^{-1}\rm{Mpc}$.
+The method of \citet{guo2012} is able to recover the true $\wpp$ with  $\sim 6\%$ accuracy in small scales ($r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$) and with $\sim 2.5\%$ at relatively large scales $r_{\rm{p}} \sim 30 \; h^{-1}\rm{Mpc}$.
 
-Note that the comoving volume of the $N$-body simulation used in this investigation is 64 $\times 10^{6} \; h^{-3}\rm{Mpc}^{3}$ which is larger than the comoving volume of all the luminosity threshold samples in the SDSS data except the two most luminous samples.
+Note that the comoving volume of the $N$-body simulation used in this investigation is 64 $\times 10^{6} \; h^{-3}\rm{Mpc}^{3}$ which is larger than the comoving volume of all the luminosity-threshold samples in the SDSS data considered in this study except the two most luminous samples.
 The comoving volumes of the $M_{\rm r}<-21, \; 21.5$ samples are 71.74 and 134.65 (in units of $10^{6} h^{-3}\rm{Mpc}^{3}$) respectively.
-Since we are only studying not very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.
+Since we are not studying very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.
 
@@
 
-Given the SDSS measurements described in \ref{sec:data}, we aim to constrain the HOD model without assembly bias (described in \ref{subsubsec:hod}), and the HOD model with assembly bias (described in \ref{subsubsec:decorated}) for every luminosity threshold samples, by sampling from the posterior probability distribution $p(\theta|d) \propto p(d|\theta) \pi(\theta)$.
-In the standard HOD modeling
+Given the SDSS measurements described in Section \ref{sec:data}, we aim to constrain the HOD model without assembly bias (described in \ref{subsubsec:hod}), and the HOD model with assembly bias (described in \ref{subsubsec:decorated}) for each luminosity-threshold sample, by sampling from the posterior probability distribution $p(\theta|d) \propto p(d|\theta) \pi(\theta)$ where $\theta$ denotes the parameter vector and $d$ denotes the data vector.
+In the standard HOD modeling $\theta$ is given by
 \beq
@@
 \end{eqnarray}
-Furthermore, data (denoted by $d$) is the combination of $[n_{g}, w_{\rm{p}}(r_{\rm{p}})]$.
-The negative log-likelihood (assuming zero negligible covariance between $n_{g}$ and $w_{\rm{p}}(r_{\rm{p}})$) is given by
+Furthermore, data (denoted by $d$) is the combination of $[n_{g}, w_{p}(r_{p})]$. The negative log-likelihood (assuming negligible covariance between $n_{g}$ and $w_{p}(r_{p})$) is given by
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\Delta \wpp$ is a 12 dimensional vector, $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $\widehat{C^{-1}}$ is the estimate of the inverse covariance matrix that is related to the inverse of the jackknife covariance matrix (provided by \citealt{guo2015}) $\widehat{C}^{-1}$, following \citealt{hartlap2007}:
+where $\Delta \wpp$ is a 12 dimensional vector, $\Delta \wpp(\rpp) = \wpp^{\rm data}(\rpp)-\wpp^{\rm model}(\rpp)$, and  $\widehat{C^{-1}}$ is the estimate of the inverse covariance matrix that is related to the inverse of the jackknife covariance matrix (provided by \citealt{guo2015}) $\widehat{C}^{-1}$, following \citet{hartlap2007}:
 \beq
@@
 \eeq
-where $N=400$ is the number of the jackknife samples, and $d=12$ is the length of the data vector $w_{p}$.
+where $N=400$ is the number of the jackknife samples, and $d=12$ is the length of the data vector $w_{\rm p}$.
 Another important ingredient of our analysis is specification of the prior probabilities $\pi(\theta)$ over the parameters of the halo occupation models considered in this study.
@@
 The prior ranges are specified in the Table \ref{tab:prior}.
-Note that a uniform prior between -1 and 1 is chosen for assembly bias parameters, since these parameters are, by definition, bounded between -1 and 1.
+Note that a uniform prior between -1 and 1 is chosen for assembly bias parameters since these parameters are, by definition, bounded between -1 and 1.
 \begin{table}
@@
   and its range for each of the parameters. 
-  All mass parameters are in unit of $h^{-1}M_\odot$. The parameters marked by $*$ are only used in the Heaviside Assembly bias modeling.}
+  All mass parameters are in unit of $h^{-1}M_\odot$. The parameters marked by $*$ are only used in the Heaviside Assembly bias modeling and by definition are bounded between -1 and 1.}
 \begin{tabular}{@{}lllll}
@@
 
-For sampling from the posterior probability, given the likelihood function (see \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler (\citealt{goodmanweare}) and its implementation $\mathtt{emcee}$ (\citealt{emcee}).
+For sampling from the posterior probability, given the likelihood function (see equation \ref{eq:lnlike_wp}) and the prior probability distributions (see Table \ref{tab:prior}), we use the affine-invariant ensemble MCMC sampler (\citealt{goodmanweare}) and its implementation $\mathtt{emcee}$ (\citealt{emcee}).
 In particular, we run the $\mathtt{emcee}$ code with 20 walkers and we run the chains for at least 10000 iterations.
-We discard one-third of the chains as burn-in samples and use the reminder of the chains as production MCMC chains.
-Furthermore, we perform Gelman-Rubin convergence test (\citealt{grtest}) to insure that the MCMC chains have reached convergence.
+We discard the first one-third part of the chains as burn-in samples and use the reminder of the chains as production MCMC chains.
+Furthermore, we perform Gelman-Rubin convergence test (\citealt{grtest}) to ensure that the MCMC chains have reached convergence.
 
@@
 In particular, findings of (\citealt{weschler2006,sunayama2016})
-have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos is larger than that of the low-$V_{\rm max}$ or low-$c$ halos.
+have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos at a fixed halo mass is larger than that of the low-$V_{\rm max}$ or low-$c$ halos.
 This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$).
 Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}).
+For halos described by NFW profile, at a fixed halo mass, halos with higher values of concentration have higher values of $V_{\rm max}$.
 
@@
 
-The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ (\citealt{prada2012}).
+The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ which is a tracer of the potential well of dark matter halos (\citealt{prada2012}).
 In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}).
-In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$.
-Note that this is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}).
+In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$:
+\beq
+\Phi(r=0) = -\Big(\frac{V_{\rm max}}{0.465}\Big)^{2},
+\eeq
+ where $\Phi(r=0)$ is the central potential of an NFW profile.
+Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}).
 The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
@@
 we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias.
-Group statistics probes the high mass end of the galaxy-halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.
+Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.
 
@@
 As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering.
+Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias.
+This is also evident in Figure \ref{fig:posterior}.
+The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of $\acen$.
+
 As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight.
 This is in keeping with the results of \citealt{guo2015} (which uses the same SDSS data) according to which, the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
-Note that even if $n_{g}$ and $w_{p}$ are used, $\sigmam$ is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end).
+Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end).
 But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter.
@@
 However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level.
-\citealt{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy-halo connection parameters.
+\citealt{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
 Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
 
-A few galaxy-halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population.
+A few galaxy--halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population.
 \citealt{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
@@
 This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}).
-The Box size for this simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, the mass per simulation particle $m_{\rm p}$ is $1.9 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1 $h^{-1} \rm{kpc}$.
+The Box size for this simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, the mass per simulation particle $m_{\rm p}$ is $1.35 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1 $h^{-1} \rm{kpc}$.
 The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}).
@@
 
-  We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation.
+  We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation (\citealt{bolshoi2016}).
+This $N$-body simulation is carried out with similar setting as the $\mathtt{Bolshoi}$ simulation with the exception that in the $\mathtt{BolshoiP}$ simulation, the Planck Cosmology is adapted and the mass per simulation particle is $1.49\times 10^8 \; h^{-1} M_{\odot}$.
 The summary of constraints are shown in Figure \ref{fig:bias_comparison}.
@@
 For $M_{\rm r}<-19, -18.5$ we find no correlation, and for the faintest sample, we find negative correlation.
-Given the large scale halo assembly bias and the scale-dependent feature of it in the quasi-linear scales, these constraints lead to improvement in modeling the galaxy clustering.
-But we do not find these improvements to be sufficient to lower the information criteria scores associated with the more complex models with the exception of $M_{\rm r}<-20,-18$ luminosity-threshold samples for which we find the strongest constraints on the central assembly bias.
+Given the large scale halo assembly bias and the scale-dependent feature of assembly bias in the quasi-linear scales, these constraints lead to improvement in modeling the galaxy clustering.
+However, we do not find these improvements to be sufficient to lower the information criteria scores associated with the more complex model.
+The exceptions are the $M_{\rm r}<-20,-18$ luminosity-threshold samples for which we find the strongest constraints on the central assembly bias.
 For these two samples, the HOD model with assembly bias yields lower BIC score than the model without assembly bias.
 
-Comparison of the levels of assembly bias in the catalogs predicted from our constraints and \citealt{hw2013} catalogs demonstrates that our mock catalogs support more modest levels of assembly bias which follows the same trend: assembly bias in the central population which vanishes in the brightest samples.
+Comparison of the levels of assembly bias in the catalogs predicted from our constraints and \citealt{hw2013} catalogs demonstrates that our mock catalogs support modest levels of assembly bias which follows the same trend: assembly bias is seen in the central population and vanishes in the brightest samples.
 
@@
 discussions related to this work.
+This work was supported by the NSF grant AST-1517237.
 All the computations in this work were carried out in the New York University High Performance Computing Mercer facility.
@@
 The SDSS clustering measurements and the covariance matrices used in this work are available at \url{http://sdss4.shao.ac.cn/guoh/files/wpxi_measurements_Guo15.tar.gz}.
-Description of the Small MultiDark Planck halo catalog used in this investigation can be found at \url{https://www.cosmosim.org/cms/simulations/smdpl/smdpl-rockstar/}, and the RockStar halo catalog of the SMDP simulation is publicly available at \url{http://yun.ucsc.edu/sims/SMDPL/hlists/index.html}.
+Description of the $\mathtt{SMDP}$ and the $\mathtt{BolshoiP}$ halo catalogs used in this investigation can be found at \url{https://www.cosmosim.org/cms/simulations}.
+The RockStar halo catalogs of the $\mathtt{SMDP}$ and the $\mathtt{BolshoiP}$ simulations are publicly available at \url{http://yun.ucsc.edu/sims/SMDPL/hlists/index.html} and \url{http://yun.ucsc.edu/sims/Bolshoi_Planck/hlists/index.html} respectively.
+We thank Peter Behroozi for making the halo catalogs publicly available.
 
@@
 \includegraphics[width=0.8\textwidth]{bias2.pdf}
-\caption{Constraints on the central assembly bias $\acen$ (Top panel) and the satellite assembly bias $\asat$ (Bottom panel) parameters. }
+\caption{Constraints on the central assembly bias $\acen$ (Top panel) and the satellite assembly bias $\asat$ (Bottom panel) parameters.
+The $\acen$ constraints for the $M_{\rm r} < -20.5, -20, -19.5$ samples favor positive values of $\acen$ with the tightest constraint coming from the $M_{\rm r} < -20$ sample.
+All the $\asat$ constraints are consistent with no satellite assembly bias.}
 \label{fig:bias}
@@
 The Dark and light shaded regions mark the 68$\%$ and the 95$\%$ confidence intervals.
-The errorbars are the from the diagonal elements of the covariance matrix.}
+The errorbars are from the diagonal elements of the covariance matrix.}
 \label{fig:wpmodel}
@@
 \includegraphics[width=\textwidth]{wpres.pdf}
-\caption{Same as Figure \ref{fig:wpmodel}, but showing the fractional difference between the posterior predictions and the observed projected 2PCF for all the luminosity threshold.
+\caption{Same as Figure \ref{fig:wpmodel}, but showing the fractional difference between the posterior predictions and the observed projected 2PCF for all the luminosity threshold samples.
 In all luminosity threshold samples, predictions of the two models for small scale clustering are consistent.
@@
 Comparison between the level of assembly bias (encoded in the relative difference in $w_p$) shows that the our constraints favor \emph{more} \emph{moderate} levels of assembly bias than the levels seen in the abundance matching mock catalogs.
-Within both models, the small scale clustering remains unaltered after randomizing the catalogs, signaling the lack of correlation between the satellite population and the halo concentration in the two models.}
+Within both models, the small scale clustering remains unaltered after randomizing the catalogs, signaling the lack of correlation between the satellite population and the halo concentration at a fixed mass in the two models.}
 \label{fig:randomized}
@@
 The errorbars mark the 68$\%$ uncertainty over the parameters.
-Shaded blue regions show the upper and lower bounds found by \citealt{zentner2016} that uses the $\mathtt{BolshoiP}$ and clustering measurements of \citealt{zehavi2011}.
+Shaded blue regions show the upper and lower bounds reported by \citet{zentner2016} that uses the $\mathtt{BolshoiP}$ and clustering measurements of \citet{zehavi2011}.
 The central assembly bias constraints found from the two simulations are consistent, with the constraints for from the $\mathtt{SMDP}$ simulation being tighter for the most luminous samples.
@@
 \includegraphics[width=\textwidth]{hist_comparison.pdf}
-\caption{Demonstration of constraints over the satellite assembly bias parameters from luminosity threshold samples $M_{\rm r}<-19 ,\; -20.5$, for two different simulations: $\mathtt{BolshoiP}$ (yellow), and $\mathtt{SMDPL}$ (green).
-The $\asat$ constraints found using the $\mathtt{BolshoiP}$ simulation is favor more positive values of $\asat$, while the constraints found using the $\mathtt{SMDP}$ simulation are consistent with no satellite assembly bias.}
+\caption{Constraints over the satellite assembly bias parameters from luminosity threshold samples $M_{\rm r}<-19 ,\; -20.5$, for two different simulations: $\mathtt{BolshoiP}$ (yellow), and $\mathtt{SMDPL}$ (green).
+The $\asat$ constraints found using the $\mathtt{BolshoiP}$ simulation favor more positive values of $\asat$, while the constraints found using the $\mathtt{SMDP}$ simulation favor zero satellite assembly bias.}
 \label{fig:asat_comparison}

### 2016-09-28 text/ms.tex
changed a few words in discussion

@@
 assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$.
-As shown in Figure \ref{fig:bias}, for all the eight luminosity threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are
+As shown in Figure \ref{fig:bias}, for all the eight luminosity-threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are
 consistent with zero.
@@
 $M_{\rm r} < -21.5$ and $M_{\rm r} < -21$, $\acen$ is poorly constrained and the constraints are equivalent to zero.
-As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift towards positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$.
+As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift toward positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$.
 Furthermore, the posterior constraints on the assembly bias parameters in the slightly fainter samples, i.e.
@@
 The central galaxy clustering can be thought as the weighted average over the halo clustering.
-The large scale bias of the dark matter halo clustering depends not only on mass, but on other the properties of halos beyond mass, such as concentration (\citealt{weschler2006,gao2007,miyatake2016}), spin (\citealt{gao2007}), formation time (\citealt{gao2007, li2008}), and the maximum circular velocity over the accretion history of the halo $V_{\rm max}$ (\citealt{sunayama2016}).
+The large scale bias of the dark matter halo clustering depends not only on mass, but also on the other properties of halos beyond mass, such as concentration (\citealt{weschler2006,gao2007,miyatake2016}), spin (\citealt{gao2007}), formation time (\citealt{gao2007, li2008}), and maximum circular velocity of the halo $V_{\rm max}$ (\citealt{sunayama2016}).
 
-In particular, findings of (\citealt{weschler2006,sunayama2016})
-have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos at a fixed halo mass is larger than that of the low-$V_{\rm max}$ or low-$c$ halos.
+In particular, findings of \citet{weschler2006} and \citet{sunayama2016}
+have demonstrated that for halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ (or equivalently high-$c$ halos at a fixed halo mass) is larger than that of the low-$V_{\rm max}$ (low-$c$ halos).
 This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$).
@@
 Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$.
-From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $\log M \sim 11.7$ (in the units of $h^{-1}M_{\odot}$) the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
-The clustering of these population of halos is therefore dictated by that of the massive halos which cluster more strongly.
-Also note that this signal vanishes for the high mass halos.
+From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $M \sim 10^11.7 \; h^{-1}M_{\odot}$ at the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
+The clustering of these population of halos is therefore dictated by that of the massive halos.
+Note that this scale-dependent bias feature vanishes as we probe high mass halos.
 
@@
 
-Figure \ref{fig:wpmodel} demonstrates the 68$\%$ and 95$\%$ percent posterior predictions for the projected 2PCF $w_{p}$ from the occupation model without assembly bias (shown in red) and the occupation model with assembly bias (shown in blue) for all eight luminosity-threshold samples.
+Figure \ref{fig:wpmodel} demonstrates the 68$\%$ and 95$\%$ posterior predictions for the projected 2PCF $w_{p}$ from the occupation model without assembly bias (shown in red) and the occupation model with assembly bias (shown in blue) for all eight luminosity-threshold samples.
 For the brightest galaxies, $M_{r} < -21.5$ and $M_{r} < -21.0$, the posterior prediction of $w_{p}$ from the two models are consistent with one another.
@@
 
-Figure \ref{fig:wpres} shows the fractional difference between the 68$\%$ and 95$\%$ percent posterior predictions of $w_p$ and the SDSS data.
-It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the model complex halo occupation model with assembly bias.
-As a result of apportioning more central galaxies to the high-$c$ halos with respect to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and larger scales.
+Figure \ref{fig:wpres} shows the fractional difference between the 68$\%$ and 95$\%$ posterior predictions of $w_p$ and the SDSS data.
+It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the more complex halo occupation model with assembly bias.
+As a result of apportioning more central galaxies to the high-$c$ halos relative to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and large scales.
 This can be also noted in significantly lower $\chi^{2}$ values---at the cost more model flexibility and higher degrees of freedom---achieved by the assembly bias model in these luminosity-threshold samples (see Table \ref{tab:constraints}).
@@
 
-Finally, In the faintest sample ($M_{\rm r} < -18$), negative constraints on the parameter $\acen$ results in higher expected number of centrals in the low-$c$ halos, which at a fixed halo mass, cluster less strongly (in the low mass halos).
+Finally, In the faintest sample ($M_{\rm r} < -18$), negative constraints on the parameter $\acen$ results in higher expected number of centrals in the low-$c$ halos, which at a fixed halo mass, cluster less strongly.
 This affects both the large scale bias and the intermediate regimes as a result of the scale-dependent bump feature (see Figures \ref{fig:wpmodel} and \ref{fig:wpres}).
@@
 In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}).
-In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$:
+In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$.
+More specifically, we have:
 \beq
@@
 Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}).
-The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
+The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest samples ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well.
+As we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
 
@@
 This results in boosting the small-scale clustering, but as pointed out in \citealt{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$.
-Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend halo concentration.
+Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend on halo concentration.
 
-However, our results suggest that for all the 8 luminosity-threshold samples, the satellite assembly bias parameter is largely unconstrained and consistent with zero.
-we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias.
-Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.
+However, our results suggest that for all the 8 luminosity-threshold samples considered in this study, the satellite assembly bias parameter is largely unconstrained and consistent with zero.
+We do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias.
+Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}).
+Therefore these measurements may shed light on potential presence of assembly bias in the satellite population.
 
@@
 Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias.
-This is also evident in Figure \ref{fig:posterior}.
-The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of $\acen$.
+This is evident in Figure \ref{fig:posterior}.
+The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of central assembly bias.
 
 As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight.
-This is in keeping with the results of \citealt{guo2015} (which uses the same SDSS data) according to which, the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
+This is in keeping with the results of \citet{guo2015} which uses the same SDSS data and finds that the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
 Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end).
 But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter.
-\citealt{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter.
-Tightening of constraints on the scatter parameters leads to reduction of uncertainty in the inferred central assembly bias parameter.
+\citet{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), and hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter.
+Tightening of constraints on the scatter parameters can lead to reduction of uncertainty in the inferred central assembly bias parameter.
 
@@
 However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level.
-\citealt{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
+\citet{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
 Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
@@
 A few galaxy--halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population.
-\citealt{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
+\citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
 
 We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$ type galaxies.
-In particular, we consider the abundance matching catalogs produced by \citealt{hw2013}.
-These catalogs have been extensively studies for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences.
+In particular, we consider the abundance matching catalogs produced by \citet{hw2013}.
+These catalogs have been extensively studied for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences.
 This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}).
@@
 The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}).
-The \citealt{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.
+The \citet{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.
 
-As noted by both \citealt{arz2014},and \citealt{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias.
+As noted by both \citet{arz2014},and \citet{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias.
 This has been shown by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs.
-Randomization is performed in a procedure described in \citealt{arz2014}: the central galaxies among all halos within each of the halo mass bins (with width of 0.1 dex).
+Randomization is performed in a procedure described in \citet{arz2014}.
+First all central galaxies are shuffled among all halos within each of the halo mass bins (with width of 0.1 dex).
 In each mass bin, once the centrals have been shuffled, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo.
@@
 For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the \citealt{hw2013} catalogs is shown in Figure \ref{fig:randomized} with the red curves.
-As previously noted by \citealt{arz2014} these catalogs and as it can be seen in Figure $\ref{fig:randomized}$ the difference in $w_{p}$ is only significant in large scales.
-This means that in these catalogs, only the central galaxies are affected by assembly bias which is in agreement with our findings.
+As previously noted by \citet{arz2014} and as it can be seen in Figure $\ref{fig:randomized}$, the difference in $w_{p}$ between these catalogs and their corresponding randomized versions is only significant in large scales.
+This implies that in these catalogs, only the central galaxies are affected by assembly bias.
+This is in agreement with our findings.
 
-Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the origin and catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend.
+Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the original catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend.
 That is, we see no difference in the small scale clustering and significant differences as we move towards larger scales.

### 2016-09-28 text/ms.tex
updated the discussion section

@@
  where $\Phi(r=0)$ is the central potential of an NFW profile.
-Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}).
+Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013,lehman2015, hod_vs_sham, halodemographic}).
 The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest samples ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well.
@@
 Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm sat} N_{\rm sat} \rangle$.
-This results in boosting the small-scale clustering, but as pointed out in \citealt{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$.
-Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend on halo concentration.
+This results in boosting the small-scale clustering.
+But as pointed out by \citet{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$.
+Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation may depend on halo concentration.
 
-However, our results suggest that for all the 8 luminosity-threshold samples considered in this study, the satellite assembly bias parameter is largely unconstrained and consistent with zero.
+However, our results suggest that for all the luminosity-threshold samples considered in this study, the satellite assembly bias parameter is largely unconstrained and consistent with zero.
 We do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias.
 Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}).
-Therefore these measurements may shed light on potential presence of assembly bias in the satellite population.
+Therefore these measurements may shed some light on potential presence of assembly bias in satellite population.
 
-It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range that satisfies the condition $0<\langle N_{\rm cen}|M \rangle<1$.
-As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering.
-Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias.
+It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range in which the condition $0<\langle N_{\rm cen}|M \rangle<1$ is met.
+Consequently, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering.
+Note that in the luminosity regimes for which we obtain tighter constraints on $\acen$, the best-estimate values of the scatter parameter $\sigmam$ appear to be higher in the model with assembly bias.
 This is evident in Figure \ref{fig:posterior}.
-The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of central assembly bias.
+The model with assembly bias tends to push $\sigmam$ to higher values.
+This can be attributed to the tendency of this model to increase the effective dynamical mass range of central assembly bias.
 
-As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight.
-This is in keeping with the results of \citet{guo2015} which uses the same SDSS data and finds that the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
+As shown in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight.
+This is in keeping with the results of \citet{guo2015} which uses the same SDSS measurements and finds that the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables.
 Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end).
@@
 \citet{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), and hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter.
-Tightening of constraints on the scatter parameters can lead to reduction of uncertainty in the inferred central assembly bias parameter.
+Tightening the constraints on the scatter parameter can lead to more precise inference of the central assembly bias parameter.
 
@@
 The only cases in which there are mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples.
-However, these tensions are within one-sigma uncertainties.
+However, these tensions are within one-sigma level.
 For instance, Figure \ref{fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias.
@@
 However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level.
-\citet{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
+
+\citet{arz2014} shows that in the mock catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
 Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
@@
 \citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
+We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$-type galaxies.
+In particular, we consider the abundance matching catalogs produced by \citet{hw2013}.
+These catalogs have been extensively studied for examining potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and halo occupation (\citealt{arz2014}) parameter inferences.
 
-We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$ type galaxies.
-In particular, we consider the abundance matching catalogs produced by \citet{hw2013}.
-These catalogs have been extensively studied for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences.
 This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}).
@@
 The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}).
-The \citet{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.
+The \citealt{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.
 
-As noted by both \citet{arz2014},and \citet{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias.
-This has been shown by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs.
-Randomization is performed in a procedure described in \citet{arz2014}.
-First all central galaxies are shuffled among all halos within each of the halo mass bins (with width of 0.1 dex).
-In each mass bin, once the centrals have been shuffled, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo.
-This procedure preserves the HOD, but erases any dependence of the galaxy population on the assembly history of halos such that, assembly bias is erased in the randomized catalog.
+As noted by \citet{arz2014} and \citet{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias in the central galaxy population.
+This has been demonstrated by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs.
+Randomization is performed in a procedure described in \citet{arz2014} which we briefly summarize here: First, halos are divided into different bins of halo mass with width of 0.1 dex.
+Then all central galaxies are shuffled among all halos within each bin.
+Once the centrals have been shuffled, within each bin, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo.
+This procedure preserves the HOD, but erases any dependence of the galaxy population on the assembly history of halos.
+Therefore, assembly bias is erased in the randomized galaxy catalog.
 
-For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the \citealt{hw2013} catalogs is shown in Figure \ref{fig:randomized} with the red curves.
-As previously noted by \citet{arz2014} and as it can be seen in Figure $\ref{fig:randomized}$, the difference in $w_{p}$ between these catalogs and their corresponding randomized versions is only significant in large scales.
+For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the original catalogs of \citet{hw2013} is shown in Figure \ref{fig:randomized} with the red curves.
+As demonstrated in Figure \ref{fig:randomized} (and as previously noted by \citealt{arz2014,edHOD-weinberg}), the relative difference in $w_{p}$ is only significant in large scales.
 This implies that in these catalogs, only the central galaxies are affected by assembly bias.
@@
 
-Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the original catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend.
-That is, we see no difference in the small scale clustering and significant differences as we move towards larger scales.
-Similar to \citealt{hw2013} catalogs, assembly bias becomes less significant as we probe brighter galaxy samples.
-Furthermore, we notice that our mock catalogs favor more modest levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
+Furthermore, we investigate whether the levels of assembly bias predicted by our findings are in agreement with the abundance matching catalogs of \citet{hw2013}.
+First, we make random draws from the posterior pdf over the parameters of the model with assembly bias.
+Then, we create mock catalogs with these random draws, and then we compute the difference in $w_{p}$ between the randomized catalogs and the original catalogs.
+The relative difference in $w_{p}$ predicted from our constraints are shown with blue curves in Figure \ref{fig:randomized}.
+
+We note that our findings follow the same trend.
+That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales.
+Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that assembly bias becomes less significant as we probe brighter galaxy samples.
+Furthermore, we notice that our mock catalogs favor more moderate levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
 
@@
 
-Figure \ref{fig:ic} shows that the comparison between the BIC and AIC scores for the model with assembly bias and the model without assembly bias shows that the model without assembly bias is still preferable by the galaxy clustering observations.
-That is, although some improvements to fitting the clustering data cen be achieved as a result of using a more complicated model, these improvements are not significant enough to justify the use of a more complicated model that takes assembly bias into account.
+Figure \ref{fig:ic} shows the comparison between the BIC and AIC scores for the model with assembly bias and the model without assembly bias.
+We note that the model without assembly bias is still preferable by the galaxy clustering observations.
+That is, although some improvements to fitting the clustering data can be achieved as a result of using a more complicated occupation model, these improvements are not significant enough to justify the use of a more complicated model that takes assembly bias into account.
 
 We note that both AIC and BIC scores improve in the luminosity-threshold samples for which, we have tighter constraints over the central assembly bias parameter.
+In particular, the model with assembly bias deliver \emph{only} \emph{slightly} lower AIC scores for the $M_{\rm r}<-18, -20$ samples.
 This supports our intuition that AIC and BIC penalize unconstrained parameters.
 Also note that, the difference between both BIC and AIC scores are marginal.
-That is, although the HOD model is preferred, it is not strongly preferred by the data.
+That is, although the HOD model is preferred, it is not strongly favored by the data.
 
@@
 
-  We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation (\citealt{bolshoi2016}).
-This $N$-body simulation is carried out with similar setting as the $\mathtt{Bolshoi}$ simulation with the exception that in the $\mathtt{BolshoiP}$ simulation, the Planck Cosmology is adapted and the mass per simulation particle is $1.49\times 10^8 \; h^{-1} M_{\odot}$.
+Given the SDSS clustering measurements described in Section \ref{sec:data}, We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation (\citealt{bolshoi2016}).
+This $N$-body simulation is carried out with similar setting as the $\mathtt{Bolshoi}$ simulation with the exception that in the $\mathtt{BolshoiP}$ simulation, Planck cosmology is adapted and the mass per simulation particle is $1.49\times 10^8 \; h^{-1} M_{\odot}$.
+
 The summary of constraints are shown in Figure \ref{fig:bias_comparison}.
 In Figure \ref{fig:bias_comparison}, the constraints from the $\mathtt{SMDP}$ and the $\mathtt{BolshoiP}$ simulations are shown with circles and crosses respectively.
-Furthermore, the upper and lower bounds on the inferred parameters reported by \citealt{zentner2016} in the shaded blue regions.
+Additionally, the upper and lower bounds on the inferred parameters reported by \citet{zentner2016} are shown in shaded blue regions.
 In the case of central assembly bias, all three constraints are consistent.
@@
 
-In the case of the satellite assembly bias parameters however, constraints from the $\mathtt{BolshoiP}$ simulation for the luminosity threshold samples $M_{\rm r}<-20.5, -19$ favor positive values of the parameter, while our constraints from the $\mathtt{SMDP}$ simulation for these two luminosity thresholds are consistent with zero.
-As it is shown in the lower panel of Figure \ref{fig:bias_comparison}, our constraints from the $\mathtt{BolshoiP}$ simulations are consistent with lower and upper bounds (shown with the shaded blue region) reported by \citealt{zentner2016} that uses the same simulation but slightly different $w_{p}$ measurements (\citealt{zehavi2011}).
+In the case of the satellite assembly bias parameters however, constraints from the $\mathtt{BolshoiP}$ simulation for the luminosity threshold samples $M_{\rm r}<-20.5, -19$ favor more positive values of the parameter, while our constraints from the $\mathtt{SMDP}$ simulation for these two luminosity thresholds favor zero satellite assembly bias.
+As it is shown in the lower panel of Figure \ref{fig:bias_comparison}, our constraints from the $\mathtt{BolshoiP}$ simulations for the $M_{\rm r}<-21, -20.5, -20, -19.5, -19$ samples are consistent with the lower and upper bounds (shown with the shaded blue region) reported by \citet{zentner2016} that uses the same simulation but slightly different $w_{p}$ measurements (\citealt{zehavi2011}).
+Therefore, there is some discrepancy between our $\asat$ constraints using the $\mathtt{SMDP}$ simulation and the $\mathtt{BolshoiP}$ simulations.
 
-The marginalized posterior PDFs over $\asat$ are shown in Figure \ref{fig:asat_comparison}.
-Note that $\asat$ is poorly constrained in both simulations and for both samples.
-For the $M_{\rm r}<-19$ sample, given how poorly constrained the parameters are, the discrepancy between the constraints is not very stark.
-Note that the tension between the inferred parameters is still at a one-sigma level.
-The disagreement however, becomes more pronounced in the $M_{\rm r}<-20.5$ sample.
-This can possibly be attributed to the different size and resolution of the simulation boxes.
+For the $M_{\rm r}<-19, -20.5$ samples, the marginalized posterior PDFs over $\asat$ from the two simulations are shown in Figure \ref{fig:asat_comparison}.
+Note that $\asat$ is poorly constrained in both simulations and for both luminosity-threshold samples.
+For the $M_{\rm r}<-19$ sample, considering how poorly constrained the parameters are, the discrepancy between the constraints is not very stark.
+Note that the tension is still at a one-sigma level.
+The discrepancy however, becomes more pronounced in the $M_{\rm r}<-20.5$ sample.
 
-In terms of the effect of assembly bias on galaxy clustering, note that mocks created using the inferred parameters with the $\mathtt{SMDP}$ simulation show the same behavior as we observe in the abundance matching catalogs of \citealt{hw2013} and \citealt{lehman2015}.
-In those catalogs, the difference in $w_{p}$ between the mock catalogs and the randomized catalogs is mostly on large scales where the clustering is governed by the central galaxies.
+In terms of the effect of assembly bias on galaxy clustering, note that mocks created using the inferred parameters with the $\mathtt{SMDP}$ simulation show the same behavior as we observe in the abundance matching catalogs presented in \citet{arz2014} and \citet{lehman2015}.
+That is, the difference in $w_{p}$ between the mock catalogs and the randomized catalogs is mostly on large scales where the clustering is governed by the central galaxies.
 
@@
 In this investigation, we provide constraints on the concentration-dependence of halo occupation for a wide range of galaxy luminosities in the SDSS data.
-In particular, the modeling is done in the context of the decorated HOD model \citealt{decorated}, and the data used in this investigation is the projected 2PCF measurements published by \citealt{guo2015}.
+In particular, the modeling is done in the context of the decorated HOD model \citet{decorated}, and the data used in this investigation is the projected 2PCF measurements published by \citet{guo2015}.
 We make use of $\mathtt{SMDP}$ high resolution $N$-body simulation that enables us to reliably perform inference for the faintest galaxy samples in the SDSS DR7 catalog that live in low mass halos, and the brightest galaxy samples that occupy large comoving volumes.
@@
 
-For the $M_{\rm r}<-20.5, -20, -19.5$ samples, we find positive correlation between the central population and halo concentration at fixed halo mass.
+For the $M_{\rm r}<-20.5, -20, -19.5$ samples, at a fixed halo mass, we find positive correlation between the central population and halo concentration at fixed halo mass.
 For $M_{\rm r}<-19, -18.5$ we find no correlation, and for the faintest sample, we find negative correlation.
@@
 
-Comparison of the levels of assembly bias in the catalogs predicted from our constraints and \citealt{hw2013} catalogs demonstrates that our mock catalogs support modest levels of assembly bias which follows the same trend: assembly bias is seen in the central population and vanishes in the brightest samples.
+Comparison of the levels of assembly bias in the catalogs constructed based on our results and the abundance matching catalogs presented in \citet{hw2013,arz2014} and \citet{edHOD-weinberg} demonstrates that our constraints predict more moderate levels of assembly bias which follows the same trend.
+That is, assembly bias mostly affects the large scale and the quasi-linear clustering and the small scale clustering remains unaltered.
+In addition, the effect of assembly bias vanishes in the brightest galaxy samples.
+Moreover, we repeat our inference using the $\mathtt{BolshoiP}$ simulation.
+First, we find that our findings based on the $\mathtt{BolshoiP}$ simulation are consistent with constraints reported by \citet{zentner2016} that predicts positive satellite assembly bias for the $M_{\rm r}<-19, -20.5$ samples.
+However, we note that the results based on the $\mathtt{SMDP}$ simulation are more consistent with the picture provided by the previous models based on the abundance matching technique (e.g.
+\citealt{arz2014,lehman2015}).
 

### 2016-09-28 text/ms.tex
fixed a few citations

@@
 Furthermore, HOD is implemented in producing mock galaxy catalogs in the BOSS survey (\citealt{manera2013,white2014}).
-It has also been used in galaxy evolution studies (\citealt{conroy09,leauthaud12,behroozi13,hudson2015,zu2015,zu2016}).
+It has also been used in galaxy evolution studies (\citealt{conroy2009,leauthaud12,behroozi13,hudson2015,zu2015,zu2016}).
 
@@
 \citealt{tinker_density_hod} proposes an extension of the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
-Based on modeling the clustering and void statistics of the SDSS galaxies, \citealt{tinker_vpf_2008} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
+Based on modeling the clustering and void statistics of the SDSS galaxies, \citealt{edHOD-tinker} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
 By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citealt{croton2007} show that assembly bias significantly impacts the galaxy two-point correlation functions.
@@
 That is, even in the presence of assembly bias in a galaxy sample, one can fit the clustering of this sample with HOD, but that does not guarantee recovery of the true HOD parameters.
-\citet{mcewen2016} demonstrated that even with a galaxy catalog that has a significant level of assembly bias (e.g.
+\citet{edHOD-weinberg} demonstrated that even with a galaxy catalog that has a significant level of assembly bias (e.g.
 \citealt{hw2013}), it is possible to extract the matter power spectrum more accurately if an environment-dependent HOD ($P(N|M,\delta)$) is used.
@@
 
-Given the SDSS clustering measurements described in Section \ref{sec:data}, We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation (\citealt{bolshoi2016}).
+Given the SDSS clustering measurements described in Section \ref{sec:data}, We repeat the inference of the assembly bias parameters $\asat$ and $\acen$ with the $\mathtt{BolshoiP}$ simulation (\citealt{smallmultidark}).
 This $N$-body simulation is carried out with similar setting as the $\mathtt{Bolshoi}$ simulation with the exception that in the $\mathtt{BolshoiP}$ simulation, Planck cosmology is adapted and the mass per simulation particle is $1.49\times 10^8 \; h^{-1} M_{\odot}$.
@@
 \includegraphics[width=\textwidth]{hist_comparison.pdf}
-\caption{Constraints over the satellite assembly bias parameters from luminosity threshold samples $M_{\rm r}<-19 ,\; -20.5$, for two different simulations: $\mathtt{BolshoiP}$ (yellow), and $\mathtt{SMDPL}$ (green).
+\caption{Constraints over the satellite assembly bias parameters from luminosity-threshold samples $M_{\rm r}<-19 ,\; -20.5$, for two different simulations: $\mathtt{BolshoiP}$ (yellow), and $\mathtt{SMDPL}$ (green).
 The $\asat$ constraints found using the $\mathtt{BolshoiP}$ simulation favor more positive values of $\asat$, while the constraints found using the $\mathtt{SMDP}$ simulation favor zero satellite assembly bias.}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{post20_5combined.pdf}
+\includegraphics[width=0.9\textwidth]{post20_5combined.pdf}
 \caption{An example of posterior probability distribution over the parameters of the standard HOD model with no assembly bias (shown with yellow), and the HOD model with assembly bias (shown in blue).

### 2016-09-29 text/ms.tex
fixing a few typos

@@
 \documentclass[12pt, preprint]{aastex}
+%\documentclass[12pt, preprint]{emulateapj}
 \usepackage[breaklinks,colorlinks, 
@@
 
-Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark-matter halos.
+Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark matter halos.
 Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
@@
 \citet{tinker_void_2009} show that the properties of the galaxies that reside in voids can be explained by the halo mass in which they live, and their properties are independent of their large scale environment of the halos.
-\citealt{tinker_density_hod} proposes an extension of the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
-Based on modeling the clustering and void statistics of the SDSS galaxies, \citealt{edHOD-tinker} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
-By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citealt{croton2007} show that assembly bias significantly impacts the galaxy two-point correlation functions.
+\citet{tinker_density_hod} proposes an extension of the standard HOD model $P(N|M)$ such that the number of galaxies residing in a halo not only depends on the mass of the halo, but also on the large scale density contrast $P(N|M,\delta)$.
+Based on modeling the clustering and void statistics of the SDSS galaxies, \citet{edHOD-tinker} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
+By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citet{croton2007} show that assembly bias significantly impacts the galaxy two-point correlation functions.
 They also show that the effect is different for the faint and the bright samples.
-By applying a group finder to SDSS DR7 galaxies, \citealt{tinker2011} shows that the quenched fraction of galaxies is independent of the large-scale environment.
+By applying a group finder to SDSS DR7 galaxies, \citet{tinker2011} shows that the quenched fraction of galaxies is independent of the large-scale environment.
 
@@
 \begin{eqnarray}
-\langle N_{c,i} | M_{h},c\rangle &=& \langle N_{c} | M_{h}\rangle + \delta N _{c,i}, \; i=1,2 \label{eq:decoratedcentral} \\
-\langle N_{s,i} | M_{h},c\rangle &=& \langle N_{s} | M_{h}\rangle + \delta N _{s,i}, \; i=1,2 \label{eq:decoratedsatellite}
+\langle N_{c,i} | M_{h},c\rangle &=& \langle N_{c} | M_{h}\rangle + \Delta N _{c,i}, \; i=1,2 \label{eq:decoratedcentral} \\
+\langle N_{s,i} | M_{h},c\rangle &=& \langle N_{s} | M_{h}\rangle + \Delta N _{s,i}, \; i=1,2 \label{eq:decoratedsatellite}
 \end{eqnarray}
-where $\langle N_{c} | M_{h}\rangle$ and $\langle N_{s} | M_{h}\rangle$ are given by Eqs \ref{hod:central} and \ref{hod:satellite} respectively, and we have $\delta N_{s,1} + \delta N_{s,2} = 0$, and $\delta N_{c,1} + \delta N_{c,2} = 0$.
+where $\langle N_{c} | M_{h}\rangle$ and $\langle N_{s} | M_{h}\rangle$ are given by Eqs \ref{hod:central} and \ref{hod:satellite} respectively, and we have $\Delta N_{s,1} + \Delta N_{s,2} = 0$, and $\Delta N_{c,1} + \Delta N_{c,2} = 0$.
 These two conditions ensure the conservation of HOD.
@@
 
-In this occupation model, the allowable ranges that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take are given by 
+In this occupation model, the allowable ranges that quantities $\Delta N_{c,i}$ and $\Delta N_{s,i}$ can take are given by 
 \begin{eqnarray}
--\langle N_{c} | M_{h}\rangle \leq \delta N_{c,i} \leq \langle N_{c} | M_{h}\rangle
+\mathrm{max} \{-\langle N_{c} | M_{h}\rangle, \langle N_{c} | M_{h}\rangle -1 \} \leq &\Delta N_{c,i}& \leq \mathrm{min} \{\langle N_{c} | M_{h}\rangle, 1-\langle N_{c} | M_{h}\rangle\}
  , \label{eq:cen-bounds} \\
--\langle N_{s} | M_{h}\rangle \leq \delta N_{s,i} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
+-\langle N_{s} | M_{h}\rangle \leq & \Delta N_{s,i}& \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \label{positive_A} \\
-\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0, \label{negative_A}
+\Delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \Delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \label{positive_A} \\
+\Delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \Delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0, \label{negative_A}
 \end{eqnarray}
-where the subscript $\alpha = c , s$ stands for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs.
+where the subscript $\alpha = c , s$ stands for the centrals and satellites respectively, and $\Delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\Delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs.
 \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.
 
-For a given $\mathcal{A}_{\alpha}$, once $\delta N_{\alpha,1}$ is computed using equation (\ref{positive_A})---if $\mathcal{A}_{\alpha}>0$---or equation (\ref{negative_A})---if $\mathcal{A}_{\alpha}<0$---, $\delta N_{\alpha,2} = 1 - \delta N_{\alpha,1}$ is computed.
+For a given $\mathcal{A}_{\alpha}$, once $\Delta N_{\alpha,1}$ is computed using equation (\ref{positive_A})---if $\mathcal{A}_{\alpha}>0$---or equation (\ref{negative_A})---if $\mathcal{A}_{\alpha}<0$---, $\Delta N_{\alpha,2} = 1 - \Delta N_{\alpha,1}$ is computed.
 At a fixed halo mass $M_{h}$, once the first moments of occupation statistics for the $type$-1 and $type$-2 halos are determined, we perform the same procedure described in \ref{subsubsec:hod} to populate the halos with mock galaxies.
@@
 $M_{\rm r} < -21.5$ and $M_{\rm r} < -21$, $\acen$ is poorly constrained and the constraints are equivalent to zero.
-As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift toward positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$.
+As we investigate less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift toward positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$.
 Furthermore, the posterior constraints on the assembly bias parameters in the slightly fainter samples, i.e.
@@
 
-Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$.
-From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $M \sim 10^11.7 \; h^{-1}M_{\odot}$ at the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
+Furthermore, investigation of the scale dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$.
+From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $M \sim 10^{11.7} \; h^{-1}M_{\odot}$ at the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing).
 The clustering of these population of halos is therefore dictated by that of the massive halos.
-Note that this scale-dependent bias feature vanishes as we probe high mass halos.
+Note that this scale-dependent bias feature vanishes in high mass halos.
 
@@
 The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest samples ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well.
-As we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
+In brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.
 
@@
 That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales.
-Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that assembly bias becomes less significant as we probe brighter galaxy samples.
+Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that assembly bias becomes less significant in brighter galaxy samples.
 Furthermore, we notice that our mock catalogs favor more moderate levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
@@
 Also note that, the difference between both BIC and AIC scores are marginal.
-That is, although the HOD model is preferred, it is not strongly favored by the data.
 

### 2016-10-06 text/ms.tex
final text prior to submission

@@
 %% you desire.
-\title{How do galaxies get assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering}
+\title{How are galaxies assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering}
 
@@
 
-Clustering of dark matter halos has been shown to depend on halo properties beyond mass such as halo concentration.
-This phenomenon is referred to as halo assembly bias.
-Standard halo occupation modeling (HOD) in large-scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
+Clustering of dark matter halos has been shown to depend on halo properties beyond mass such as halo concentration, a phenomenon referred to as halo assembly bias.
+Standard halo occupation modeling (HOD) in large scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
 Modeling of galaxy clustering can face systematic effects if the number or properties of galaxies are correlated with other halo properties.
@@
 Given the SDSS clustering data, our constraints on HOD with assembly bias, suggests that satellite population is not correlated with halo concentration at fixed halo mass.
-Furthermore, in terms of the number of centrals at fixed halo mass, our results favor lack of correlation with halo concentration in the most luminous samples ($M_{\rm r}<-21.5,-21$), modest levels of correlation for $M_{\rm r}<-20.5,-20, -19.5$ samples, lack of correlation for $M_{\rm r}<-19,-18.5$ samples, and anti-correlation for the faintest sample $M_{\rm r}<-18$.
+Furthermore, in terms of the occupation of centrals at fixed halo mass, our results favor lack of correlation with halo concentration in the most luminous samples ($M_{\rm r}<-21.5,-21$), modest levels of correlation for $M_{\rm r}<-20.5,-20, -19.5$ samples, lack of correlation for $M_{\rm r}<-19,-18.5$ samples, and anti-correlation for the faintest sample $M_{\rm r}<-18$.
 
-We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of assembly bias.
+We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of assembly bias that is only present in the central occupation.
 Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
@@
 HOD is an empirical framework that provides an analytic prescription for the expected number of galaxies $N$ that reside in halos by specifying a probability distribution function $P(N|x)$ where $x$ is a property of the halo.
-Under standard HOD modeling, the assumption is made that the halo mass $M$ alone is sufficient in determining the galaxy population of a halo.
+The assumption of the standard HOD modeling is that the halo mass $M$ alone is sufficient in determining the galaxy population of a halo.
 That is, the statistical properties of galaxies is governed by the halo mass.
-Mathematically, this assumption can be written as $P(N_g|M,\{x\})=P(N_g|M)$ where $\{x\}$ is the set of all possible halo properties beyond halo mass $M$.
+Mathematically, this assumption can be written as $P(N|M,\{x\})=P(N|M)$ where $\{x\}$ is the set of all possible halo properties beyond halo mass $M$.
 
-Despite this very simplifying assumption, the models of galaxy--halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g.
+Despite this simplifying assumption, the models of galaxy--halo connection based on HOD have been successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g.
 \citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}).
@@
 
-This simple assumption of standard HODs  
-does not sufficiently model the complexity of structure formation. Numerous $N$-body simulations that examine the clustering of 
+The complexity of structure formation however, is not sufficiently modeled under the standard HOD framework. Numerous $N$-body simulations that examine the clustering of 
 dark matter halos have demonstrated that halo clustering is correlated with the formation 
@@
 This phenomenon is known as halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}). 
-There is even support for halo assembly bias in observations (\citealt{miyatake2016,more2016}).
+There is support for halo assembly bias in observations of SDSS redMaPPer galaxy clusters (\citealt{miyatake2016}).
 
 Furthermore, the properties of galaxies within the halo may also depend on the halo's formation history.
-Then we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos, environment, and etc.
-There have been many attempts in the literature at examining the dependence of galaxy properties on larger scale environment of the halos.
+Then we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos.
+There have been many attempts in the literature at examining the dependence of galaxy properties on environment of the halos.
 But the results are mixed, and there is very little consensus.
@@
 Based on modeling the clustering and void statistics of the SDSS galaxies, \citet{edHOD-tinker} shows that the dependence of the expected number of central galaxies on large scale density is not very strong.
-By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citet{croton2007} show that assembly bias significantly impacts the galaxy two-point correlation functions.
+By randomly shuffling the galaxies among host halos of similar mass in the Millenium simulation, \citet{croton2007} shows that assembly bias significantly impacts the galaxy two-point correlation functions.
 They also show that the effect is different for the faint and the bright samples.
@@
 Based on a group catalog of SDSS galaxies, \citet{blanton_group_2007} find that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
-Based on an alternative group catalog, \citet{wang2013} show that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
+Based on an alternative group catalog, \citet{wang2013} shows that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
 
 Another family of empirical galaxy--halo connection models is \emph{Abundance} \emph{Matching}.
-In Abundance Matching models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity or stellar mass
-(\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
-In practice, the standard abundance-matching models assume a monotonic mapping between the stellar mass/luminosity of galaxies and some host-halo property, such as 
-the maximum circular velocity the host halo $V_\mathrm{max}$ that traces the depth of the gravitational potential well of the halo.
-Furthermore, a scatter is assumed in this one-to-one relation between galaxy property and halo/subhalo property.
-With this framework, abundance-matching models have been successfully used in modeling a wide range of the
-statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).
+In Abundance Matching models, galaxies are assumed to live in halos and are assigned luminosities or stellar masses by assuming a monotonic mapping.
+In this monotonic mapping, the abundance of the halos are matched to the abundance of some property of galaxies (\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}).
+One of the most commonly used host halo properties in abundance matching is the maximum circular velocity of the host halo $V_\mathrm{max}$ that traces the depth of the gravitational potential well of the halo.
+Furthermore, a scatter is assumed in this mapping.
+Within this galaxy--halo connection framework, abundance matching models have been successfully used in modeling a wide range of the statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).
 
-It has been shown that the abundance-matching mock catalogs that use $V_{\rm max}$ (see \citealt{hw2013,arz2014}), or the ones that use some combination of $V_{\rm max}$ and host halo/subhalo virial mass $M_{\rm vir} $(see \citealt{lehman2015}) exhibit significant levels of assembly bias.
+It has been shown that the abundance matching mock catalogs that use $V_{\rm max}$ (see \citealt{hw2013,arz2014}), or the ones that use some combination of $V_{\rm max}$ and host halo virial mass $M_{\rm vir}$ (see \citealt{lehman2015}) exhibit significant levels of assembly bias.
 That is, halo occupation in these models depends not only on halo mass, but also on other halo properties.
-This has been demonstrated by randomizing the galaxies among host halos of in bins of halo mass, such that the HOD remains constant, and comparing the difference in the 2PCF of the randomized catalog and the original mock catalog.
+This has been demonstrated by randomizing the galaxies among host halos in bins of halo mass, such that the HOD remains constant, and then comparing the difference in the 2PCF of the randomized catalog and that of the original mock catalog.
 
-Abundance-Matching models can be extended to account for even higher orders of galaxy 
-assembly bias. In so called \emph{Age-Matching} models, galaxy color is abundance-matched
-to subhalo formation time so that older (redder) galaxies preferentially reside in older halos (\citealt{hw2013}).
+Age Matching models extend the Abundance Matching models to account for even higher orders of galaxy 
+assembly bias.
+In these models, galaxy color is matched to halo formation time so that older (redder) galaxies preferentially reside in older halos (\citealt{hw2013}).
 \citet{hearin2014} demonstrates that such an approach can reproduce a range of color and luminosity-dependent statistics of SDSS galaxies such as the 2PCF and galaxy-galaxy lensing.
@@
 
-Furthermore, we discuss how taking assembly bias into account in a more complex HOD model can improve our modeling of galaxy clustering in certain brightness limit.
-Then, we make a qualitative comparison between the levels of assembly bias in the mock catalogs created from our constrained on the decorated HOD model, and the \citet{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
+Furthermore, we discuss how taking assembly bias into account in a more complex HOD model can improve our modeling of galaxy clustering in certain brightness limits.
+Then, we make a qualitative comparison between the levels of assembly bias in the mock catalogs created from our constraints on the decorated HOD model, and the \citealt{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
+Our comparison shows the levels of assembly bias seen in the predictions of both models follow the same trend.
+That is assembly bias is more prominent in lower luminosity-threshold samples and its impact on galaxy clustering is only significant on large scales.
 
 In order to investigate whether the additional complexity of the decorated HOD model is demanded by the galaxy clustering data, we perform a model comparison between the standard HOD model and the HOD model with assembly bias.
-We also discuss the effect of our choice of $N$-body simulation on our constraints, and previous works in the literature based on smaller $N$-body simulations (\citealt{zentner2016}).
+We also discuss the effect of our choice of $N$-body simulation on our constraints, and previous works in the literature (\citealt{zentner2016}) based on smaller $N$-body simulations.
+In addition to analysis of the luminosity-threshold samples presented in \citet{zentner2016}, we consider the faintest ($M_{\rm r} < -18,-18.5$) and the brightest ($M_{\rm r}<-20.5$) galaxy samples.
+For the samples considered in both \citet{zentner2016} and this investigation, we compare the constraints on the expected levels of assembly bias.
 
@@
 \begin{eqnarray}
-\langle N_{\rm cen}(M_{h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
-\langle N_{\rm sat}(M_{h}) \rangle &=& \Big( \frac{M_{h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
+\langle N_{\rm c}| M_{h} \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
+\langle N_{\rm s} | M_{h} \rangle &=& \Big( \frac{M_{h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
 \end{eqnarray}
@@
 
-In this occupation model, the allowable ranges that quantities $\Delta N_{c,i}$ and $\Delta N_{s,i}$ can take are given by 
+In this occupation model, the allowable ranges that quantities $\Delta N_{c,1}$ and $\Delta N_{s,1}$ can take are given by 
 \begin{eqnarray}
@@
 Moreover as \citet{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$).
-This scales can be impacted by fiber collision systematics.
+This scale can be impacted by fiber collision systematics.
 Precise investigation of the possible impact of this signal on the galaxy clustering modeling requires accurate measurements of 2PCF on small scales.
@@
 The comoving volumes of the $M_{\rm r}<-21, \; 21.5$ samples are 71.74 and 134.65 (in units of $10^{6} h^{-3}\rm{Mpc}^{3}$) respectively.
-Since we are not studying very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.
+Since we are not studying very large scale clustering ($r_{p,\; \rm max} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.
 
@@
 It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the more complex halo occupation model with assembly bias.
-As a result of apportioning more central galaxies to the high-$c$ halos relative to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and large scales.
+As a result of apportioning more central galaxies to the high-$c$ halos relative to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and large scales.
 This can be also noted in significantly lower $\chi^{2}$ values---at the cost more model flexibility and higher degrees of freedom---achieved by the assembly bias model in these luminosity-threshold samples (see Table \ref{tab:constraints}).
@@
 
-The satellite assembly bias can only alter the galaxy clustering at small-to-intermediate scales.
-Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm sat} N_{\rm sat} \rangle$.
+The satellite assembly bias can only significantly alter the galaxy clustering at small-to-intermediate scales.
+Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm s} N_{\rm s} \rangle$.
 This results in boosting the small-scale clustering.
@@
 
-It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range in which the condition $0<\langle N_{\rm cen}|M \rangle<1$ is met.
+It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range in which the condition $0<\langle N_{\rm c}|M \rangle<1$ is met.
 Consequently, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering.
@@
 The only cases in which there are mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples.
-However, these tensions are within one-sigma level.
+However, these tensions are still within one-sigma level.
 For instance, Figure \ref{fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias.
@@
 For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the original catalogs of \citet{hw2013} is shown in Figure \ref{fig:randomized} with the red curves.
-As demonstrated in Figure \ref{fig:randomized} (and as previously noted by \citealt{arz2014,edHOD-weinberg}), the relative difference in $w_{p}$ is only significant in large scales.
-This implies that in these catalogs, only the central galaxies are affected by assembly bias.
+As demonstrated in Figure \ref{fig:randomized} (and as previously noted by \citealt{arz2014,edHOD-weinberg}), the relative difference in $w_{p}$ is only significant in relatively large scales.
+This implies that in these catalogs, only the central occupation are affected by assembly bias.
 This is in agreement with our findings.
@@
 Furthermore, we investigate whether the levels of assembly bias predicted by our findings are in agreement with the abundance matching catalogs of \citet{hw2013}.
-First, we make random draws from the posterior pdf over the parameters of the model with assembly bias.
+First, we make random draws from the posterior probability distribution function over the parameters of the model with assembly bias.
 Then, we create mock catalogs with these random draws, and then we compute the difference in $w_{p}$ between the randomized catalogs and the original catalogs.
@@
 We note that our findings follow the same trend.
-That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales.
+That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales ($r_{p} > 1 Mpc \; h^{-1}$).
 Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that assembly bias becomes less significant in brighter galaxy samples.
@@
 In the case of the satellite assembly bias parameters however, constraints from the $\mathtt{BolshoiP}$ simulation for the luminosity threshold samples $M_{\rm r}<-20.5, -19$ favor more positive values of the parameter, while our constraints from the $\mathtt{SMDP}$ simulation for these two luminosity thresholds favor zero satellite assembly bias.
-As it is shown in the lower panel of Figure \ref{fig:bias_comparison}, our constraints from the $\mathtt{BolshoiP}$ simulations for the $M_{\rm r}<-21, -20.5, -20, -19.5, -19$ samples are consistent with the lower and upper bounds (shown with the shaded blue region) reported by \citet{zentner2016} that uses the same simulation but slightly different $w_{p}$ measurements (\citealt{zehavi2011}).
+As it is shown in the lower panel of Figure \ref{fig:bias_comparison}, our constraints from the $\mathtt{BolshoiP}$ simulations for the $M_{\rm r}<-21, -20.5, -20, -19.5, -19$ samples are consistent with the lower and upper bounds (shown with the shaded blue region) reported by \citet{zentner2016} that uses the same simulation but different $w_{p}$ measurements (\citealt{zehavi2011}).
 Therefore, there is some discrepancy between our $\asat$ constraints using the $\mathtt{SMDP}$ simulation and the $\mathtt{BolshoiP}$ simulations.
@@
 That is, the difference in $w_{p}$ between the mock catalogs and the randomized catalogs is mostly on large scales where the clustering is governed by the central galaxies.
+That is, the impact of assembly bias on the satellite occupation is negligible and only the central occupation is affected.
 
@@
 In addition, the effect of assembly bias vanishes in the brightest galaxy samples.
+
 Moreover, we repeat our inference using the $\mathtt{BolshoiP}$ simulation. 
-First, we find that our findings based on the $\mathtt{BolshoiP}$ simulation are consistent with constraints reported by \citet{zentner2016} that predicts positive satellite assembly bias for the $M_{\rm r}<-19, -20.5$ samples.
+We find that our findings based on the $\mathtt{BolshoiP}$ simulation are consistent with constraints reported by \citet{zentner2016} (in the $M_{\rm r}<-21, -20.5, -20, -19.5, -19$ luminosity-threshold samples) that predicts positive satellite assembly bias (correlation between the expected number of satellites and $V_{\rm max}$ at fixed host halo mass) for the $M_{\rm r}<-19, -20.5$ samples.
 However, we note that the results based on the $\mathtt{SMDP}$ simulation are more consistent with the picture provided by the previous models based on the abundance matching technique (e.g.
 \citealt{arz2014,lehman2015}).
+That is, only the large-scale clustering, governed by the centrals, is affected by assembly bias.
 
@@
 
-We are grateful to David~W.~Hogg, Yao~Yun Mao, Chang~Hoon~Hahn, Andrew Hearin, Andrew Zentner, Tomomi Sunayama, and Chia~Hsun~Chuang for
-discussions related to this work.
+We are grateful to David~W.~Hogg, Chang~Hoon~Hahn, Alex~I.~Malz, Andrew~Hearin, Andrew~Zentner, Chia-Hsun~Chuang, Michael~R.~Blanton, and Kilian~Walsh for discussions related to this work.
 This work was supported by the NSF grant AST-1517237.
@@
 All of the code written for this project is available in an open-source
-code repository at \url{https://github.com/mjvakili/gambly}. All the MCMC chains of our analysis will be available upon request.
+code repository at \url{https://github.com/mjvakili/gambly}.
 The SDSS clustering measurements and the covariance matrices used in this work are available at \url{http://sdss4.shao.ac.cn/guoh/files/wpxi_measurements_Guo15.tar.gz}.
@@
 We thank Peter Behroozi for making the halo catalogs publicly available.
+In this work we have made use of the publicly available codes: corner (\citealt{corner}), emcee (\citealt{emcee}), halotools (\citealt{halotools}), Corrfunc (\citealt{corrfunc}), and changtools (\url{https://github.com/changhoonhahn/ChangTools}).
+The abundance matching mock catalogs used in this study are available at (\url{http://logrus.uchicago.edu/~aphearin/}).
 
@@
 The $\acen$ constraints for the $M_{\rm r} < -20.5, -20, -19.5$ samples favor positive values of $\acen$ with the tightest constraint coming from the $M_{\rm r} < -20$ sample.
+The $\acen$ constraints for the $M_{\rm r}<-18$ sample favor negative values of $\acen$.
 All the $\asat$ constraints are consistent with no satellite assembly bias.}
@@
 In all luminosity threshold samples, predictions of the two models for small scale clustering are consistent.
-In the samples that favor more positive values of the central assembly bias parameter ($M_{\rm r}<-19.5,-19,-20,-20.5$), modeling of the intermediate and large-scale clustering is slightly improved.
-The large-scale clustering modeling of the $M_{\rm r}<-18$ sample is also improved because of negative constraints on $\acen$.}
+In the samples that favor more positive values of the central assembly bias parameter ($M_{\rm r}<-19.5,-19,-20,-20.5$), modeling of the intermediate and large scale clustering is slightly improved.
+The large scale clustering modeling of the $M_{\rm r}<-18$ sample is also improved because of negative constraints on $\acen$ which is equivalent to allocation of more central galaxies in low concentration halos at fixed halo mass.}
 \label{fig:wpres}
@@
 \includegraphics[width=\textwidth]{paper_wprandom.pdf}
- \caption{Demonstration of the relative difference in $w_{p}$ between randomized and non-randomized catalogs for different luminosity threshold samples: $M_{\mathrm r}<-20,-20.5,-21.5$.
-The errorbars show the diagonal elements of the covariance matrix.
+ \caption{Demonstration of the relative difference in $w_{p}$ between randomized and non-randomized catalogs for different luminosity threshold samples: $M_{\mathrm r}<-20,-20.5,-21$.
+The errorbars are from the diagonal elements of the covariance matrix.
 The blue lines correspond to the random draws from the posterior probability (summarized in Table \ref{tab:constraints}) over the parameters of the HOD model with assembly bias.
@@
 Shaded blue regions show the upper and lower bounds reported by \citet{zentner2016} that uses the $\mathtt{BolshoiP}$ and clustering measurements of \citet{zehavi2011}.
+For the confidence intervals corresponding to the shaded blue regions, we refer the readers to Table 2 of \citet{zentner2016}.
 The central assembly bias constraints found from the two simulations are consistent, with the constraints for from the $\mathtt{SMDP}$ simulation being tighter for the most luminous samples.
-The constraints on $\asat$ from the two simulations are in agreements with the exception of $M_{\rm r}<-19 ,\; -20.5$ samples that favor more positive values of $\asat$ when the $\mathtt{BolshoiP}$ simulation is used.}
+The constraints on $\asat$ from the two simulations are largely in agreement with the exception of $M_{\rm r}<-19 ,\; -20.5$ samples that favor more positive values of $\asat$ when the $\mathtt{BolshoiP}$ simulation is used.}
 \label{fig:bias_comparison}
@@
 The dark (light) blue shaded regions show the 68$\%$ (95 $\%$) confidence intervals.
-The constraints on $\acen$ and $\asat$ show positive correlation between the central fraction and the halo concentration at fixed halo mass, and lack of correlation between the satellite fraction and halo concentration at fixed halo mass.}
+The constraints on $\acen$ and $\asat$ show positive correlation between the central occupation and the halo concentration at fixed halo mass, and lack of correlation between the satellite occupation and halo concentration at fixed halo mass.}
 \label{fig:posterior}

### 2017-03-05 code/adhoc_mcmc.py
model covariance

@@ -50,8 +50,11 @@ def lnPost(theta, **kwargs):
     	prior_range = kwargs['prior_range']
     	# Likelihood
     	model_obvs = generator(theta, prior_range)
-        model_nbar , model_wp = model_obvs[0] , model_obvs[1]
-        
+        model_nbar , model_wp , model_nbar_var , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2] , model_obvs[3]
+       
+        wp_cov = wp_cov + model_wp_var
+        nbar_var = nbar_var + model_nbar_var 
+
         res_nbar = model_nbar - data_nbar
         res_wp = model_wp - data_wp
 

### 2017-03-05 code/biased_hod.py

@@ -42,6 +42,7 @@ class MCMC_model(object):
         self.boxsize = self.halocat.Lbox
         self.nthreads = 1
         self.pimax = 40.0
+        self.rbins = np.loadtxt(self.binfile) 
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
         self.autocorr = 1
@@ -64,6 +65,38 @@ class MCMC_model(object):
         y = self.model.mock.galaxy_table['y']
         z = self.model.mock.galaxy_table['z']
         vz = self.model.mock.galaxy_table['vz']
+        
+        ########################## rewrite for model covariance ######################
+        
+        #applying RSD
+        pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
+        # enforcing PBC
+        pos = enforce_periodicity_of_box(pos, self.boxsize)
+        pos = pos.astype(np.float32)
+        #x, y, z = pos[:,0] , pos[:,1] , pos[:,2]
+
+        wp , wp_cov = helpers.projected_correlation(pos, self.rbins, self.pimax, self.boxsize, 
+                                           jackknife_nside = 8 , bias_correction = True) 
+
+        nbar = 1.*len(pos)/(self.boxsize)**3.
+        
+        nsub = 8. #FIXME
+        number_of_subboxes = nsub ** 3
+        subbox_size = self.boxsize / nsub
+        
+        nbars = np.zeros((number_of_subboxes , 1)) #placeholder for nbars of jk subsamples
+
+        for subvol_index in xrange(number_of_subboxes):
+
+            sub_rsd_pos = mask_positions(rsd_pos , subvol_index , nsub)
+            sub_rsd_pos = sub_rsd_pos.astype(np.float32)
+            nbars[subvol_index] = 1.*len(sub_rsd_pos)/subbox_size**3.
+           
+        nbar_var = np.array([np.var(nbars)])    
+        
+        ######################## End of rewriting for model covariance ############## 
+        
+        """
         # applying RSD
         pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
         # enforcing PBC
@@ -75,5 +108,23 @@ class MCMC_model(object):
                                            self.binfile, x, y, z)
         wp = np.array(results_wp)[:,3]
         nbar = 1.*len(pos)/(self.boxsize)**3.
+        """
[…]

### 2017-03-05 code/hod.py

@@ -34,6 +34,8 @@ class MCMC_model(object):
         self.pimax = 40.0
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
+        
+        self.rbins = np.loadtxt(self.binfile) 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):
@@ -57,11 +59,67 @@ class MCMC_model(object):
         # enforcing PBC
         pos = enforce_periodicity_of_box(pos, self.boxsize)
         pos = pos.astype(np.float32)
+         
+        wp , wp_cov = helpers.projected_correlation(pos, self.rbins, self.pimax, self.boxsize, 
+                                           jackknife_nside = 8 , bias_correction = True) 
+
+        nbar = 1.*len(pos)/(self.boxsize)**3.
+        
+        nsub = 8. #FIXME
+        number_of_subboxes = nsub ** 3
+        subbox_size = self.boxsize / nsub
+        
+        nbars = np.zeros((number_of_subboxes , 1)) #placeholder for nbars of jk subsamples
+
+        for subvol_index in xrange(number_of_subboxes):
+
+            sub_rsd_pos = mask_positions(rsd_pos , subvol_index , nsub)
+            sub_rsd_pos = sub_rsd_pos.astype(np.float32)
+            nbars[subvol_index] = 1.*len(sub_rsd_pos)/subbox_size**3.
+           
+        nbar_var = np.array([np.var(nbars)])    
+        
+        ######################## End of rewriting for model covariance ############## 
+        
+        """
+        # applying RSD
+        pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
+        # enforcing PBC
+        pos = enforce_periodicity_of_box(pos, self.boxsize)
+        pos = pos.astype(np.float32)
         x, y, z = pos[:,0] , pos[:,1] , pos[:,2]
         results_wp = _countpairs.countpairs_wp(self.boxsize, self.pimax, 
                                            self.nthreads,
                                            self.binfile, x, y, z)
         wp = np.array(results_wp)[:,3]
         nbar = 1.*len(pos)/(self.boxsize)**3.
+        """
+        return nbar , wp , nbar_var , wp_cov
 
-        return nbar , wp
+
+        #x, y, z = pos[:,0] , pos[:,1] , pos[:,2]
[…]

### 2017-03-05 code/mcmc.py

@@ -51,7 +51,11 @@ def lnPost(theta, **kwargs):
     	prior_range = kwargs['prior_range']
     	# Likelihood
     	model_obvs = generator(theta, prior_range)
-        model_nbar , model_wp = model_obvs[0] , model_obvs[1]
+        
+        model_nbar , model_wp , model_nbar_var , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2] , model_obvs[3]
+       
+        wp_cov = wp_cov + model_wp_var
+        nbar_var = nbar_var + model_nbar_var 
         
         res_nbar = model_nbar - data_nbar
         res_wp = model_wp - data_wp

### 2017-03-05 code/biased_hod.py
rbins

@@ -42,9 +42,9 @@ class MCMC_model(object):
         self.boxsize = self.halocat.Lbox
         self.nthreads = 1
         self.pimax = 40.0
-        self.rbins = np.loadtxt(self.binfile) 
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
+        self.rbins = np.loadtxt(self.binfile) 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):

### 2017-03-05 code/CorrelationFunction.py
cleaned up model covariance

@@ -1,0 +1,194 @@
+"""
+Copoed from Yao Mao's helpers:
+
+https://github.com/manodeep/yymao-helpers 
+
+"""
+__all__ = ['projected_correlation']
+from itertools import izip
+import math
+import numpy as np
+from scipy.integrate import quad
+from fast3tree import fast3tree
+
+def _yield_periodic_points(center, dcorner1, dcorner2, box_size):
+    cc = np.array(center)
+    flag = (cc+dcorner1 < 0).astype(int) - (cc+dcorner2 >= box_size).astype(int)
+    cp = cc + flag*box_size
+    a = range(len(cc))
+    for j in xrange(1 << len(cc)):
+        for i in a:
+            if j >> i & 1 == 0:
+                cc[i] = center[i]
+            elif flag[i]:
+                cc[i] = cp[i]
+            else:
+                break
+        else:
+            yield cc
+
+def _jackknife_2d_random(rbins, box_size, jackknife_nside):
+    def corner_area(x, y):
+        a = math.sqrt(1.0-x*x)-y
+        b = math.sqrt(1.0-y*y)-x
+        theta = math.asin(math.sqrt(a*a+b*b)*0.5)*2.0
+        return (a*b + theta - math.sin(theta))*0.5
+
+    def segment_without_corner_area(x, r):
+        half_chord = math.sqrt(1.0-x*x)
+        return math.acos(x) - x*half_chord \
+                - quad(corner_area, 0, min(half_chord, 1.0/r), (x,))[0]*r
+
+    def overlapping_circular_areas(r):
+        if r*r >= 2: return 1.0
+        return (math.pi - quad(segment_without_corner_area, 0, min(1, 1.0/r), \
+                (r,))[0]*4.0*r)*r*r
+
+    overlapping_circular_areas_vec = np.vectorize(overlapping_circular_areas, \
+            [float])
+
+    side_length = box_size/float(jackknife_nside)
+    square_area = 1.0/float(jackknife_nside*jackknife_nside)
+    rbins_norm = rbins/side_length
+    annulus_areas = np.ediff1d(overlapping_circular_areas_vec(rbins_norm))
+    annulus_areas /= np.ediff1d(rbins_norm*rbins_norm)*math.pi
+    return 1.0 - square_area * (2.0 - annulus_areas)
+
+def projected_correlation(points, rbins, zmax, box_size, jackknife_nside=0, \
+        bias_correction=True):
+    """
+    Calculate the projected correlation function wp(rp) and its covariance 
[…]

### 2017-03-05 code/adhoc_mcmc.py

@@ -50,10 +50,10 @@ def lnPost(theta, **kwargs):
     	prior_range = kwargs['prior_range']
     	# Likelihood
     	model_obvs = generator(theta, prior_range)
-        model_nbar , model_wp , model_nbar_var , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2] , model_obvs[3]
+        model_nbar , model_wp , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2]
        
         wp_cov = wp_cov + model_wp_var
-        nbar_var = nbar_var + model_nbar_var 
+        nbar_var = nbar_var
 
         res_nbar = model_nbar - data_nbar
         res_wp = model_wp - data_wp

### 2017-03-05 code/biased_hod.py

@@ -4,8 +4,11 @@ Central/Satellite galaxy assembly biased model
 import numpy as np
 import os.path as path
 
+import CorrelationFunction as helpers
+
 from Corrfunc import _countpairs
 from Corrfunc.utils import read_catalog
+#from Corrfunc.theory.wp import wp
 
 from halotools.sim_manager import CachedHaloCatalog
 from halotools.empirical_models import HodModelFactory
@@ -44,7 +47,7 @@ class MCMC_model(object):
         self.pimax = 40.0
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
-        self.rbins = np.loadtxt(self.binfile) 
+        self.rbins = np.loadtxt("rbins.dat") 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):
@@ -65,66 +68,71 @@ class MCMC_model(object):
         y = self.model.mock.galaxy_table['y']
         z = self.model.mock.galaxy_table['z']
         vz = self.model.mock.galaxy_table['vz']
-        
-        ########################## rewrite for model covariance ######################
-        
-        #applying RSD
-        pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
-        # enforcing PBC
-        pos = enforce_periodicity_of_box(pos, self.boxsize)
-        pos = pos.astype(np.float32)
-        #x, y, z = pos[:,0] , pos[:,1] , pos[:,2]
 
-        wp , wp_cov = helpers.projected_correlation(pos, self.rbins, self.pimax, self.boxsize, 
-                                           jackknife_nside = 8 , bias_correction = True) 
-
-        nbar = 1.*len(pos)/(self.boxsize)**3.
-        
-        nsub = 8. #FIXME
-        number_of_subboxes = nsub ** 3
-        subbox_size = self.boxsize / nsub
-        
-        nbars = np.zeros((number_of_subboxes , 1)) #placeholder for nbars of jk subsamples
-
-        for subvol_index in xrange(number_of_subboxes):
-
-            sub_rsd_pos = mask_positions(rsd_pos , subvol_index , nsub)
-            sub_rsd_pos = sub_rsd_pos.astype(np.float32)
-            nbars[subvol_index] = 1.*len(sub_rsd_pos)/subbox_size**3.
-           
-        nbar_var = np.array([np.var(nbars)])    
-        
[…]

### 2017-03-05 code/hod.py

@@ -6,7 +6,7 @@ import os.path as path
 
 from Corrfunc import _countpairs
 from Corrfunc.utils import read_catalog
-
+import CorrelationFunction as helpers
 from halotools.sim_manager import CachedHaloCatalog
 from halotools.empirical_models import PrebuiltHodModelFactory
 from halotools.empirical_models.factories.mock_helpers import three_dim_pos_bundle
@@ -35,7 +35,7 @@ class MCMC_model(object):
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
         
-        self.rbins = np.loadtxt(self.binfile) 
+        self.rbins = np.loadtxt("rbins.dat") 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):
@@ -58,68 +58,63 @@ class MCMC_model(object):
         pos = return_xyz_formatted_array(x, y, z, velocity = vz, velocity_distortion_dimension = 'z')
         # enforcing PBC
         pos = enforce_periodicity_of_box(pos, self.boxsize)
-        pos = pos.astype(np.float32)
-         
+        #pos = pos.astype(np.float32)
+
+              
         wp , wp_cov = helpers.projected_correlation(pos, self.rbins, self.pimax, self.boxsize, 
                                            jackknife_nside = 8 , bias_correction = True) 
-
+        
         nbar = 1.*len(pos)/(self.boxsize)**3.
         
-        nsub = 8. #FIXME
+        """
+        nsub = 8 #FIXME
         number_of_subboxes = nsub ** 3
         subbox_size = self.boxsize / nsub
         
         nbars = np.zeros((number_of_subboxes , 1)) #placeholder for nbars of jk subsamples
-
+        
         for subvol_index in xrange(number_of_subboxes):
-
-            sub_rsd_pos = mask_positions(rsd_pos , subvol_index , nsub)
-            sub_rsd_pos = sub_rsd_pos.astype(np.float32)
-            nbars[subvol_index] = 1.*len(sub_rsd_pos)/subbox_size**3.
-           
-        nbar_var = np.array([np.var(nbars)])    
-        
-        ######################## End of rewriting for model covariance ############## 
-        
+             
+            sub_pos = mask_positions(pos , self.boxsize, subvol_index , nsub)
+            print sub_pos.shape
[…]

### 2017-03-05 code/mcmc.py

@@ -52,10 +52,10 @@ def lnPost(theta, **kwargs):
     	# Likelihood
     	model_obvs = generator(theta, prior_range)
         
-        model_nbar , model_wp , model_nbar_var , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2] , model_obvs[3]
+        model_nbar , model_wp , model_wp_var = model_obvs[0] , model_obvs[1] , model_obvs[2]
        
         wp_cov = wp_cov + model_wp_var
-        nbar_var = nbar_var + model_nbar_var 
+        nbar_var = nbar_var
         
         res_nbar = model_nbar - data_nbar
         res_wp = model_wp - data_wp

### 2017-03-06 code/biased_hod.py
uptodate hpc jobs

@@ -38,7 +38,8 @@ class MCMC_model(object):
         
         self.Mr = Mr
         self.model = composite_model(Mr)
-        self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+        self.halocat = CachedHaloCatalog(simname = 'smdp', redshift = 0.0 , version_name = 'mj', halo_finder = 'rockstar')
+        #self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0.0 , halo_finder = 'rockstar')
 
         ###pair counter settings ###
 
@@ -47,7 +48,7 @@ class MCMC_model(object):
         self.pimax = 40.0
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
-        self.rbins = np.loadtxt("rbins.dat") 
+        self.rbins = np.loadtxt("/scratch/mv1003/projects/gambly/code/rbins.dat") 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):

### 2017-03-06 text/ms.tex
the most up-to-date version of the text

@@
 %\documentclass[12pt, preprint]{emulateapj}
-\usepackage[breaklinks,colorlinks, 
-urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{graphicx}	% For figures
@@
 \newcommand{\asat}{\mathcal{A}_{\rm sat}}
-%\newcommand{\comment}[1]{{\bf \textcolor{red}{ #1}}}
 \newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}
-
-%% preprint2 produces a double-column, single-spaced document:
-
-%% \documentclass[preprint2]{aastex}
-
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-%% If you are submitting to a journal that translates manuscripts
-%% into SGML, you need to follow certain guidelines when preparing
-%% your macros. See the AASTeX v5.x Author Guide
-%% for information.
-
-%% You can insert a short comment on the title page using the command below.
-
-%\slugcomment{Not to appear in Nonlearned J., 45.}
-
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%% The left head contains a list of authors,
-%% usually a maximum of three (otherwise use et al.).  The right
-%% head is a modified title of up to roughly 44 characters.
-%% Running heads will not print in the manuscript style.
-
-%\shorttitle{Collapsed Cores in Globular Clusters}
-%\shortauthors{Djorgovski et al.}
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
 
@@
 
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
 \title{How are galaxies assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering}
 
-%%\title{Collapsed Cores in Globular Clusters, \\
-%%    Gauge-Boson Couplings, and AAS\TeX\ Examples}
-
-%% Use \author, \affil, and the \and command to format
-%% author and affiliation information.
-%% Note that \email has replaced the old \authoremail command
-%% from AASTeX v4.0. You can use \email to mark an email address
-%% anywhere in the paper, not just in the front matter.
-%% As in the title, use \\ to force line breaks.
-
-\author{Mohammadjavad Vakili\altaffilmark{1}}
+\author{Mohammadjavad Vakili\altaffilmark{1}, Chang~Hoon Hahn\altaffilmark{1}}
 
@@
 Standard halo occupation modeling (HOD) in large scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
-Modeling of galaxy clustering can face systematic effects if the number or properties of galaxies are correlated with other halo properties.
+Modeling of galaxy clustering can face systematic effects if the number of galaxies are correlated with other halo properties.
 Using the Small MultiDark-Planck high resolution $N$-body simulation and the measurements of the projected two-point correlation function and the number density of Sloan Digital Sky Survey (SDSS) DR7 main galaxy sample, we investigate the extent to which the dependence of halo occupation on halo concentration can be constrained, and to what extent allowing for this dependence can improve our modeling of galaxy clustering.
@@
 
-We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of assembly bias that is only present in the central occupation.
+We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of the impact of halo assembly bias on galaxy clustering.
+That is, the effect is only present in the central occupation and becomes less significant in brighter galaxy samples.
 Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
@@
 This phenomenon is known as halo assembly bias (see \citealt{sheth2004,gao2005, harker2006, weschler2006, gao2007,croton2007,wang2007,angulo2008,dalal2008,li2008,sunayama2016}).
-There is support for halo assembly bias in observations of SDSS redMaPPer galaxy clusters (\citealt{miyatake2016}).
+It has been claimed that there is support for halo assembly bias in observations of SDSS redMaPPer galaxy clusters (\citealt{miyatake2016}).
 
-Furthermore, the properties of galaxies within the halo may also depend on the halo's formation history.
-Then we may expect the occupation statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos.
-There have been many attempts in the literature at examining the dependence of galaxy properties on environment of the halos.
+Furthermore, the halo occupation may also depend on the formation history of halos.
+Then we may expect the spatial statistics of galaxies to be tied to the halo properties beyond mass such as the concentration of halos.
+There have been many attempts in the literature at examining the dependence of halo occupation on environment of the halos.
 But the results are mixed, and there is very little consensus.
@@
 They also show that the effect is different for the faint and the bright samples.
-By applying a group finder to SDSS DR7 galaxies, \citet{tinker2011} shows that the quenched fraction of galaxies is independent of the large-scale environment.
 
-Based on a group catalog of SDSS galaxies, \citet{blanton_group_2007} find that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
+%Based on a group catalog of SDSS galaxies, \citet{blanton_group_2007} find that shuffling of galaxy colors among groups of similar mass has very little effect (only a slight change in small scales: less than $\sim 300 \rm{kpc}$) on the clustering of galaxies.
 Based on an alternative group catalog, \citet{wang2013} shows that clustering of the central galaxies does not depend only on the halo mass, but also on additional parameters such as the specific star formation rate.
+%\todo{I think this paragraph might be a bit misleading to the reader, I think the paper could do without it. %Your work doesn't incorporate galaxy properties, but only halo properties.}
 
@@
 
-Age Matching models extend the Abundance Matching models to account for even higher orders of galaxy 
-assembly bias.
-In these models, galaxy color is matched to halo formation time so that older (redder) galaxies preferentially reside in older halos (\citealt{hw2013}).
-\citet{hearin2014} demonstrates that such an approach can reproduce a range of color and luminosity-dependent statistics of SDSS galaxies such as the 2PCF and galaxy-galaxy lensing.
-Based on the projected 2PCF measurements of (\citealt{hw2013}) galaxy catalogs, \citet{arz2014} showed that although the 2PCF measurements of these catalogs can be fit with the standard HOD modeling, the inferred HOD parameters cannot recover the underlying true HOD of these catalogs.
-That is, even in the presence of assembly bias in a galaxy sample, one can fit the clustering of this sample with HOD, but that does not guarantee recovery of the true HOD parameters.
-\citet{edHOD-weinberg} demonstrated that even with a galaxy catalog that has a significant level of assembly bias (e.g.
-\citealt{hw2013}), it is possible to extract the matter power spectrum more accurately if an environment-dependent HOD ($P(N|M,\delta)$) is used.
+Based on the projected 2PCF measurements of (\citealt{hw2013}) galaxy catalogs, \citet{arz2014} showed that after fitting the 2PCF measurements of these catalogs with the standard \emph{mass-only} HOD modeling, the inferred HOD does not match the \emph{true} halo occupation of these catalogs.
+That is, in the presence of assembly bias in a galaxy sample, one can fit the clustering of this sample with the standard \emph{mass-only} HOD, but that does not guarantee recovery of the true HOD parameters.
 
@@
 Furthermore, we discuss how taking assembly bias into account in a more complex HOD model can improve our modeling of galaxy clustering in certain brightness limits.
-Then, we make a qualitative comparison between the levels of assembly bias in the mock catalogs created from our constraints on the decorated HOD model, and the \citealt{hw2013} mock catalogs created using the abundance matching technique that uses maximum circular velocity $V_{\rm max}$ as subhalo property.
-Our comparison shows the levels of assembly bias seen in the predictions of both models follow the same trend.
-That is assembly bias is more prominent in lower luminosity-threshold samples and its impact on galaxy clustering is only significant on large scales.
+Then, we make a qualitative comparison between the levels of the impact of assembly bias in our best-fit decorated HOD model on galaxy clustering, and the impact of assembly bias present in (\citealt{hw2013}) catalogs on galaxy clustering.
+Our comparison shows the levels of the impact of assembly bias on galaxy clustering seen in the predictions of both models follow the same trend.
+That is assembly bias is more prominent in lower luminosity-threshold samples and its impact on galaxy clustering is only significant on large scales (more than a few Mpc).
 
@@
 In addition to the projected 2PCF, we use the number density given by the number of mock galaxies divided by the comoving volume of the $\mathtt{SMDP}$ simulation.
+
+Note that a full forward model of the data requires running the simulation at different redshifts, generation of light cones, accounting for the complex survey geometry and systematic errors such as fiber collisions.
+Using the $z=0$ output of the $\mathtt{SMDP}$ simulation in our forward model of the spatial distribution of galaxies is only an approximation.
+This approximation can be justified by the small redshift range of the SDSS DR7 main galaxy sample.
+As described in \citealt{zehavi2011}, using random catalogs with angular window function of the data in measurements of galaxy clustering accounts for the geometry of the data.
+As described in Section~\ref{sec:data}, the fiber collision correction method of \citealt{guo2012} is applied to the SDSS clustering measurements used in this study.
+Therefore we do not account for that effect in our forward model.
 
@@
 \citet{arz2014} shows that in the mock catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters.
-Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
+Although we cannot rule out moderate levels of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.
 
@@
 \citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
-We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$-type galaxies.
+We aim to provide a comparison between the impact of assembly bias on clustering in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$-type galaxies.
 In particular, we consider the abundance matching catalogs produced by \citet{hw2013}.
@@
 For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the original catalogs of \citet{hw2013} is shown in Figure \ref{fig:randomized} with the red curves.
-As demonstrated in Figure \ref{fig:randomized} (and as previously noted by \citealt{arz2014,edHOD-weinberg}), the relative difference in $w_{p}$ is only significant in relatively large scales.
-This implies that in these catalogs, only the central occupation are affected by assembly bias.
+As demonstrated in Figure \ref{fig:randomized} (and as previously noted by \citealt{arz2014,edHOD-weinberg}), the relative difference in $w_{p}$ is only significant in relatively large scales ($r_{p} > 1 \mathrm{Mpc} \; h^{-1}$).
+This implies that in these catalogs, only the central occupation is affected by assembly bias.
 This is in agreement with our findings.
 
-Furthermore, we investigate whether the levels of assembly bias predicted by our findings are in agreement with the abundance matching catalogs of \citet{hw2013}.
+Furthermore, we investigate whether the impact of assembly bias on galaxy clustering predicted by our findings are in agreement with the abundance matching catalogs of \citet{hw2013}.
 First, we make random draws from the posterior probability distribution function over the parameters of the model with assembly bias.
@@
 We note that our findings follow the same trend.
-That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales ($r_{p} > 1 Mpc \; h^{-1}$).
-Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that assembly bias becomes less significant in brighter galaxy samples.
-Furthermore, we notice that our mock catalogs favor more moderate levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
+That is, we see negligible difference in the small scale clustering and more considerable differences in $w_{p}$ on larger scales ($r_{p} > 1\; \mathrm{Mpc}h^{-1}$).
+Similar to findings of \citet{arz2014}, \citet{lehman2015}, and \citet{edHOD-weinberg}, we see that the impact of assembly bias on galaxy clustering becomes less significant in brighter galaxy samples.
+Furthermore, we notice that our mock catalogs favor more moderate changes in galaxy clustering as a result of assembly bias.
 
@@
 For $M_{\rm r}<-19, -18.5$ we find no correlation, and for the faintest sample, we find negative correlation.
-Given the large scale halo assembly bias and the scale-dependent feature of assembly bias in the quasi-linear scales, these constraints lead to improvement in modeling the galaxy clustering.
+Given the large scale halo assembly bias and the scale-dependent feature of assembly bias in the quasi-linear scales, our constraints on the more flexible HOD model lead to improvement in modeling the galaxy clustering.
 However, we do not find these improvements to be sufficient to lower the information criteria scores associated with the more complex model.
@@
 
-Comparison of the levels of assembly bias in the catalogs constructed based on our results and the abundance matching catalogs presented in \citet{hw2013,arz2014} and \citet{edHOD-weinberg} demonstrates that our constraints predict more moderate levels of assembly bias which follows the same trend.
-That is, assembly bias mostly affects the large scale and the quasi-linear clustering and the small scale clustering remains unaltered.
-In addition, the effect of assembly bias vanishes in the brightest galaxy samples.
+We compare the impact of assembly bias on galaxy clustering between the catalogs constructed from our results and the abundance matching catalogs presented in \citet{hw2013,arz2014}.
+We demonstrate that the effect of assembly bias on galaxy clustering predicted from our results is similar to (but more moderate than) the effects seen in the abundance matching catalogs of \citet{hw2013}.
+That is, assembly bias mostly affects the large scales and the quasi-linear clustering and the small scale clustering remains unaltered.
+In addition, the effect of assembly bias on galaxy clustering vanishes in the brightest galaxy samples.
 
@@
 
-We are grateful to David~W.~Hogg, Chang~Hoon~Hahn, Alex~I.~Malz, Andrew~Hearin, Andrew~Zentner, Chia-Hsun~Chuang, Michael~R.~Blanton, and Kilian~Walsh for discussions related to this work.
+We are grateful to David~W.~Hogg, Alex~I.~Malz, Andrew~Hearin, Andrew~Zentner, Chia-Hsun~Chuang, Michael~R.~Blanton, and Kilian~Walsh for discussions related to this work.
 This work was supported by the NSF grant AST-1517237.
@@
 The red line corresponds to the subhalo abundance matching catalog (\citealt{hw2013,hearin2014}).
-Comparison between the level of assembly bias (encoded in the relative difference in $w_p$) shows that the our constraints favor \emph{more} \emph{moderate} levels of assembly bias than the levels seen in the abundance matching mock catalogs.
-Within both models, the small scale clustering remains unaltered after randomizing the catalogs, signaling the lack of correlation between the satellite population and the halo concentration at a fixed mass in the two models.}
+Our constraints favor \emph{more} \emph{moderate} levels of the impact of assembly bias on galaxy clustering than the levels seen in the abundance matching mock catalogs.
+Within both models, the small scale clustering remains unaltered after randomizing the catalogs, signaling the lack of correlation between the satellite occupation and the halo concentration at a fixed mass in the two models.}
 \label{fig:randomized}

### 2017-03-06 text/ms.tex
make file and some edits

@@
 \usepackage{morefloats}
+\definecolor{dred}{rgb}{0.75,0,0}
 \definecolor{darkred}{rgb}{0.5,0,0}
@@
 For the simulations used in this work, we make use of the Rockstar (\citealt{rockstar}) halo catalogs in the $z=0$ snapshot of the Small MultiDark of Planck cosmology (referred to as $\mathtt{SMDP}$) (\citealt{smallmultidark}).
-This high resolution $N$-body simulation (publicly available at \url{https://www.cosmosim.org}) was carried out using the GADGET-2 code
-(see \citealt{smallmultidark} and references therein) code, following the Planck $\Lambda$CDM cosmological parameters 
+This high resolution $N$-body simulation (publicly available at \url{https://www.cosmosim.org}) was carried out using the
+%%% CHH: small typo
+{\bf \color{dred} GADGET-2 (see \citealt{smallmultidark} and references therein) code}, 
+%%%
+following the Planck $\Lambda$CDM cosmological parameters 
 $\Omega_{\rm m} = 0.307$, $\Omega_{\rm b} = 0.048$, $\Omega_{\Lambda} = 0.693$, $\sigma_{8} = 0.823$, $n_{\rm s}=0.96$, 
@@
 
-In the $\mathtt{SMDP}$ simulation, as discussed in \citet{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.
+In the $\mathtt{SMDP}$ simulation, as discussed in \citet{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$
+%%% CHH: grammar error
+{\bf \color{dred} particles, which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.}
+%%%
 The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy--halo connection in a wide range of luminosity thresholds.

### 2017-03-06 text/ms.tex
some further edits; see github issue

@@
 %%%
-The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy--halo connection in a wide range of luminosity thresholds.
-Fainter galaxy samples reside in lower mass halos, and the more luminous galaxy samples considered in this investigation occupy higher comoving volumes.
+%The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution 
+%requirements of studying the galaxy--halo connection in a wide range of luminosity thresholds. 
+%%%
+%%% Re-worded 
+{\bf \color{dred}
+    The $\mathtt{SMDP}$ simulation provides a number of advantages by satisfying both the size 
+    and resolution requirements of studying the galaxy--halo connection in a wide range of 
+    luminosity thresholds. For fainter galaxy samples, the faintest galaxies reside in lower 
+    mass halos, which requires high resolution. Meanwhile for luminous galaxy samples, their 
+    lower number densities requires a large comoving volume. 
+}
+%%%
 Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos.
-In the context of Subhalo-Abundance matching modeling, accuracy of which depends on subhalo completeness especially in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest galaxy samples in the SDSS data (see \citet{hod_vs_sham}).
+%%% CHH: see issue in github
+{\bf \color{darkgreen}
+    In the context of Subhalo-Abundance matching modeling accuracy of which depends on subhalo completeness especially in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest galaxy samples in the SDSS data~\citep[see][]{hod_vs_sham}.
+}
+%%%
 The added advantage of using the $\mathtt{SMDP}$ simulation over some of the other industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its larger comoving volume.

### 2017-03-06 text/ms.tex
Ref. Report Minor #1 addressed. @MJV Double check correction.

@@
 
-In this work, we aim to investigate the dependence of halo occupation on halo concentration, and how this dependence can be constrained in the low-redshift universe with the measurements of the 2PCF of galaxies with a wide range of luminosities in the SDSS DR7 main galaxy sample.
+%In this work, we aim to investigate the dependence of halo occupation on halo concentration, and how this dependence can be constrained in the low-redshift universe with the measurements of the 2PCF of galaxies with a wide range of luminosities in the SDSS DR7 main galaxy sample.
+%%% CHH: Re-phrasing 
+In this work, we aim to investigate the dependence of halo occupation on 
+{\bf \color{dred} 
+    halo concentration and how this dependence can be constrained in the low-redshift universe by 2PCF measurements of galaxies in a wide range of luminosities in the SDSS DR7 main galaxy sample. 
+}
+%%%
 In order to achieve this goal, we need to adopt a HOD model that takes into account 
 a dependence on halo properties beyond mass. 
-There are a number of frameworks in the literature.
-\citet{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} have proposed environment-dependent HOD modeling methods that take into account the large-scale density contrast.
-The model that we use in this investigation is the decorated HOD framework (\citealt{decorated}).
-In the decorated HOD framework, at a fixed halo mass, halos are populated with galaxies according to the standard HOD modeling.
-Then, a secondary halo property is selected.
-At a fixed halo mass, halos are split into two populations: halos with the highest and halos with the lowest values of the secondary property.
-The two population receive enhancements (decrements) in their number of galaxies according to a assembly bias amplitude parameter.
-The assembly bias parameter will not be degenerate with the rest of the HOD parameters.
+%%% CHH: Re-phrasing to address ref. report
+{\bf \color{dred} 
+    A number of frameworks in the literature \citep{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} 
+    have proposed environment-dependent HOD models that take into account the large-scale density contrast. 
+    In this investigation, we use the following case of the decorated HOD framework \citep{decorated}.  
+    In our decorated HOD framework, at fixed halo mass, halos are populated with galaxies according to 
+    the standard HOD model. Then using a secondary halo property, halos are split into two populations
+    in halo mass bins: halos with the highest and lowest secondary property values. Afterwards, based
+    on the assembly bias amplitude parameter, the number of galaxies in the two populations are enhanced
+    or reduced. In this model, the assembly bias parameter is not be degenerate with the rest of the HOD 
+    parameters. 
+}
+%%%
 

### 2017-03-06 text/ms.tex
Ref. Report Minor #5 addressed; Minor #7 partly addressed

@@
 Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos.
-%%% CHH: see issue in github
-{\bf \color{darkgreen}
-    In the context of Subhalo-Abundance matching modeling accuracy of which depends on subhalo completeness especially in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest galaxy samples in the SDSS data~\citep[see][]{hod_vs_sham}.
+%%% CHH: Re-worded based on (github issue #1)
+{\bf \color{dred}
+    In the context of Subhalo-Abundance Matching models, which requires subhalo completeness 
+    in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest 
+    galaxy samples in the SDSS data~\citep[see][]{hod_vs_sham}. 
 }
@@
 This approach is different from other simulation-based halo occupation modeling techniques (see \citealt{hod_vs_sham,zheng_guo}) in that the positions of the satellites are not assigned to the dark matter particles in the $N$-body simulation.
-The concentration of the NFW profile is given by the empirical mass-concentration relation provided by \citet{nfw_c(M)}.
+%%% Missing citation
+{\bf \color{darkgreen} 
+    The concentration of the NFW profile is given by the empirical 
+    mass-concentration relation provided by \citet{nfw_c(M)}. 
+}
+%%%
 The velocities of the satellite galaxies are given by two components.
@@
 
-\subsection{constraints and interpretations}
-
-Our constraints on the assembly bias parameters fall into two main categories. First, the satellite 
-assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$.
+\subsection{{\color{dred} Constraints and Interpretations}}
+%Our constraints on the assembly bias parameters fall into two main categories. First, the satellite 
+%assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$. 
+%%% Re-worded
+{\bf \color{dred}  
+    In this section, we present the constraints derived for the two assembly 
+    bias parameters: the satellite assembly bias parameter ($\asat$) and the 
+    central assembly bias parameter $\acen$. 
+} 
+%%%
 As shown in Figure \ref{fig:bias}, for all the eight luminosity-threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are 
 consistent with zero.
-On the other hand, our constraints on the parameter $\acen$---albeit not tightly constrained---show a trend which can be summarized as the following.
+On the other hand, our constraints on the parameter $\acen$--- albeit not tightly constrained--- show a trend which can be summarized as the following.
 In the most luminous galaxy samples, i.e.
@@
 A few galaxy--halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population. 
-\citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.
+%%%% CHH: (Ref. Report Minor #5) re-worded and Conroy et al. (2006) included in citations. 
+{\bf \color{dred} 
+    \citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ 
+    \citep{conroy:2006aa,hw2013,reddick2013} exhibit some levels of assembly bias. 
+}
 We aim to provide a comparison between the impact of assembly bias on clustering in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$-type galaxies.

### 2017-03-06 text/ms.tex
apj format

@@
-\documentclass[12pt, preprint]{aastex}
-%\documentclass[12pt, preprint]{emulateapj}
-\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{graphicx}	% For figures
-\usepackage{natbib}	% For citep and citep
-\usepackage{amsmath}	% for \iint
-\usepackage{mathtools}
-\usepackage{bm}
-\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
-\usepackage{hyperref}
-\usepackage{algorithmic,algorithm}
-\hypersetup{colorlinks}
-\usepackage{color}
-\usepackage{morefloats}
+\documentclass[twocolumn]{aastex61}
+\pdfoutput=1 %for arXiv submission
+\usepackage{amsmath,amstext}
+\usepackage[T1]{fontenc}
+\usepackage{apjfonts} 
+\usepackage[figure,figure*]{hypcap}
+
+\renewcommand*{\sectionautorefname}{Section} %for \autoref
+\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+
 \definecolor{dred}{rgb}{0.75,0,0}
@@
 
+\shorttitle{AASTeX 6.1 Template}
+\shortauthors{Vakili \& Hahn}
+
 \begin{document}
@@
 
-\author{Mohammadjavad Vakili\altaffilmark{1}, Chang~Hoon Hahn\altaffilmark{1}}
+\author{Mohammadjavad Vakili}
+\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl, New York, NY, 10003}
 
-\email{mjvakili@nyu.edu}
-
-\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl, New York, NY, 10003}
+\author{ChangHoon Hahn}
+\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl, New York, NY, 10003}
 
 \begin{abstract}
-
 Clustering of dark matter halos has been shown to depend on halo properties beyond mass such as halo concentration, a phenomenon referred to as halo assembly bias.
@@
 \end{abstract}
-\keywords{Cosmology: large-scale-structure of the universe, galaxies: halos}
+
+\keywords{Cosmology: large-scale-structure of the universe--- galaxies: halos}
 
 \section{Introduction}
-
 Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark matter halos.
@@
 %%% CHH: Re-phrasing to address ref. report
-{\bf \color{dred} 
+{\bf \color{red} 
     A number of frameworks in the literature \citep{edHOD-tinker,edHOD-gillmartin,edHOD-weinberg} 
@@
 %%% CHH: small typo
-{\bf \color{dred} GADGET-2 (see \citealt{smallmultidark} and references therein) code}, 
+{\bf \color{red} GADGET-2 (see \citealt{smallmultidark} and references therein) code}, 
 %%%
@@
 %%% CHH: grammar error
-{\bf \color{dred} particles, which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.}
+{\bf \color{red} particles, which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$.}
 %%%
@@
 %%% Re-worded 
-{\bf \color{dred}
+{\bf \color{red}
     The $\mathtt{SMDP}$ simulation provides a number of advantages by satisfying both the size 
@@
 %%% CHH: Re-worded based on (github issue #1)
-{\bf \color{dred}
+{\bf \color{red}
     In the context of Subhalo-Abundance Matching models, which requires subhalo completeness 
@@
 %%% Missing citation
-{\bf \color{darkgreen} 
+{\bf \color{green} 
     The concentration of the NFW profile is given by the empirical 
@@
 
-\clearpage
+%\clearpage
 
@@
 \end{figure*}
-\clearpage
+%\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{document}
-
-%%
-%% End of file `sample.tex'.

### 2017-03-06 code/biased_hod.py
mercer cleanup

@@ -38,7 +38,9 @@ class MCMC_model(object):
         
         self.Mr = Mr
         self.model = composite_model(Mr)
-        self.halocat = CachedHaloCatalog(simname = 'smdp', redshift = 0.0 , version_name = 'mj', halo_finder = 'rockstar')
+        self.halocat = CachedHaloCatalog(simname = 'bolshoi_planck', redshift = 0.0 , version_name = 'mj', halo_finder = 'rockstar')
+
+        # , fname ='/scratch/mv1003/halocat/', update_cached_fname ='/home/mj/halocat/hlist_1.00.list.smdp.hdf5.')# '/scratch/mv1003/halocat/hlist_1.00.list.smdp.hdf5.')
         #self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0.0 , halo_finder = 'rockstar')
 
         ###pair counter settings ###

### 2017-03-06 code/hod.py

@@ -25,7 +25,7 @@ class MCMC_model(object):
         
         self.Mr = Mr
         self.model = single_model(Mr)
-        self.halocat = CachedHaloCatalog(simname = 'bolplanck', redshift = 0, halo_finder = 'rockstar')
+        self.halocat = CachedHaloCatalog(simname = 'bolshoi_planck', version_name = 'mj', redshift = 0, halo_finder = 'rockstar')
 
         ###pair counter settings ###
 
@@ -35,7 +35,7 @@ class MCMC_model(object):
         self.binfile = path.join(path.dirname(path.abspath(__file__)),
                         "../", "bin")
         
-        self.rbins = np.loadtxt("rbins.dat") 
+        self.rbins = np.loadtxt("/scratch/mv1003/projects/wp195/code/rbins.dat") 
         self.autocorr = 1
 
     def __call__(self, theta, prior_range):

### 2017-03-07 text/ms.tex
Edits on the abstract and starting on the intro

@@
 Clustering of dark matter halos has been shown to depend on halo properties beyond mass such as halo concentration, a phenomenon referred to as halo assembly bias. 
-Standard halo occupation modeling (HOD) in large scale structure studies assumes that halo mass alone is sufficient in characterizing the connection between galaxies and halos.
+%%% 
+Standard halo occupation {\bf \color{dred} models} (HOD) in large scale structure studies assume that halo mass alone is sufficient in characterizing the connection between galaxies and halos. 
+%%% 
+%%% CHH: @MJV, this sentence is far too long and indirect (RE RefReport Minor #7)
+{\bf \color{darkgreen}
 Modeling of galaxy clustering can face systematic effects if the number of galaxies are correlated with other halo properties.
 Using the Small MultiDark-Planck high resolution $N$-body simulation and the measurements of the projected two-point correlation function and the number density of Sloan Digital Sky Survey (SDSS) DR7 main galaxy sample, we investigate the extent to which the dependence of halo occupation on halo concentration can be constrained, and to what extent allowing for this dependence can improve our modeling of galaxy clustering.
+}
+%%%
 
-Given the SDSS clustering data, our constraints on HOD with assembly bias, suggests that satellite population is not correlated with halo concentration at fixed halo mass.
-Furthermore, in terms of the occupation of centrals at fixed halo mass, our results favor lack of correlation with halo concentration in the most luminous samples ($M_{\rm r}<-21.5,-21$), modest levels of correlation for $M_{\rm r}<-20.5,-20, -19.5$ samples, lack of correlation for $M_{\rm r}<-19,-18.5$ samples, and anti-correlation for the faintest sample $M_{\rm r}<-18$.
+%%% 
+{\bf \color{dred} From our} constraints on HOD with assembly bias, suggests that satellite population is not correlated with halo concentration at fixed halo mass. 
+%%% 
+%%% CHH: @MJV, this sentence is also long and a bit difficult to comprehend -- clarify. 
+{\bf \color{darkgreen} 
+Furthermore, in terms of the occupation of centrals at fixed halo mass, our results favor lack of correlation with halo concentration in the most luminous samples ($M_{\rm r}<-21.5,-21$), modest levels of correlation for $M_{\rm r}<-20.5,-20, -19.5$ samples, lack of correlation for $M_{\rm r}<-19,-18.5$ samples, and anti-correlation for the faintest sample $M_{\rm r}<-18$.}
+%%%
 
 We show that in comparison with abundance-matching mock catalogs, our findings suggest qualitatively similar but modest levels of the impact of halo assembly bias on galaxy clustering. 
-That is, the effect is only present in the central occupation and becomes less significant in brighter galaxy samples.
+{\bf \color{dred} The} effect is only present in the central occupation and becomes less significant in brighter galaxy samples.
 Furthermore, by performing model comparison based on information criteria, we find that in most cases, the standard mass-only HOD model is still favored by the observations.
@@
 Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark matter halos. 
-Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
+%%%
+Detailed study of the galaxy--halo connection is therefore critical in {\bf \color{dred} constraining} cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics.
+%%%
 One of the most powerful methods for describing the galaxy--halo connection is the halo occupation 
@@
 HOD is an empirical framework that provides an analytic prescription for the expected number of galaxies $N$ that reside in halos by specifying a probability distribution function $P(N|x)$ where $x$ is a property of the halo.
-The assumption of the standard HOD modeling is that the halo mass $M$ alone is sufficient in determining the galaxy population of a halo.
-That is, the statistical properties of galaxies is governed by the halo mass.
+%%%
+{\bf \color{dred} The standard HOD model assumes} that halo mass $M$ alone is sufficient in determining the galaxy population of a halo. 
+%%%
+%%% CHH: @MJV, what do you mean by "statistical properties of galaxies"? Their spacial statistics? 
+{\bf \color{dred} In the standard model,} {\bf \color{darkgreen} the statistical properties of galaxies is governed by the halo mass.}
+%%%
 Mathematically, this assumption can be written as $P(N|M,\{x\})=P(N|M)$ where $\{x\}$ is the set of all possible halo properties beyond halo mass $M$.
